### 2023-05-22 paper/Chapters/Chapter1.tex
Add template paper

\chapter{Introduction}

\section{History}

Something on the topic

\endinput

### 2023-05-22 paper/paper.tex
Renames

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Masters/Doctoral Thesis 
% LaTeX Template
% Version 2.5 (27/8/17)
%
% This template was downloaded from:
% http://www.LaTeXTemplates.com
%
% Version 2.x major modifications by:
% Vel (vel@latextemplates.com)
%
% This template is based on a template by:
% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
%
% Template license:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
openany
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{mathpazo} % Use the Palatino font by default

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=3.8cm, % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	THESIS INFORMATION
%----------------------------------------------------------------------------------------

\thesistitle{Thesis Title} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{John \textsc{Smith}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Data Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.ucu.edu.ua}{Ukrainian Catholic University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{http://department.university.com}{Faculty of Applied Sciences}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{http://researchgroup.university.com}{Department of Computer Sciences}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
}

\begin{document}
\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages

\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}
\begin{center}

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Master Thesis}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{http://www.johnsmith.com}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{http://www.jamessmith.com}{\supname} % Supervisor name - remove the \href bracket to remove the link  
\end{flushright}
\end{minipage}\\[3cm]

\vfill

\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
\textit{in the}\\[0.4cm]
\groupname\\\deptname\\[2cm] % Research group name and department name

\vfill
\includegraphics[height=3cm]{UCU-Apps 2022.png} % University/department logo - uncomment to place it

\vfill
{\large Lviv 2022}\\[4cm] % Date

\vfill
\end{center}
\end{titlepage}

%----------------------------------------------------------------------------------------
%	DECLARATION PAGE
%----------------------------------------------------------------------------------------

\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

\cleardoublepage

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak

\hfill Dave Barry

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots

\noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
\end{acknowledgements}

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

\tableofcontents % Prints the main table of contents

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)

\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\

\end{abbreviations}

%----------------------------------------------------------------------------------------
%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
%----------------------------------------------------------------------------------------

\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it

Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
%Constant Name & $Symbol$ & $Constant Value$ with units\\

\end{constants}

%----------------------------------------------------------------------------------------
%	SYMBOLS
%----------------------------------------------------------------------------------------

\begin{symbols}{lll} % Include a list of Symbols (a three column table)

$a$ & distance & \si{\meter} \\
$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
%Symbol & Name & Unit \\

\addlinespace % Gap to separate the Roman symbols from the Greek

$\omega$ & angular frequency & \si{\radian} \\

\end{symbols}

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedicatory{For/Dedicated to/To my\ldots}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter % Begin numeric (1,2,3...) page numbering

\pagestyle{thesis} % Return the page headers back to the "thesis" style

% Include the chapters of the thesis as separate files from the Chapters folder
% Uncomment the lines as you write the chapters

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2} 
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\appendix % Cue to tell LaTeX that the following "chapters" are Appendices

% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\printbibliography[heading=bibintoc]

%----------------------------------------------------------------------------------------

\end{document}

### 2023-05-22 paper/paper.tex
Formatting, add title etc

@@
 
-\usepackage[utf8]{inputenc} % Required for inputting international characters
+% \usepackage[utf8]{inputenc} % Required for inputting international characters
 \usepackage[T1]{fontenc} % Output font encoding for international characters
@@
 
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+% \usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
 
-\addbibresource{example.bib} % The filename of the bibliography
+\addbibresource{references.bib} % The filename of the bibliography
 
 \usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
+
+\usepackage{todonotes}
 
@@
 
-\thesistitle{Thesis Title} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
-\supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
+\thesistitle{Corner localization and camera calibration from imaged lattices} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\supervisor{Dr. James \textsc{Pritts}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
 \examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
 \degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
-\author{John \textsc{Smith}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
+\author{Andrii \textsc{Stadnik}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
 \addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
@@
 \university{\href{http://www.ucu.edu.ua}{Ukrainian Catholic University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
-\department{\href{http://department.university.com}{Faculty of Applied Sciences}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
-\group{\href{http://researchgroup.university.com}{Department of Computer Sciences}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
-\faculty{\href{http://faculty.university.com}{}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
+% \department{\href{http://department.university.com}{Faculty of Applied Sciences}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+% \group{\href{http://researchgroup.university.com}{Department of Computer Sciences}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
+% \faculty{\href{http://faculty.university.com}{}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
+\department{Faculty of Applied Sciences} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
+\group{Department of Computer Sciences} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
+\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
 
@@
 				\emph{Author:}\\
-\href{http://www.johnsmith.com}{\authorname} % Author name - remove the \href bracket to remove the link
+				% \href{http://www.johnsmith.com}{\authorname} % Author name - remove the \href bracket to remove the link
+				\authorname % Author name - remove the \href bracket to remove the link
 			\end{flushleft}
@@
 				\emph{Supervisor:} \\
-\href{http://www.jamessmith.com}{\supname} % Supervisor name - remove the \href bracket to remove the link  
+				\href{https://prittjam.github.io/}{\supname} % Supervisor name - remove the \href bracket to remove the link  
 			\end{flushright}
@@
 	The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
+
+	% Camera calibration is a crucial step in many computer vision applications.
+	% However, despite the constant development of solutions, they still tend to
+	% be sensitive to the noise of the input data, bad lightning conditions,
+	% occlusions and other problems, especially under the conditions of
+	% high distortion, such as mobile phones and GoPro-type cameras.
+	%
+	% In this paper, we propose a novel approach to camera calibration. We want to
+	% use a robust solver to estimate the geometry between the correspondence of
+	% points on the calibration pattern, which are called conjugate translations.
+	% It is possible to use those
+	% conjugate translations to predict the possible position of the previously
+	% undetected calibration board features. We want to use the new points to constrain the camera calibration further. This process can be run iteratively,
+	% refining the calibration board features, conjugate translations, and improving
+	% the camera calibration.
 \end{abstract}
@@
 
-\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
-
-\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
-\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\
-
-\end{abbreviations}
+% \begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
+%
+% 	\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
+% 	\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\
+%
+% \end{abbreviations}
 
@@
 
-\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
-
-% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
-
-Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
-%Constant Name & $Symbol$ & $Constant Value$ with units\\
-
-\end{constants}
+% \begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
+%
+% 	% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
+%
+% 	Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
+% 	%Constant Name & $Symbol$ & $Constant Value$ with units\\
+%
+% \end{constants}
 
@@
 
-\begin{symbols}{lll} % Include a list of Symbols (a three column table)
-
-$a$ & distance & \si{\meter} \\
-$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
-%Symbol & Name & Unit \\
-
-\addlinespace % Gap to separate the Roman symbols from the Greek
-
-$\omega$ & angular frequency & \si{\radian} \\
-
-\end{symbols}
+% \begin{symbols}{lll} % Include a list of Symbols (a three column table)
+%
+% 	$a$ & distance & \si{\meter} \\
+% 	$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
+% 	%Symbol & Name & Unit \\
+%
+% 	\addlinespace % Gap to separate the Roman symbols from the Greek
+%
+% 	$\omega$ & angular frequency & \si{\radian} \\
+%
+% \end{symbols}
 
@@
 \pagestyle{thesis} % Return the page headers back to the "thesis" style
+
+\listoftodos{1}
+\todo{Remove list of todos}
 
@@
 
-\include{Appendices/AppendixA}
+% \include{Appendices/AppendixA}
 %\include{Appendices/AppendixB}

### 2023-05-22 paper/Chapters/Chapter1.tex
Paper updates

@@
-\chapter{Introduction}
+\chapter{Introduction and motivation}\label{cha:introduction_and_motivation}
 
-\section{History}
+\section{Outline of the problem}\label{sec:outline_of_the_problem}
 
-Something on the topic
+Better camera calibration improves the performance of various downstream tasks
+by providing a more accurate mapping between 3D world coordinates and 2D image
+plane coordinates. This improved mapping enables precise alignment, positioning,
+and scaling of objects within the scene. By determining the camera's intrinsic
+and extrinsic parameters, algorithms can correct for lens distortion, estimate
+depth information, and accurately overlay virtual content. Consequently, tasks
+such as 3D reconstruction, augmented reality, and object detection can achieve
+better results in terms of precision, spatial consistency, and overall visual
+quality.
+
+Although manufacturers can estimate camera calibration parameters a priori,
+fully automatic calibration is often preferred, especially when camera metadata
+is unavailable. Currently, wide-angle lenses, particularly in mobile phones and
+GoPro-type cameras, dominate consumer photography. These cameras pose additional
+challenges due to their requirement for highly non-linear models with numerous
+parameters. The high distortion of the image plane also makes finding key points
+robustly challenging.
+
+Typically, camera calibration is obtained by capturing an image of a known
+calibration pattern, which is then used to estimate the camera parameters.
+Alternatively, some methods do not use a calibration pattern but instead infer
+geometric constraints directly from the scene. However, this approach is
+generally less accurate.
+
+As reported by \textcite{duisterhofTartanCalibIterativeWideAngle2022} on
+\citedate{duisterhofTartanCalibIterativeWideAngle2022}, the current state-of-the-art
+methods
+\cite{olsonAprilTagRobustFlexible2011}
+\cite{schopsWhyHaving102020} \cite{krogiusFlexibleLayoutsFiducial2019}
+fail on images with high distortion.
+\textcite{duisterhofTartanCalibIterativeWideAngle2022} suggested an iterative
+the approach of image undistortion and target reprojection, achieving the superior
+robustness to the noise than the state-of-the-art methods because the feature
+detection is performed on the undistorted image.
+
+Instead of searching for the features on the undistorted image, it is possible to
+use conjugate translations \cite{schaffalitzkyGeometricGroupingRepeated1998},
+to predict the position of the previously undetected feature points and to
+further, constrain the camera calibration.
+\textcite{prittsMinimalSolversRectifying2021} showed that three pairs of points,
+related by the same translations on the scene plane are sufficient to estimate
+the camera calibration and the parameters of the conjugate translations.
+
+We want to use the work of \textcite{prittsMinimalSolversRectifying2021} to bootstrap
+the camera calibration, and then use the found conjugate translations and camera
+parameters to iteratively predict and refine the positions of the calibration
+board features, calibration parameters, and conjugate translations.
+
+\section{Thesis structure}\label{sec:thesis_structure}
+
+This paper has the following structure: in \autoref{sec:related_work}, we will describe the related work, including the
+literature search method and methodology, various subtopics of the camera
+calibration, mention conjugate translations, and outline the state-of-the-art
+solutions. We define the research gap in \autoref{sec:gap_analysis} and outline
+the proposed approach to solution and evaluation in
+\autoref{sec:problem_setting_and_approach_to_solution}. We will describe the
+early results in \autoref{sec:early_results_and_discussion}, including the
+dataset analysis, feature detector, and conjugately translated points simulator.
+In \autoref{sec:summary_and_future_work}, we will summarize the results and
+outline future work.
+\todo{Update}
 

### 2023-05-22 calibration/benchmark/benchmark.py
Update solvers, add optimization

@@ -2,10 +2,18 @@ from dataclasses import dataclass, field
 
 import numpy as np
 from tqdm.contrib.concurrent import process_map
-
 from calibration.benchmark.calib import calibrate
-from calibration.benchmark.features import (Features, babelcalib_features,
-                                            simul_features)
+from calibration.solver.scaramuzza.solve import solve as solve_scaramuzza
+from calibration.solver.optimization.solve import solve as solve_optimization
+
+# from calibration.benchmark.calib import calibrate_optimization, calibrate_scaramuzza
+from calibration.benchmark.features import (
+    BABELCALIB_INP,
+    SIMUL_INP,
+    Features,
+    babelcalib_features,
+    simul_features,
+)
 from calibration.data.babelcalib.babelcalib import Dataset, load_babelcalib
 from calibration.data.babelcalib.entry import Entry
 from calibration.projector.board import gen_checkerboard_grid
@@ -17,39 +25,37 @@ from calibration.projector.projector import Projector
 class BenchmarkResult:
     input: Entry | Projector
     features: Features | None
-    prediction: Projector | None
-    error: float | None = field(init=False)
+    predictions: dict[str, Projector]
+    errors: dict[str, float] = field(init=False)
 
     def __post_init__(self):
-        self.error = self._calc_error()
+        self.errors = {k: self._calc_error(v) for k, v in self.predictions.items()}
 
-    def _calc_error(self) -> float | None:
-        if self.features is None or self.prediction is None:
-            return None
+    def _calc_error(self, proj: Projector) -> float:
+        assert self.features is not None
         try:
-            max_point_img_space = np.r_[self.prediction.camera.resolution, 1]
+            max_point_img_space = np.r_[proj.camera.resolution, 1]
             max_point = (
-                np.linalg.inv(self.prediction.camera.intrinsic_matrix)
-                @ max_point_img_space
+                np.linalg.inv(proj.camera.intrinsic_matrix) @ max_point_img_space
             )
             max_r = float(np.linalg.norm(max_point[:2]))
-            corners_ = self.prediction.project(self.features.board, max_r)
[…]

### 2023-05-22 calibration/benchmark/calib.py

@@ -1,20 +1,63 @@
+from functools import partial
+from typing import Callable
+import numpy as np
+from tqdm.auto import tqdm
 from tqdm.contrib.concurrent import process_map
 
 from calibration.projector.camera import Camera
 from calibration.projector.projector import Projector
-from calibration.solver.solve import solve
 
 from .features import Features
 
 
-def _calibrate(arg: tuple[Features | None, Camera]) -> Projector | None:
+_SOLVER = Callable[[np.ndarray, np.ndarray, Camera], Projector]
+
+
+def _calibrate_helper(
+    arg: tuple[Features | None, Camera], solvers: list[tuple[str, _SOLVER]]
+) -> dict[str, Projector]:
     features, camera = arg
-    return None if features is None else solve(features.corners, features.board, camera)
+    if features is None:
+        return {}
+    return features and {
+        solver_name: solver(features.corners, features.board, camera)
+        for solver_name, solver in solvers
+    }
 
 
 def calibrate(
-    feature_and_camera: list[tuple[Features | None, Camera]]
-) -> list[Projector | None]:
-    return process_map(
-        _calibrate, feature_and_camera, chunksize=1000, leave=False, desc="Calibrating"
+    solvers: list[tuple[str, _SOLVER]],
+    feature_and_camera: list[tuple[Features, Camera]],
+) -> list[dict[str, Projector]]:
+    return list(
+        map(
+            partial(_calibrate_helper, solvers=solvers),
+            tqdm(feature_and_camera),
+        )
     )
+    # return process_map(
+    #     partial(_calibrate_helper, solvers=solvers),
+    #     feature_and_camera,
+    #     # chunksize=1000,
+    #     chunksize=10,
+    #     leave=False,
+    #     desc="Calibrating",
+    # )
+
+
+#
+# def calibrate_optimization(feature_and_camera: list[tuple[Features, Camera]]):
+#     cornerss = np.stack([feature.corners for feature, _ in feature_and_camera])
+#     boards = np.stack([feature.board for feature, _ in feature_and_camera])
+#     resolutions = np.stack([camera.resolution for _, camera in feature_and_camera])
+#
+#     f = jax.vmap(optimize_optax)
+#     optimized_params = f(
+#         jnp.array(cornerss), jnp.array(boards), jnp.array(resolutions), num_steps=10000
+#     )
+#
+#     params = [dict(zip(optimized_params, t)) for t in zip(*optimized_params.values())]
+#     return [
[…]

### 2023-05-22 calibration/benchmark/features.py

@@ -17,11 +17,14 @@ class Features:
     corners: np.ndarray
 
 
+SIMUL_INP = tuple[Projector, Features | None]
+BABELCALIB_INP = tuple[Entry, Features | None]
+
+
 # TODO: Add noise
-def _process_projector(
-    projector_board: tuple[Projector, np.ndarray]
-) -> tuple[Features | None, Projector]:
-    p, board = projector_board
+def _simul_features(args: tuple[dict, np.ndarray]) -> SIMUL_INP:
+    kwargs, board = args
+    p = Projector(**kwargs)
     with contextlib.suppress(ValueError):
         corners = p.project(board)
         out_of_img = ((corners < 0) | (corners > p.camera.resolution)).any(axis=1)
@@ -29,31 +32,19 @@ def _process_projector(
         corners = corners[~out_of_img]
 
         if corners.size != 0 and not np.isinf(corners).any():
-            return Features(board_, corners), p
+            return (p, Features(board_, corners))
 
-    return None, p
-
-
-def _get_Projector(kwargs: dict) -> Projector:
-    return Projector(**kwargs)
+    return (p, None)
 
 
-def simul_features(
-    n: int, board: np.ndarray, kwargs: dict
-) -> list[tuple[Features | None, Projector]]:
-    projectors = process_map(
-        _get_Projector,
-        (kwargs for _ in range(n)),
+def simul_features(n: int, board: np.ndarray, kwargs: dict) -> list[SIMUL_INP]:
+    # TODO: try partial
+    return process_map(
+        _simul_features,
+        ((kwargs, board) for _ in range(n)),
         chunksize=100,
         leave=False,
         total=n,
-        desc="Generating projectors",
-    )
-    return process_map(
-        _process_projector,
-        [(p, board) for p in projectors],
-        chunksize=100,
-        leave=False,
         desc="Simulating",
     )
 
@@ -90,9 +81,8 @@ def _process_ds(ds: Dataset) -> list[Features | None]:
 
 
 # TODO: Add ds, subds and image index name
-def babelcalib_features(datasets: list[Dataset]) -> list[tuple[Features | None, Entry]]:
+def babelcalib_features(datasets: list[Dataset]) -> list[BABELCALIB_INP]:
     results = process_map(_process_ds, datasets, leave=False, desc="Process dataset")
     results = [r for res in results for r in res]
-
     entries = (e for ds in datasets for subds in (ds.train, ds.test) for e in subds)
-    return list(zip(results, entries))
+    return list(zip(entries, results))

### 2023-05-22 calibration/solver/closed_form.py

@@ -1,82 +1,0 @@
-import numpy as np
-
-
-def orthonormality_closed_form(r_11, r_12, r_21, r_22):
-    return [
-        1 / 2 * r_11**2
-        - 1 / 2 * r_12**2
-        + 1 / 2 * r_21**2
-        - 1 / 2 * r_22**2
-        + 1
-        / 2
-        * np.sqrt(
-            r_11**4
-            + 2 * r_11**2 * r_12**2
-            + r_12**4
-            + 2 * r_11**2 * r_21**2
-            - 2 * r_12**2 * r_21**2
-            + r_21**4
-            + 8 * r_11 * r_12 * r_21 * r_22
-            - 2 * r_11**2 * r_22**2
-            + 2 * r_12**2 * r_22**2
-            + 2 * r_21**2 * r_22**2
-            + r_22**4
-        ),
-        1 / 2 * r_11**2
-        - 1 / 2 * r_12**2
-        + 1 / 2 * r_21**2
-        - 1 / 2 * r_22**2
-        + 1
-        / 2
-        * np.sqrt(
-            r_11**4
-            + 2 * r_11**2 * r_12**2
-            + r_12**4
-            + 2 * r_11**2 * r_21**2
-            - 2 * r_12**2 * r_21**2
-            + r_21**4
-            + 8 * r_11 * r_12 * r_21 * r_22
-            - 2 * r_11**2 * r_22**2
-            + 2 * r_12**2 * r_22**2
-            + 2 * r_21**2 * r_22**2
-            + r_22**4
-        ),
-        1 / 2 * r_11**2
-        - 1 / 2 * r_12**2
-        + 1 / 2 * r_21**2
-        - 1 / 2 * r_22**2
-        - 1
-        / 2
-        * np.sqrt(
-            r_11**4
-            + 2 * r_11**2 * r_12**2
-            + r_12**4
-            + 2 * r_11**2 * r_21**2
-            - 2 * r_12**2 * r_21**2
-            + r_21**4
-            + 8 * r_11 * r_12 * r_21 * r_22
-            - 2 * r_11**2 * r_22**2
-            + 2 * r_12**2 * r_22**2
-            + 2 * r_21**2 * r_22**2
-            + r_22**4
-        ),
-        1 / 2 * r_11**2
-        - 1 / 2 * r_12**2
-        + 1 / 2 * r_21**2
-        - 1 / 2 * r_22**2
-        - 1
-        / 2
-        * np.sqrt(
[…]

### 2023-05-22 calibration/solver/extrinsics.py

@@ -1,83 +1,0 @@
-import numpy as np
-from scipy.linalg import svd
-
-
-def solve_extrinsic(x: np.ndarray, X: np.ndarray) -> list[np.ndarray]:
-    """
-    Computes the extrinsic parameters of a camera, given the 2D image points and
-    the 3D world points.
-
-    Args:
-        x (np.ndarray): Points in image space, with shape (n, 2),
-            where n is the number of points and each point is represented as [x, y].
-        X (np.ndarray): Points in the board space, with shape (n, 2),
-            where n is the number of points and each point is represented as [x, y].
-        image_center (tuple[float, float]): A tuple representing the
-            image center coordinates (x, y).
-
-    Returns:
-        np.ndarray: A 3x3 array representing the extrinsic parameters of the camera."""
-    M = np.vstack(
-        [[-v * X_, -v * Y_, u * X_, u * Y_, -v, u] for (u, v), (X_, Y_) in zip(x, X)]
-    )
-
-    # _, _, V = np.linalg.svd(M, full_matrices=False)
-    _, _, V = svd(M, full_matrices=False)
-    assert isinstance(V, np.ndarray)
-    H = V.T[:, -1]
-    r_11, r_12, r_21, r_22, t_1, t_2 = H
-
-    AA = (r_11 * r_12 + r_21 * r_22) ** 2
-    BB = r_11**2 + r_21**2
-    CC = r_12**2 + r_22**2
-
-    # TODO: Use resolution
-    r_32_2 = np.roots([1, CC - BB, -AA])
-    r_32_2 = r_32_2[(r_32_2 >= 0) & (r_32_2 <= 1000)]
-
-    # r_32_2_closed_form = [
-    #     r for r in orthonormality_closed_form(r_11, r_12, r_21, r_22)
-    #     if 0 <= r <= 1000
-    # ]
-    #
-    # assert np.allclose(r_32_2, r_32_2_closed_form)
-    assert len(r_32_2) != 0
-
-    r_31, r_32 = [], []
-    for r_32_2_ in r_32_2:
-        for sg in [-1, 1]:
-            r_32_ = sg * np.sqrt(r_32_2_)
-            r_32.append(r_32_)
-            if np.isclose(r_32_, 0):
-                # r_31 += [np.sqrt(CC - BB), -np.sqrt(CC - BB)]
-                r_31 += [np.sqrt(abs(CC - BB)), -np.sqrt(abs(CC - BB))]
[…]

### 2023-05-22 calibration/solver/intrinsics.py

@@ -1,51 +1,0 @@
-import numpy as np
-
-
-def solve_intrinsic(
-    x: np.ndarray, X: np.ndarray, p: np.ndarray
-) -> tuple[np.ndarray, np.ndarray]:
-    """
-    Computes the intrinsic parameters of a camera, given the 2D image points,
-    the 3D world points, and the extrinsic parameters.
-
-    Args:
-        x (np.ndarray): Points in image space, with shape (n, 2),
-            where n is the number of points and each point is represented as [x, y].
-        X (np.ndarray): Points in the board space, with shape (n, 2),
-            where n is the number of points and each point is represented as [x, y].
-        p (np.ndarray): A 3x3 array representing the extrinsic parameters of the camera.
-
-    Returns:
-        tuple[np.ndarray, np.ndarray]: A tuple containing the intrinsic parameters
-            (lambdas) and the updated extrinsic parameters (H)
-            with the third translation component (t_3).
-    """
-    r_11, r_12, t_1, r_21, r_22, t_2, r_31, r_32, _ = p.flatten()
-
-    N = 2
-    A_vec = r_21 * X[:, 0] + r_22 * X[:, 1] + t_2
-    C_vec = r_11 * X[:, 0] + r_12 * X[:, 1] + t_1
-    B_vec = x[:, 1] * (r_31 * X[:, 0] + r_32 * X[:, 1])
-    D_vec = x[:, 0] * (r_31 * X[:, 0] + r_32 * X[:, 1])
-
-    A_C_vec = np.r_[A_vec, C_vec]
-
-    p_vals = np.linalg.norm(x[:, :2], axis=1)
-    p_vals = np.tile(p_vals, 2)
-    # p_vals = p_vals[:, np.newaxis] ** (2 * np.arange(1, N + 1)[np.newaxis, :])
-    p_vals = np.c_[p_vals**2, p_vals**4]
-
-    A_C_p_mat = A_C_vec[:, None] * p_vals
-
-    # Change it if we have multiple images
-    v_u_mat = np.r_[-x[:, 1], -x[:, 0]]
-
-    M = np.c_[A_C_p_mat, v_u_mat]
-
-    B_D_vec = np.r_[B_vec, D_vec]
-    B_D_vec -= A_C_vec
-
-    # a_t = np.linalg.lstsq(M, B_D_vec, rcond=None)[0]
-    a_t = np.linalg.pinv(M) @ B_D_vec
-
-    return a_t[:N], a_t[N]

### 2023-05-22 calibration/solver/test_solver.py

@@ -1,81 +1,0 @@
-import unittest
-from itertools import product
-
-import numpy as np
-from scipy.spatial.transform import Rotation
-from tqdm.auto import tqdm
-
-from calibration.projector.board import gen_charuco_grid, gen_checkerboard_grid
-from calibration.projector.camera import Camera
-from calibration.projector.projector import Projector
-from calibration.solver.solve import solve
-
-
-class TestProjectorAndSolver(unittest.TestCase):
-    def test_proj_equal_backproj(self):
-        Rs = [
-            np.eye(3),
-            Rotation.from_euler("xyz", [5, 5, 5], degrees=True).as_matrix(),
-            Rotation.from_euler("xyz", [-5, 3, 5], degrees=True).as_matrix(),
-            Rotation.from_euler("xyz", [0, 0, 90], degrees=True).as_matrix(),
-            # Rotation.from_euler("xyz", [0, 0, 180], degrees=True).as_matrix(),
-        ]
-        lambdass = [
-            np.array([l1, l2])
-            for l1 in np.arange(-5.0, 1.1, 2)
-            for l2 in np.arange(
-                -2.61752136752137 * l1 - 6.85141810943093,
-                -2.61752136752137 * l1 - 4.39190876941320,
-                1.0,
-            )
-        ]
-        cameras = [
-            Camera(),
-            Camera(135.0, np.array([40, 30]), np.array([1920, 1080]), 1.0),
-        ]
-        ts_for_cameras = [
-            list(map(np.array, product([-1.0, 0.0], [-0.7, -0.3], [3.0, 4.0]))),
-            list(map(np.array, product([-1.7, -0.8], [-1.2, -0.8], [20.0]))),
-        ]
-        boards = [gen_checkerboard_grid(7, 9), gen_charuco_grid(7, 9, 0.4, 0.2)]
-
-        def f(R, t, lambdas, camera, board):
-            with self.subTest(R=R, t=t, lambdas=lambdas, camera=camera):
-                self.assertEqual(board.dtype, np.float64)
-                proj = Projector(R=R, t=t, lambdas=lambdas, camera=camera)
-                x = proj.project(board)
-
-                self.assertTrue((x > 0).all())
-                self.assertTrue((x < proj.camera.resolution).all())
-
-                X_ = proj.backproject(x)
-                np.testing.assert_allclose(X_, board, atol=1e-10, rtol=1e-6)
-
-                proj_ = solve(x, board, camera)
[…]

### 2023-05-22 main.py

@@ -14,7 +14,7 @@ from calibration.feature_detector.visualization import show_boards
 
 def run_benchmark():
     if not os.path.isfile("simul_results.pkl"):
-        simul_results = benchmark_simul(int(1e5))
+        simul_results = benchmark_simul(int(1e3))
         with open("simul_results.pkl", "wb") as f:
             pkl.dump(simul_results, f)
     if not os.path.isfile("babelcalib_results.pkl"):
@@ -34,8 +34,7 @@ def run_corner_refinement():
         assert isinstance(r.input, Entry)
         assert r.input.image is not None
         assert r.features is not None
-    show_boards(np.array(r.input.image), r.features.corners,
-                r.features.board).show()
+    show_boards(np.array(r.input.image), r.features.corners, r.features.board).show()
 
 
 if __name__ == "__main__":

### 2023-05-23 calibration/solver/optimization/solve.py
Add an additional solver

@@ -1,0 +1,72 @@
+import optax
+import jax.numpy as jnp
+import numpy as np
+import jax
+from calibration.projector.camera import Camera
+from calibration.projector.projector import Projector
+from calibration.solver.optimization.backproject import backprojection_loss
+from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+
+
+# @partial(jax.jit, static_argnames=("step_size", "num_steps"))
+def optimize_optax(
+    corners: jax.Array,
+    board: jax.Array,
+    resolution: jax.Array,
+    step_size=0.01,
+    # num_steps=100000,
+    num_steps=1000,
+) -> dict[str, jax.Array]:
+    params = {
+        "theta": jnp.array([1.0, 1.0, 1.0]),
+        "t": jnp.array([1.0, 1.0, 1.0]),
+        "lambdas": jnp.array([-1.0, -1.0]),
+        "focal_length": jnp.array([35.0]),
+        "sensor_size": jnp.array([36.0, 24.0]),
+    }
+
+    # Create an Adam optimizer
+    optimizer = optax.adam(step_size)
+
+    # Initialize the optimizer state.
+    opt_state = optimizer.init(params)
+
+    # Define a function to compute the gradient and update the parameters
+    @jax.jit
+    def step(params, opt_state):
+        loss_value, grads = jax.value_and_grad(backprojection_loss)(
+            params, corners, board, resolution
+        )
+        updates, opt_state = optimizer.update(grads, opt_state, params)
+        params = optax.apply_updates(params, updates)
+        return params, opt_state, loss_value
+
+    # Run the optimization loop
+    params, opt_state, _ = jax.lax.fori_loop(
+        0, num_steps, lambda _, x: step(*x[:2]), (params, opt_state, 0.0)
+    )
+
+    assert isinstance(params, dict)
+    return params
+
+
+def solve(corners: np.ndarray, board: np.ndarray, camera: Camera) -> Projector:
+    resolution = camera.resolution
+    params = optimize_optax(
+        jnp.array(corners), jnp.array(board), jnp.array(resolution), num_steps=10000
+    )
+    params = {k: np.array(v) for k, v in params.items()}
+
+    camera = Camera(
+        focal_length=int(params["focal_length"]),
+        sensor_size=params["sensor_size"],
+        resolution=np.array(resolution),
+    )
+
+    del params["focal_length"]
+    del params["sensor_size"]
+
[…]

### 2023-05-23 calibration/solver/scaramuzza/extrinsics.py

@@ -1,0 +1,83 @@
+import numpy as np
+from scipy.linalg import svd
+
+
+def solve_extrinsic(x: np.ndarray, X: np.ndarray) -> list[np.ndarray]:
+    """
+    Computes the extrinsic parameters of a camera, given the 2D image points and
+    the 3D world points.
+
+    Args:
+        x (np.ndarray): Points in image space, with shape (n, 2),
+            where n is the number of points and each point is represented as [x, y].
+        X (np.ndarray): Points in the board space, with shape (n, 2),
+            where n is the number of points and each point is represented as [x, y].
+        image_center (tuple[float, float]): A tuple representing the
+            image center coordinates (x, y).
+
+    Returns:
+        np.ndarray: A 3x3 array representing the extrinsic parameters of the camera."""
+    M = np.vstack(
+        [[-v * X_, -v * Y_, u * X_, u * Y_, -v, u] for (u, v), (X_, Y_) in zip(x, X)]
+    )
+
+    # _, _, V = np.linalg.svd(M, full_matrices=False)
+    _, _, V = svd(M, full_matrices=False)
+    assert isinstance(V, np.ndarray)
+    H = V.T[:, -1]
+    r_11, r_12, r_21, r_22, t_1, t_2 = H
+
+    AA = (r_11 * r_12 + r_21 * r_22) ** 2
+    BB = r_11**2 + r_21**2
+    CC = r_12**2 + r_22**2
+
+    # TODO: Use resolution
+    r_32_2 = np.roots([1, CC - BB, -AA])
+    r_32_2 = r_32_2[(r_32_2 >= 0) & (r_32_2 <= 1000)]
+
+    # r_32_2_closed_form = [
+    #     r for r in orthonormality_closed_form(r_11, r_12, r_21, r_22)
+    #     if 0 <= r <= 1000
+    # ]
+    #
+    # assert np.allclose(r_32_2, r_32_2_closed_form)
+    assert len(r_32_2) != 0
+
+    r_31, r_32 = [], []
+    for r_32_2_ in r_32_2:
+        for sg in [-1, 1]:
+            r_32_ = sg * np.sqrt(r_32_2_)
+            r_32.append(r_32_)
+            if np.isclose(r_32_, 0):
+                # r_31 += [np.sqrt(CC - BB), -np.sqrt(CC - BB)]
+                r_31 += [np.sqrt(abs(CC - BB)), -np.sqrt(abs(CC - BB))]
[…]

### 2023-05-23 calibration/solver/test_solvers.py

@@ -1,0 +1,90 @@
+import unittest
+from itertools import product
+
+import numpy as np
+from scipy.spatial.transform import Rotation
+from tqdm.auto import tqdm
+
+from calibration.projector.board import gen_charuco_grid, gen_checkerboard_grid
+from calibration.projector.camera import Camera
+from calibration.projector.projector import Projector
+from .optimization import solve as solve_optimization
+from .scaramuzza import solve as solve_scaramuzza
+
+
+class TestProjectorAndSolverOptimization(unittest.TestCase):
+    def test_proj_equal_backproj(self):
+        Rs = [
+            np.eye(3),
+            Rotation.from_euler("xyz", [5, 5, 5], degrees=True).as_matrix(),
+            Rotation.from_euler("xyz", [-5, 3, 5], degrees=True).as_matrix(),
+            Rotation.from_euler("xyz", [0, 0, 90], degrees=True).as_matrix(),
+            # Rotation.from_euler("xyz", [0, 0, 180], degrees=True).as_matrix(),
+        ]
+        lambdass = [
+            np.array([l1, l2])
+            for l1 in np.arange(-5.0, 1.1, 2)
+            for l2 in np.arange(
+                -2.61752136752137 * l1 - 6.85141810943093,
+                -2.61752136752137 * l1 - 4.39190876941320,
+                1.0,
+            )
+        ]
+        cameras = [
+            Camera(),
+            Camera(135.0, np.array([40, 30]), np.array([1920, 1080]), 1.0),
+        ]
+        ts_for_cameras = [
+            list(map(np.array, product([-1.0, 0.0], [-0.7, -0.3], [3.0, 4.0]))),
+            list(map(np.array, product([-1.7, -0.8], [-1.2, -0.8], [20.0]))),
+        ]
+        boards = [gen_checkerboard_grid(7, 9), gen_charuco_grid(7, 9, 0.4, 0.2)]
+
+        def f(R, t, lambdas, camera, board, solve, solve_name):
+            with self.subTest(
+                R=R, t=t, lambdas=lambdas, camera=camera, solve_name=solve_name
+            ):
+                self.assertEqual(board.dtype, np.float64)
+                proj = Projector(R=R, t=t, lambdas=lambdas, camera=camera)
+                x = proj.project(board)
+
+                self.assertTrue((x > 0).all())
+                self.assertTrue((x < proj.camera.resolution).all())
+
+                X_ = proj.backproject(x)
[…]

### 2023-05-23 calibration/feature_refiner/classifier.py
Add corner detection function to classifier

@@ -1,0 +1,39 @@
+from calibration.benchmark.benchmark import BenchmarkResult
+import numpy as np
+from PIL import ImageOps
+from calibration.data.babelcalib.entry import Entry
+from calibration.feature_detector.checkerboard import detect_corners
+
+
+def get_corner_responses(r: BenchmarkResult):
+    assert isinstance(r.input, Entry)
+    assert r.input.image is not None
+    assert r.features is not None
+    cornerness = detect_corners(np.array(ImageOps.grayscale(r.input.image)))
+
+    corners = r.features.corners.astype(int)
+
+    # Preparing output array
+    outputs = []
+
+    # Padding image to handle edge cases
+    pad_image = np.pad(cornerness, ((5, 5), (5, 5)), mode="constant")
+
+    # Shifting corners because of padding
+    corners += 5
+
+    # Iterate over corners
+    for corner in corners:
+        x, y = corner
+        # Get 11x11 window around corner
+        window = pad_image[y - 5 : y + 6, x - 5 : x + 6].flatten()
+        # Get distances to the corner
+        yy, xx = np.mgrid[-5:6, -5:6]
+        distances = np.hypot(xx, yy).flatten()
+        # Get corner_id
+        # ids = np.full(distances.shape, idx)
+        # Stack arrays
+        output = np.column_stack((window, distances))
+        outputs.append(output)
+
+    return np.concatenate(outputs)

### 2023-05-24 paper/Chapters/Chapter1.tex
Updates for the paper

@@
 methods
-\cite{olsonAprilTagRobustFlexible2011}
+\cite{olsonAprilTagRobustFlexible2011a}
 \cite{schopsWhyHaving102020} \cite{krogiusFlexibleLayoutsFiducial2019}
@@
 detection is performed on the undistorted image.
+% \todo{Probably remove the emphasis on TartanCalib, if I am not going to compare
+% with it}
 
-Instead of searching for the features on the undistorted image, it is possible to
-use conjugate translations \cite{schaffalitzkyGeometricGroupingRepeated1998},
-to predict the position of the previously undetected feature points and to
-further, constrain the camera calibration.
-\textcite{prittsMinimalSolversRectifying2021} showed that three pairs of points,
-related by the same translations on the scene plane are sufficient to estimate
-the camera calibration and the parameters of the conjugate translations.
+Instead of searching for the features on the undistorted image from scratch, it
+is possible to utilize the prior knowledge of the geometry of the calibration
+board, effectively predicting the possible positions of previously undetected
+features. It can be done by projecting the board onto the image using the
+intermediate camera calibration, and then filtering the possible positions in
+order to eliminate false positives.
 
-We want to use the work of \textcite{prittsMinimalSolversRectifying2021} to bootstrap
-the camera calibration, and then use the found conjugate translations and camera
-parameters to iteratively predict and refine the positions of the calibration
-board features, calibration parameters, and conjugate translations.
+This additional points will further constrain the camera calibration, improving
+the accuracy of the calibration parameters.
+\todo{Explain why more features is better}
+\missingfigure{Show the example of the calibration board and the image}
 

### 2023-05-24 paper/Chapters/Chapter2.tex
Updates for the paper

\chapter{Related work}\label{cha:related_work}

\section{Camera calibration}\label{sub:camera_calibration}

Getting the correspondence between the spatial
and the image coordinates requires camera calibration. Camera
calibration consists of the geometric camera model and the parameters of this
model. That information makes it possible to obtain the 2d image coordinates
of any point in the 3d space.

Usually, the geometric camera model is obtained from the domain knowledge of the
researcher or the camera manufacturer. Often, they choose the simplified model as
a trade-off between accuracy and complexity. The model's parameters are usually
obtained by solving the constrained optimization problem, given the set of
points with known geometry.

\section{Calibration boards}\label{sub:calibration_boards}

To achieve a robust calibration, images with repeating patterns are
usually used. The camera
calibration parameters can be found using prior knowledge of the properties of the pattern, such that the pattern invariants hold on
the image. Initially, the chessboard~\citep{OpenCVCameraCalibration, v.douskosAutomaticCalibrationDigital2007} patterns were used
(Fig.~\ref{fig:chessboard}).

Later, ArUco
~\cite{garrido-juradoAutomaticGenerationDetection2014} allowed detecting the
orientation of the pattern, as well as uniquely identifying each located pattern
even under occlusion (Fig. \ref{fig:gboriginal}). Based on ArUco,
ChArUcO~\cite{OpenCVCameraCalibration} (Fig.~\ref{fig:charuco}) and
AprilTag~\cite{olsonAprilTagRobustFlexible2011a} (Fig.~\ref{fig:apriltag}) were
proposed as more robust.

\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[width=\linewidth]{chessboard.png}
\caption{Chessboard~\cite{OpenCVCameraCalibration}}
\label{fig:chessboard}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[width=\linewidth]{gboriginal.png}
\caption{ArUco board~\cite{OpenCVDetectionArUco}}
\label{fig:gboriginal}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[width=\linewidth]{charuco.png}
\caption{Charuco board~\cite{OpenCVDetectionChArUco}}
\label{fig:charuco}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[width=\linewidth]{apriltag.png}
  \caption{AprilTag board~\cite{rosebrockAprilTagPython2020} (right)}
\label{fig:apriltag}
\end{subfigure}
\caption{Calibration boards.}
\end{figure}

\section{Camera models}\label{sub:camera_models}

The camera model's choice depends on the camera's physical properties
and the accuracy required. Usually, the parametric models are simpler to use, as
they have only a few parameters and deliver good accuracy. 
The most common are the Double Sphere
model~\cite{usenkoDoubleSphereCamera2018}, the Kannala-Brandt
model~\cite{kannalaGenericCameraModel2006}, and the Field-of-View
model~\cite{devernayStraightLinesHave2001}.
In the ill-posed problem of camera calibration, the common choice
of the camera model is the division
model~\cite{fitzgibbonSimultaneousLinearEstimation2001}.
However, \textcite{schopsWhyHaving102020} show that they tend to have
significantly higher errors than the non-parametric (general) models.
The \textcite{lochmanBabelCalibUniversalApproach2021} suggested a framework for
converting the parameters of a powerful back-projection
\cite{zhangFlexibleNewTechnique2000} model to recover different models' parameters.

\section{Camera parameters estimation}\label{sub:camera_parameters_estimation}

Camera calibration using repeating patterns was an important subject for a long
time, for example, \textcite{schaffalitzkyGeometricGroupingRepeated1998} in
\citeyear{schaffalitzkyGeometricGroupingRepeated1998} and
\textcite{zhangFlexibleNewTechnique2000}.

% Camera calibration is a crucial step for many computer vision tasks,
% hence many methods were proposed to solve this problem (e.g.,
% ~\cite{brownCloseRangeCameraCalibration1971},
% ~\cite{heikkilaFourstepCameraCalibration1997},
% ~\cite{fitzgibbonSimultaneousLinearEstimation2001},
% ~\cite{sturmGenericConceptCamera2004},
% ~\cite{clausRationalFunctionLens2005},
% ~\cite{meiSingleViewPoint2007},
% ~\cite{ramalingamUnifyingModelCamera2017}).

Nevertheless, camera calibration is still an open problem; recently,
multiple new approaches have arisen. 
\textcite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
to camera calibration, with a separate step of converting between camera models.
\textcite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
\textcite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
approach to camera calibration, which outperforms the previous state-of-the-art
approaches for wide-angle cameras.

% The camera calibration depends a lot on the physical camera properties, choice
% of the camera model, calibration method, number of images used for calibration,
% prior knowledge of the camera, and many other variables. Therefore, currently,
% there is no established method of general camera calibration approach
% comparison, and the state-of-the-art is not well-defined. However, it is possible
% to compare the methods in the context of specific tasks and datasets.

### 2023-05-24 paper/paper.tex
Paper updates
Updates for the paper

@@
 
-\usepackage{todonotes}
-
 %----------------------------------------------------------------------------------------
@@
 }
+
+\usepackage[textwidth=20mm]{todonotes}
+\setlength{\marginparwidth}{2.5cm}
+\usepackage{caption}
+\usepackage{subcaption}
+\graphicspath{ {images/} }
 
@@
 
-\begin{declaration}
-	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
-	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
-
-	\begin{itemize}
-		\item This work was done wholly or mainly while in candidature for a research degree at this University.
-		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
-		\item Where I have consulted the published work of others, this is always clearly attributed.
-		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
-		\item I have acknowledged all main sources of help.
-		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
-	\end{itemize}
-
-	\noindent Signed:\\
-	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
-
-	\noindent Date:\\
-	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
-\end{declaration}
-
-\cleardoublepage
+% \begin{declaration}
+% 	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
+% 	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
+%
+% 	\begin{itemize}
+% 		\item This work was done wholly or mainly while in candidature for a research degree at this University.
+% 		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
+% 		\item Where I have consulted the published work of others, this is always clearly attributed.
+% 		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
+% 		\item I have acknowledged all main sources of help.
+% 		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
+% 	\end{itemize}
+%
+% 	\noindent Signed:\\
+% 	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
+%
+% 	\noindent Date:\\
+% 	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
+% \end{declaration}
+%
+% \cleardoublepage
+\todo{Enable}
 
@@
 
-\vspace*{0.2\textheight}
-
-\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
-
-\hfill Dave Barry
+% \vspace*{0.2\textheight}
+%
+% \noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
+%
+% \hfill Dave Barry
+\todo{Enable}
 
@@
 
-	% Camera calibration is a crucial step in many computer vision applications.
-	% However, despite the constant development of solutions, they still tend to
-	% be sensitive to the noise of the input data, bad lightning conditions,
-	% occlusions and other problems, especially under the conditions of
-	% high distortion, such as mobile phones and GoPro-type cameras.
-	%
+	Camera calibration is a crucial step in many computer vision applications.
+  Typically, it involves taking a set of images of a calibration pattern,
+  detecting its' features, and estimating the camera parameters. However, under
+  certain conditions (including occlusions, bad lightning, highly distorted
+  images etc.), feature detectors might fail to detect some of the
+  features.\todo{Do I have to justify it?}.
+
+  In this paper, we propose a novel approach to feature detection in the context
+  of camera calibration. After the initial feature detection and calibration,
+  we use the intermediate camera parameters to predict the possible positions
+  of the previously undetected features. Those features are filtered using the
+  binary classifier, and the remaining features are used to further constrain
+  the camera calibration.
+
 	% In this paper, we propose a novel approach to camera calibration. We want to
@@
 
-\begin{acknowledgements}
-	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
-	The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
-
-	\noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
-\end{acknowledgements}
+% \begin{acknowledgements}
+% 	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
+% 	The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
+%
+% 	\noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
+% \end{acknowledgements}
+\todo{Enable}
 
@@
 
-\tableofcontents % Prints the main table of contents
-
-\listoffigures % Prints the list of figures
-
-\listoftables % Prints the list of tables
+% \tableofcontents % Prints the main table of contents
+\todo{Enable}
+%
+% \listoffigures % Prints the list of figures
+\todo{Enable}
+%
+% \listoftables % Prints the list of tables
+\todo{Enable}
 
@@
 
-\dedicatory{For/Dedicated to/To my\ldots}
+% \dedicatory{For/Dedicated to/To my\ldots}
+\todo{Enable}
 
@@
 \include{Chapters/Chapter1}
-%\include{Chapters/Chapter2} 
-%\include{Chapters/Chapter3}
-%\include{Chapters/Chapter4} 
-%\include{Chapters/Chapter5}
+\include{Chapters/Chapter2} 
+\include{Chapters/Chapter3}
+\include{Chapters/Chapter4} 
+\include{Chapters/Chapter5} 
+\include{Chapters/Chapter6}
 

### 2023-05-24 calibration/benchmark/calib.py
Try to use the Gauss-Newton method

@@ -1,6 +1,7 @@
 from functools import partial
 from typing import Callable
 import numpy as np
+from tqdm.auto import tqdm
 from tqdm.contrib.concurrent import process_map
 
 from calibration.projector.camera import Camera
@@ -9,19 +10,20 @@ from calibration.projector.projector import Projector
 from .features import Features
 
 
-_SOLVER = Callable[[np.ndarray, np.ndarray, Camera], Projector]
+_SOLVER = Callable[[np.ndarray, np.ndarray, Camera], Projector | None]
 
 
 def _calibrate_helper(
-    arg: tuple[Features , Camera], solvers: list[tuple[str, _SOLVER]]
+    arg: tuple[Features, Camera] | None, solvers: list[tuple[str, _SOLVER]]
 ) -> dict[str, Projector]:
     if arg is None:
         return {}
     features, camera = arg
-    return features and {
+    ret = {
         solver_name: solver(features.corners, features.board, camera)
         for solver_name, solver in solvers
     }
+    return {k: v for k, v in ret.items() if v is not None}
 
 
 def calibrate(
@@ -36,3 +38,6 @@ def calibrate(
         leave=False,
         desc="Calibrating",
     )
+    # return list(
+    #     map(partial(_calibrate_helper, solvers=solvers), tqdm(feature_and_camera))
+    # )

### 2023-05-24 calibration/solver/optimization/solve.py

@@ -1,4 +1,5 @@
-import optax
+# import optax
+from jaxopt import GaussNewton
 import jax.numpy as jnp
 import numpy as np
 import jax
@@ -9,13 +10,52 @@ from calibration.solver.optimization.rotation import euler_angles_to_rotation_ma
 
 
 # @partial(jax.jit, static_argnames=("step_size", "num_steps"))
-def optimize_optax(
+# def optimize_optax(
+#     corners: jax.Array,
+#     board: jax.Array,
+#     resolution: jax.Array,
+#     step_size=0.01,
+#     num_steps=100000,
+#     # num_steps=10000,
+# ) -> dict[str, jax.Array]:
+#     params = {
+#         "theta": jnp.array([1.0, 1.0, 1.0]),
+#         "t": jnp.array([1.0, 1.0, 1.0]),
+#         "lambdas": jnp.array([-1.0, -1.0]),
+#         "focal_length": jnp.array([35.0]),
+#         "sensor_size": jnp.array([36.0, 24.0]),
+#     }
+#
+#     # Create an Adam optimizer
+#     optimizer = optax.adam(step_size)
+#
+#     # Initialize the optimizer state.
+#     opt_state = optimizer.init(params)
+#
+#     # Define a function to compute the gradient and update the parameters
+#     @jax.jit
+#     def step(params, opt_state):
+#         loss_value, grads = jax.value_and_grad(backprojection_loss)(
+#             params, corners, board, resolution
+#         )
+#         updates, opt_state = optimizer.update(grads, opt_state, params)
+#         params = optax.apply_updates(params, updates)
+#         return params, opt_state, loss_value
+#
+#     # Run the optimization loop
+#     params, opt_state, _ = jax.lax.fori_loop(
+#         0, num_steps, lambda _, x: step(*x[:2]), (params, opt_state, 0.0)
+#     )
+#
+#     assert isinstance(params, dict)
+#     return params
+
+
+def optimize_gauss_newton(
     corners: jax.Array,
     board: jax.Array,
     resolution: jax.Array,
-    step_size=0.01,
     # num_steps=100000,
-    num_steps=10000,
 ) -> dict[str, jax.Array]:
     params = {
         "theta": jnp.array([1.0, 1.0, 1.0]),
@@ -25,37 +65,29 @@ def optimize_optax(
         "sensor_size": jnp.array([36.0, 24.0]),
     }
 
-    # Create an Adam optimizer
-    optimizer = optax.adam(step_size)
[…]

### 2023-05-24 main.py

@@ -1,4 +1,5 @@
 import pickle as pkl
+import numpy as np
 
 from pandas.compat import os
 
@@ -6,17 +7,153 @@ from calibration.benchmark.benchmark import (
     benchmark_babelcalib,
     benchmark_simul,
 )
+from calibration.projector.camera import Camera
+from calibration.solver.optimization.solve import solve
 
 
 def run_benchmark():
-    if not os.path.isfile("simul_results.pkl"):
-        simul_results = benchmark_simul(int(1e2))
-        with open("simul_results.pkl", "wb") as f:
-            pkl.dump(simul_results, f)
     if not os.path.isfile("babelcalib_results.pkl"):
         babelcalib_results = benchmark_babelcalib()
         with open("babelcalib_results.pkl", "wb") as f:
             pkl.dump(babelcalib_results, f)
+    if not os.path.isfile("simul_results.pkl"):
+        simul_results = benchmark_simul(int(1e3))
+        with open("simul_results.pkl", "wb") as f:
+            pkl.dump(simul_results, f)
+
+def debug_test():
+    corners = np.array([[558.33307563, 504.842542  ],
+       [531.8274827 , 522.49001733],
+       [504.42809411, 540.51581882],
+       [476.34149001, 558.75704413],
+       [447.82010119, 577.02480587],
+       [419.15285163, 595.11314233],
+       [390.64922842, 612.81203692],
+       [362.61840085, 629.92284786],
+       [335.34685326, 646.27333435],
+       [511.35216838, 490.38560834],
+       [484.99160889, 506.90884558],
+       [458.0405242 , 523.70718971],
+       [430.71995865, 540.63305707],
+       [403.28141178, 557.52216574],
+       [375.99454313, 574.20216615],
+       [349.13086666, 590.50354641],
+       [322.94579252, 606.27114647],
+       [297.66215734, 621.37421239],
+       [467.90381902, 476.37056393],
+       [442.09937817, 491.83708643],
+       [415.98158061, 507.49873814],
+       [389.76798898, 523.22565067],
+       [363.69171421, 538.87843524],
+       [337.98886031, 554.31565875],
+       [312.88443081, 569.40226451],
+       [288.57889546, 584.01762736],
+       [265.23760915, 598.06193028],
+       [428.23202111, 463.00519502],
+       [403.29432905, 477.50043595],
+       [378.27868642, 492.13125218],
[…]

### 2023-05-24 paper/Chapters/Chapter1.tex
OMG it's horrible

@@
 methods
-\cite{olsonAprilTagRobustFlexible2011a}
-\cite{schopsWhyHaving102020} \cite{krogiusFlexibleLayoutsFiducial2019}
+\citep{olsonAprilTagRobustFlexible2011a, schopsWhyHaving102020,
+krogiusFlexibleLayoutsFiducial2019}
 fail on images with high distortion.
-\textcite{duisterhofTartanCalibIterativeWideAngle2022} suggested an iterative
+\cite{duisterhofTartanCalibIterativeWideAngle2022} suggested an iterative
 the approach of image undistortion and target reprojection, achieving the superior
@@
 
+\section{Research objective}\label{sec:research_objective}
+
+The objective of this research is to improve the accuracy of the camera
+calibration by finding previously undetected features on the calibration
+board \todo{Probably rephrase if I won't compare the actual calibration}. For
+that, we formulate the set of research questions:
+\begin{itemize}
+  \item How to find additional features on the calibration board which were not
+    detected by the feature detector?
+  \item How to filter out falsely detected features?
+    \todo{Add more}
+\end{itemize}
+
 \section{Thesis structure}\label{sec:thesis_structure}

### 2023-05-24 paper/Chapters/Chapter2.tex
OMG it's horrible

@@
 usually used. The camera
-calibration parameters can be found using prior knowledge of the properties of the pattern, such that the pattern invariants hold on
-the image. Initially, the chessboard~\citep{OpenCVCameraCalibration, v.douskosAutomaticCalibrationDigital2007} patterns were used
-(Fig.~\ref{fig:chessboard}).
+calibration parameters can be found using prior knowledge of the properties of
+the pattern, such that the pattern invariants hold on
+the image. Initially, the chessboard~\citep{OpenCVCameraCalibration,
+v.douskosAutomaticCalibrationDigital2007} patterns were used
+(\cref{fig:chessboard}).
 
 Later, ArUco
-~\cite{garrido-juradoAutomaticGenerationDetection2014} allowed detecting the
+~\citep{garrido-juradoAutomaticGenerationDetection2014} (\cref{fig:gboriginal}) and
+AprilTag~\citep{olsonAprilTagRobustFlexible2011a} (\cref{fig:apriltag})
+allowed detecting the
 orientation of the pattern, as well as uniquely identifying each located pattern
-even under occlusion (Fig. \ref{fig:gboriginal}). Based on ArUco,
-ChArUcO~\cite{OpenCVCameraCalibration} (Fig.~\ref{fig:charuco}) and
-AprilTag~\cite{olsonAprilTagRobustFlexible2011a} (Fig.~\ref{fig:apriltag}) were
+even under occlusion. Based on ArUco,
+ChArUcO~\citep{OpenCVCameraCalibration} (\cref{fig:charuco}) was
 proposed as more robust.
@@
 
-The camera model's choice depends on the camera's physical properties
+The choice of the camera model depends on the camera's physical properties
 and the accuracy required. Usually, the parametric models are simpler to use, as
@@
 The most common are the Double Sphere
-model~\cite{usenkoDoubleSphereCamera2018}, the Kannala-Brandt
-model~\cite{kannalaGenericCameraModel2006}, and the Field-of-View
-model~\cite{devernayStraightLinesHave2001}.
+model~\citep{usenkoDoubleSphereCamera2018}, the Kannala-Brandt
+model~\citep{kannalaGenericCameraModel2006}, and the Field-of-View
+model~\citep{devernayStraightLinesHave2001}.
 In the ill-posed problem of camera calibration, the common choice
 of the camera model is the division
-model~\cite{fitzgibbonSimultaneousLinearEstimation2001}.
-However, \textcite{schopsWhyHaving102020} show that they tend to have
+model~\citep{fitzgibbonSimultaneousLinearEstimation2001}.
+However, \cite{schopsWhyHaving102020} shows that they tend to have
 significantly higher errors than the non-parametric (general) models.
-The \textcite{lochmanBabelCalibUniversalApproach2021} suggested a framework for
+The \cite{lochmanBabelCalibUniversalApproach2021} suggested a framework for
 converting the parameters of a powerful back-projection
@@
 Camera calibration using repeating patterns was an important subject for a long
-time, for example, \textcite{schaffalitzkyGeometricGroupingRepeated1998} in
+time, for example, \cite{schaffalitzkyGeometricGroupingRepeated1998} in
 \citeyear{schaffalitzkyGeometricGroupingRepeated1998} and
-\textcite{zhangFlexibleNewTechnique2000}.
+\cite{zhangFlexibleNewTechnique2000}.
 
@@
 multiple new approaches have arisen.
-\textcite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
+\cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
 to camera calibration, with a separate step of converting between camera models.
-\textcite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
+\cite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
 Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
-\textcite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
+\cite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
 approach to camera calibration, which outperforms the previous state-of-the-art
 approaches for wide-angle cameras.
+
+\todo{Add the paper about the feature detection}
 

### 2023-05-24 paper/Chapters/Chapter4.tex
OMG it's horrible

\chapter{Approach}\label{cha:approach}

\section{Feature detection}\label{sec:feature_detection}

\section{Classifier}\label{sec:classifier}

### 2023-05-25 calibration/benchmark/benchmark.py
Optimize calibration solver with Adam

@@ -6,7 +6,6 @@ from tqdm.contrib.concurrent import process_map
 
 from calibration.benchmark.calib import calibrate
 
-# from calibration.benchmark.calib import calibrate_optimization, calibrate_scaramuzza
 from calibration.benchmark.features import (
     BABELCALIB_INP,
     SIMUL_INP,

### 2023-05-25 calibration/solver/optimization/solve.py

@@ -1,5 +1,5 @@
-# import optax
-from jaxopt import GaussNewton
+import optax
+
 import jax.numpy as jnp
 import numpy as np
 import jax
@@ -10,52 +10,13 @@ from calibration.solver.optimization.rotation import euler_angles_to_rotation_ma
 
 
 # @partial(jax.jit, static_argnames=("step_size", "num_steps"))
-# def optimize_optax(
-#     corners: jax.Array,
-#     board: jax.Array,
-#     resolution: jax.Array,
-#     step_size=0.01,
-#     num_steps=100000,
-#     # num_steps=10000,
-# ) -> dict[str, jax.Array]:
-#     params = {
-#         "theta": jnp.array([1.0, 1.0, 1.0]),
-#         "t": jnp.array([1.0, 1.0, 1.0]),
-#         "lambdas": jnp.array([-1.0, -1.0]),
-#         "focal_length": jnp.array([35.0]),
-#         "sensor_size": jnp.array([36.0, 24.0]),
-#     }
-#
-#     # Create an Adam optimizer
-#     optimizer = optax.adam(step_size)
-#
-#     # Initialize the optimizer state.
-#     opt_state = optimizer.init(params)
-#
-#     # Define a function to compute the gradient and update the parameters
-#     @jax.jit
-#     def step(params, opt_state):
-#         loss_value, grads = jax.value_and_grad(backprojection_loss)(
-#             params, corners, board, resolution
-#         )
-#         updates, opt_state = optimizer.update(grads, opt_state, params)
-#         params = optax.apply_updates(params, updates)
-#         return params, opt_state, loss_value
-#
-#     # Run the optimization loop
-#     params, opt_state, _ = jax.lax.fori_loop(
-#         0, num_steps, lambda _, x: step(*x[:2]), (params, opt_state, 0.0)
-#     )
-#
-#     assert isinstance(params, dict)
-#     return params
-
-
-def optimize_gauss_newton(
+def optimize_optax(
     corners: jax.Array,
     board: jax.Array,
     resolution: jax.Array,
-    # num_steps=100000,
+    step_size=0.01,
+    num_steps=30000,
+    # num_steps=10000,
 ) -> dict[str, jax.Array]:
     params = {
         "theta": jnp.array([1.0, 1.0, 1.0]),
@@ -65,25 +26,41 @@ def optimize_gauss_newton(
         "sensor_size": jnp.array([36.0, 24.0]),
     }
 
-    # Define a function to compute the residuals
-    def residuals(params):
[…]

### 2023-05-25 main.py

@@ -7,8 +7,6 @@ from calibration.benchmark.benchmark import (
     benchmark_babelcalib,
     benchmark_simul,
 )
-from calibration.projector.camera import Camera
-from calibration.solver.optimization.solve import solve
 
 
 def run_benchmark():
@@ -20,140 +18,6 @@ def run_benchmark():
         simul_results = benchmark_simul(int(1e3))
         with open("simul_results.pkl", "wb") as f:
             pkl.dump(simul_results, f)
-
-def debug_test():
-    corners = np.array([[558.33307563, 504.842542  ],
-       [531.8274827 , 522.49001733],
-       [504.42809411, 540.51581882],
-       [476.34149001, 558.75704413],
-       [447.82010119, 577.02480587],
-       [419.15285163, 595.11314233],
-       [390.64922842, 612.81203692],
-       [362.61840085, 629.92284786],
-       [335.34685326, 646.27333435],
-       [511.35216838, 490.38560834],
-       [484.99160889, 506.90884558],
-       [458.0405242 , 523.70718971],
-       [430.71995865, 540.63305707],
-       [403.28141178, 557.52216574],
-       [375.99454313, 574.20216615],
-       [349.13086666, 590.50354641],
-       [322.94579252, 606.27114647],
-       [297.66215734, 621.37421239],
-       [467.90381902, 476.37056393],
-       [442.09937817, 491.83708643],
-       [415.98158061, 507.49873814],
-       [389.76798898, 523.22565067],
-       [363.69171421, 538.87843524],
-       [337.98886031, 554.31565875],
-       [312.88443081, 569.40226451],
-       [288.57889546, 584.01762736],
-       [265.23760915, 598.06193028],
-       [428.23202111, 463.00519502],
-       [403.29432905, 477.50043595],
-       [378.27868642, 492.13125218],
-       [353.38568573, 506.78572495],
-       [328.81933963, 521.34742067],
-       [304.77617481, 535.7013782 ],
-       [281.4345261 , 549.74025258],
-       [258.94561842, 563.36972239],
-       [237.42765814, 576.51241424],
-       [392.36489229, 450.42483391],
-       [368.50390718, 464.04033855],
-       [344.75165555, 477.74831004],
-       [321.28381983, 491.45354107],
-       [298.27112056, 505.05949276],
-       [275.87090854, 518.47284479],
-       [254.21984799, 531.60782414],
-       [233.42862867, 544.38975996],
[…]

### 2023-05-25 paper/Chapters/Chapter4.tex
Update the paper

@@
 
+\section{Camera calibration}\label{sec:camera_calibration}
+
+\subsection{Reprojection error}\label{sub:reprojection_error}
+
+The reprojection error is the distance between the reprojected point and the
+measured one. It is used to evaluate the quality of the camera calibration.
+
+We chose to minimize the reprojection error between the board and back-projected
+corners, which were initially detected. The projection and back-projection are
+the inverse of each other, hence minimizing the error between the projection of
+the board and the detected corners and minimizing the error between the
+back-projection of the detected corners and the board are
+equivalent\todo{Doesn't sound very rigorous to me.}.
+
+Let's define the following variables: \(\boldsymbol{\theta} = \begin{pmatrix}
+	\theta_x, \theta_y, \theta_z
+\end{pmatrix}^{T}\) is the vector of Euler rotation angles, \(\mathbf{t} = \begin{pmatrix}
+	t_x, t_y, t_z
+\end{pmatrix}^{T}\) is the translation vector, \(\boldsymbol{\lambda} = \begin{pmatrix}
+	\lambda_1, \lambda_2
+\end{pmatrix}^{T}\)\todo{Justify why we used 2} is the intrinsic parameters vector, \(\) is the focal
+length, and \(\mathbf{s} = \begin{pmatrix}
+	s_x, s_y
+\end{pmatrix}^{T}\) is the sensor size\todo{Make sure I'm using the correct terms.}.
+From the input image, we know the resolution \(\mathbf{r} = \begin{pmatrix}
+	r_x, r_y
+\end{pmatrix}^{T}\).
+From the rotation vector, we can compute the rotation matrix \(\mathbf{R}\) as:
+
+From \(\boldsymbol{\theta}\), the rotation matrix $R$ can be calculated as follows:
+
+\begin{equation}
+	R = R(\theta_x) R(\theta_y) R(\theta_z)
+\end{equation} \todo{Is the notation ok?}
+
+where
+
+\begin{align}
+	% R_x(\phi)   & =
+	% \begin{bmatrix}
+	% 	1 & 0          & 0           \\
+	% 	0 & \cos(\phi) & -\sin(\phi) \\
+	% 	0 & \sin(\phi) & \cos(\phi)
+	% \end{bmatrix} \\
+	% R_y(\theta) & =
+	% \begin{bmatrix}
+	% 	\cos(\theta)  & 0 & \sin(\theta) \\
+	% 	0             & 1 & 0            \\
+	% 	-\sin(\theta) & 0 & \cos(\theta)
+	% \end{bmatrix}                 \\
+	% R_z(\psi)   & =
+	% \begin{bmatrix}
+	% 	\cos(\psi) & -\sin(\psi) & 0 \\
+	% 	\sin(\psi) & \cos(\psi)  & 0 \\
+	% 	0          & 0           & 1
+	% \end{bmatrix}
+	R(\theta_x) & =
+	\begin{bmatrix}
+		1 & 0              & 0               \\
+		0 & \cos(\theta_x) & -\sin(\theta_x) \\
+		0 & \sin(\theta_x) & \cos(\theta_x)
+	\end{bmatrix} \\
+	R(\theta_y) & =
+	\begin{bmatrix}
+		\cos(\theta_y)  & 0 & \sin(\theta_y) \\
+		0               & 1 & 0              \\
+		-\sin(\theta_y) & 0 & \cos(\theta_y)
+	\end{bmatrix}     \\
+	R(\theta_z) & =
+	\begin{bmatrix}
+		\cos(\theta_z) & -\sin(\theta_z) & 0 \\
+		\sin(\theta_z) & \cos(\theta_z)  & 0 \\
+		0              & 0               & 1
+	\end{bmatrix}
+\end{align}
+
+Then, \(H\) is given by:
+\begin{equation}
+	H = \begin{bmatrix}
+		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
+	\end{bmatrix}.
+\end{equation}
+
+We can compute the intrinsic camera matrices as follows:
+\begin{equation}
+	K = \begin{pmatrix}
+		\frac{f r_x}{s_x} & 0                 & \frac{r_x}{2} \\
+		0                 & \frac{f r_y}{s_y} & \frac{r_y}{2} \\
+		0                 & 0                 & 1
+	\end{pmatrix},
+\end{equation}.
+
+Then, the back-projection of a 2D point \(\mathbf{u} = \begin{pmatrix}
+	u, v, 1
+\end{pmatrix}\) into a scene point with \(Z = 0\) \(\mathbf{X} = \begin{pmatrix}
+	X, Y, 1
+\end{pmatrix}\) is given by:
+\begin{equation}
+	\mathbf{X} = H g_{\lambda_1, \lambda_2}(K^{-1} \mathbf{u}).
+\end{equation}
+
+\subsection{Optimization}\label{sub:optimization}
+
+The loss function is the sum of the squared reprojection errors between the board and
+the back-projected corners, which were initially detected:
+\begin{equation}
+	L = \sum_{i=1}^{N} \left\lVert
+	H g_{\lambda_1, \lambda_2}(K^{-1} \mathbf{u_i}) -
+	\mathbf{X_i} \right\rVert^2.
+\end{equation}
+
+For the initial guess, we used the randomly chosen constant small values.
+
+The model converged to the same results compared to the initial parameters, set
+using the Scaramuzza solver, unless the initial guess was very degenerate (i.e.
+\(R\) was such that the board plane passed through the principal point, and all
+backprojected points were projected onto the same line).
+
+This issue also occured with random small initial values, due to the best
+approximation for \(R\) which minimizes \(L\) when the distance from the
+back-projected board from the measure one was high (i.e., the \(t\) was far from
+the true value) being the degenerate solution\todo{Am I using the term
+correctly?}. In order to avoid this issue, we first optimized only the \(t\),
+until the loss function converged, meaning that \(t\) is close to the true
+value.
+
+However, another issue was that when the board was rotated close to the
+\(180^{\circ}\), \(R\) once again converged to the degenerate solution. In order
+to avoid this issue, we found the solution with initial \(\theta_z\) set to
+value, close to \(0^{\circ}\) and \(180^{\circ}\), and then used the solution
+which minimized the loss function.
+
+\missingfigure{Show the distribution of the reprojection error}.
+
+\section{Feature detection}\label{sec:feature_detection}
+
+Often, not all of the board's corners were detected initially. Firstly, we
+assumed that the whole board was detected, and imputed the missing points in the
+board space.\todo{Add ref to the figure}. Then, we tried extending the board
+points.
+
+\missingfigure{Show the image, the respective board, and the imputed points}
+
+We used the obtained camera parameters to then project the imputed board points
+into the image space.
+
 \section{Classifier}\label{sec:classifier}
+
+Given the possible positions of the previously undetected corners, we used a
+classifier, proposed by \cite{geigerAutomaticCameraRange2012}.
+By convolving the image with the templates of the board corners\todo{I have to
+reference it from the related work section}, we obtained the
+probability\todo{It's not probability} of
+each pixel being a corner.\todo{Also, explain in details + math how it's done}
+
+The original paper then used a number of checks to further prune the detected
+corners, and extending line by line the initial board, formed from the
+random close points which made a square \todo{Make sure that's accurate, and
+reference. Also, the sentence is too compicated}.
+We did not require that, since we already had the board, and we directly used
+the response map to find the corners.
+
+\missingfigure{Show the map of responses, and the detected corners}
+
+To create a training dataset, we collected the true and false positives from the
+corners we already had:
+
+For each of the detected corners on all images, we collected the values of the
+response function at the previously detected corners, and around them.
+We didn't collect the values of all of the pixels, because then we would have
+got too optimistic values for selecting the true positives\todo{Rephrase}.
+
+\missingfigure{Show the distribution of the response function}
+
+We trained a binary classifier, using the collected data, and then used it to
+detect the true corners.

### 2023-05-25 paper/Chapters/Chapter5.tex
Update the paper

\chapter{Experiments}\label{cha:experiments}

\section{Simulator}\label{sec:simulator}

We created a symulator to generate distorted points. We used it to test the
solver, and test the correctness of projection and back-projection points.

\section{Metrics}\label{sec:metrics}

\begin{itemize}
	\item Reprojection error
	\item Number of detected corners
\end{itemize}

\section{Dataset}\label{sec:dataset}

For the project, we need highly distorted photos of calibration boards. It takes
a lot of work to generate such a dataset, as cameras which produce such images are
usually expensive. Therefore, it would be preferable to use an existing dataset.

\textcite{lochmanBabelCalibUniversalApproach2021} collected a wide number of
datasets, typically used in the field for the benchmarking of the camera
calibration. They're provided in a Deltille \cite{DeltilleDetector2023} format,
and are well documented:

\textbf{Kalibr} contains several established datasets that are commonly used for testing
the accuracy of camera calibration frameworks: Double Sphere
\cite{usenkoDoubleSphereCamera2018}, EuRoC \cite{burriEuRoCMicroAerial2016}, TUM
VI \cite{schubertTUMVIBenchmark2018}, and ENTANIYA 1
\cite{Calibration250degFisheye}.
The Kalibr calibration framework was used in the
original publications cited above, hence the name of the dataset.
As a calibration pattern, AprilGrid with 6x6 tags of 88 mm size was used.
In total, the datasets contain approximately 800 images.

\textbf{OCamCalib} \cite{scaramuzzaFlexibleTechniqueAccurate2006} is a dataset
of approximately 300 images.
As a calibration pattern, the checkerboard pattern of different sizes was used.

\textbf{UZH} \cite{AreWeReady} is a dataset of approximately 800 images
collected using the following cameras:
As a calibration pattern, AprilGrid with 4x5 tags of 75 mm size was used.
The dataset contains approximately 800 images.

\textbf{OV} \cite{duisterhofTartanCalibIterativeWideAngle2022} is a dataset of
approximately 1400 images. It was collected using eight stereo cameras.
As a calibration pattern, the checkerboard pattern with 9x6 tags of 22 mm size
was used.

\textcite{duisterhofTartanCalibIterativeWideAngle2022} also provide their
dataset from the TartanCalib project, but it is quite challenging to use it as it
comes in the Robot Operating System (ROS) .bag format.

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{Kalibr.png}
		\caption{Kalibr}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{OCamCalib.png}
		\caption{OCamCalib}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{OV.png}
		\caption{OV}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{UZH.png}
		\caption{UZH}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\linewidth}
		\includegraphics[width=\linewidth]{tartancalib.png}
		\caption{TartanCalib}
	\end{subfigure}
	\caption{Images from the datasets}
\end{figure}

\todo{Probably, remove everything but BabelCalib, as we didn't use AprilGrid}

### 2023-05-26 calibration/solver/optimization/solve.py
Refactor solve() function to use theta instead of th

@@ -23,10 +23,10 @@ def params_to_proj(jparams: dict[str, jArr], resolution: nArr) -> Projector | No
         int(jparams["focal_length"]), params["sensor_size"], np.array(resolution)
     )
 
-    th = jnp.concatenate([jparams["th_x"], jparams["th_y"], jparams["th_z"]])
-    params["R"] = np.array(euler_angles_to_rotation_matrix(th))
+    theta = jnp.concatenate([jparams["theta_x"], jparams["theta_y"], jparams["theta_z"]])
+    params["R"] = np.array(euler_angles_to_rotation_matrix(theta))
 
-    for p in ["focal_length", "sensor_size", "th_x", "th_y", "th_z"]:
+    for p in ["focal_length", "sensor_size", "theta_x", "theta_y", "theta_z"]:
         del params[p]
 
     return Projector(**params, camera=camera)
@@ -39,15 +39,15 @@ def optimize_optax(
     board: jArr,
     resolution: jArr,
     # step_size=0.05,
-    step_size=0.01,
+    step_size=0.001,
     patience=100,
 ) -> dict[str, jArr]:
-    # optimizer = optax.rmsprop(step_size)
-    optimizer = optax.adam(step_size)
+    optimizer = optax.rmsprop(step_size)
+    # optimizer = optax.adam(step_size)
     start_optimizing_during_phase = [
         ["t"],
-        ["th_z"],
-        ["th_x", "th_y"],
+        ["theta_z"],
+        ["theta_x", "theta_y"],
         ["lambdas", "focal_length", "sensor_size"],
     ]
     phase_when_optimize = {
@@ -78,14 +78,14 @@ def optimize_optax(
             updates, _ = phases[phase].update(updates, inits[phase])
         params_ = optax.apply_updates(params, updates)
 
-        jax.lax.cond(
-            i % 1000 == 0,
-            lambda _: jax.debug.print(
-                "iteration: {}, loss {}, phase: {}", i, loss_val, phase
-            ),
-            lambda _: None,
-            None,
-        )
+        # jax.lax.cond(
+        #     i % 1000 == 0,
+        #     lambda _: jax.debug.print(
+        #         "iteration: {}, loss {}, phase: {}", i, loss_val, phase
+        #     ),
+        #     lambda _: None,
+        #     None,
+        # )
 
         # Update the loss history
         loss_history = loss_history.at[i % patience].set(loss_val)
[…]

### 2023-05-27 calibration/benchmark/benchmark.py
Updates

@@ -22,9 +22,14 @@ from calibration.solver.scaramuzza.solve import solve as solve_scaramuzza
 def evaluate(
     inp: list[SIMUL_INP] | list[BABELCALIB_INP], projs: list[dict[str, Projector]]
 ) -> list[BenchmarkResult]:
-    args = [(i, f, p) for (i, f), p in zip(inp, projs) if f is not None]
     return process_map(
-        BenchmarkResult, *args, chunksize=100, leave=False, desc="Evaluating"
+        BenchmarkResult,
+        [i for i, _ in inp],
+        [f for _, f in inp],
+        projs,
+        chunksize=100,
+        leave=False,
+        desc="Evaluating",
     )
 
 

### 2023-05-27 calibration/benchmark/features.py

@@ -27,7 +27,7 @@ def _simul_features(args: tuple[dict, np.ndarray]) -> SIMUL_INP:
     p = Projector(**kwargs)
     with contextlib.suppress(ValueError):
         corners = p.project(board)
-        out_of_img = ((corners < 0) | (corners > p.camera.resolution)).any(axis=1)
+        out_of_img = ((corners < 0) | (corners >= p.camera.resolution)).any(axis=1)
         board_ = board[~out_of_img]
         corners = corners[~out_of_img]
 

### 2023-05-27 calibration/feature_refiner/classifier.py

@@ -5,13 +5,27 @@ from calibration.feature_detector.checkerboard import detect_corners
 
 
 def prune_corners(
-        corners: np.ndarray, mask: np.ndarray, image: Image, thr:float
+    corners: np.ndarray, mask: np.ndarray, image: Image, thr: float
 ) -> tuple[np.ndarray, np.ndarray]:
     cornerness = detect_corners(np.array(ImageOps.grayscale(image)))
+
     corners = corners.astype(int)[mask]
-    responses = cornerness[corners[:, 1], corners[:, 0]]
-    # Now mask is an array of 0 and 1
     mask = mask.astype(int)
+
+    out_of_img = ((corners < 0) | (corners >= image.size)).any(axis=1).astype(int)
+    # Now mask is an array of 0, 1 and 3
+    mask[mask == 1] = 1 + out_of_img * 2
+    corners = corners[out_of_img == 0]
+
+    responses = cornerness[corners[:, 1], corners[:, 0]]
+
+    # Now mask is an array of 0 and 1
     # Now, if responces > thr, mask is 2, otherwise 1. 0s are unchanged
-    mask[mask==1] = (responses > thr).astype(int) + 1
+    mask[mask == 1] = (responses > thr).astype(int) + 1
+
+    # Mask:
+    # 0 - unchanged
+    # 1 - filtered out
+    # 2 - new corner
+    # 3 - out of image
     return responses, mask

### 2023-05-27 calibration/feature_refiner/refine.py

@@ -33,8 +33,8 @@ def view1D(a, b):  # a, b are arrays
 
 
 def refine_features_single(
-    r: BenchmarkResult, solver_name: str = "Optimization", pan_size: int = 1, thr=13.8
-) -> RefinedResult:
+    r: BenchmarkResult, solver_name: str, pan_size: int = 1, thr=13.8
+) -> RefinedResult | None:
     assert isinstance(r.input, Entry) and r.input.image is not None
     board = r.features.board.astype(int)
     x_min, x_max, y_min, y_max = (
@@ -52,7 +52,10 @@ def refine_features_single(
     mask = np.isin(A, B, invert=True)
 
     proj = r.predictions[solver_name]
-    new_corners = proj.project(new_board)
+    try:
+        new_corners = proj.project(new_board)
+    except ValueError:
+        return None
     responses, new_mask = prune_corners(new_corners, mask, r.input.image, thr)
     return RefinedResult(
         r.input, r.features, Features(new_board, new_corners), responses, new_mask, proj
@@ -60,12 +63,12 @@ def refine_features_single(
 
 
 def refine_features(
-    results: list[BenchmarkResult], solver_name: str, pan_size: int = 1
-) -> list[RefinedResult]:
+    results: list[BenchmarkResult], solver_name: str = "Optimization", pan_size: int = 1
+) -> list[RefinedResult|None]:
     return process_map(
         partial(refine_features_single, solver_name=solver_name, pan_size=pan_size),
         results,
-        chunksize=100,
+        chunksize=10,
         leave=False,
         desc="Refining features",
     )

### 2023-05-27 calibration/solver/optimization/solve.py

@@ -1,5 +1,4 @@
 from functools import partial
-import plotly.express as px
 import optax
 
 import jax.numpy as jnp
@@ -23,7 +22,9 @@ def params_to_proj(jparams: dict[str, jArr], resolution: nArr) -> Projector | No
         int(jparams["focal_length"]), params["sensor_size"], np.array(resolution)
     )
 
-    theta = jnp.concatenate([jparams["theta_x"], jparams["theta_y"], jparams["theta_z"]])
+    theta = jnp.concatenate(
+        [jparams["theta_x"], jparams["theta_y"], jparams["theta_z"]]
+    )
     params["R"] = np.array(euler_angles_to_rotation_matrix(theta))
 
     for p in ["focal_length", "sensor_size", "theta_x", "theta_y", "theta_z"]:

### 2023-05-27 main.py

@@ -8,7 +8,9 @@ from calibration.benchmark.benchmark import (
     benchmark_babelcalib,
     benchmark_simul,
 )
+from calibration.data.babelcalib.babelcalib import load_babelcalib
 from calibration.data.babelcalib.entry import Entry
+from calibration.feature_refiner.refine import refine_features
 from calibration.projector.camera import Camera
 from calibration.solver.optimization.solve import solve
 
@@ -18,6 +20,11 @@ def run_benchmark():
         babelcalib_results = benchmark_babelcalib()
         with open("babelcalib_results.pkl", "wb") as f:
             pkl.dump(babelcalib_results, f)
+        # with open("babelcalib_results_old.pkl", "rb") as f:
+        #     babelcalib_results = pkl.load(f)
+        refined_babelcalib_results = refine_features(babelcalib_results)
+        with open("refined_babelcalib_results.pkl", "wb") as f:
+            pkl.dump(refined_babelcalib_results, f)
     if not os.path.isfile("simul_results.pkl"):
         simul_results = benchmark_simul(int(1e3))
         with open("simul_results.pkl", "wb") as f:
@@ -43,4 +50,4 @@ def run_corner_refinement():
 if __name__ == "__main__":
     # debug_test()
     run_benchmark()
-    run_corner_refinement()
+    # run_corner_refinement()

### 2023-05-27 paper/Chapters/Chapter2.tex
WIP

@@
 proposed as more robust.
+
+There are also other calibration patterns, some of which are not square (for
+example, Delitlle~\citep{haDeltilleGridsGeometric2017}).
 
@@
 % to compare the methods in the context of specific tasks and datasets.
+
+\section{Boards' features detection}\label{sec:boards_features_detection}
+
+The detection of the calibration board's features is a crucial step in the
+camera calibration pipeline. The detection accuracy directly affects the
+calibration accuracy. Besides the feature detection, it's also important to
+associate the detected features with the board's corners.
+
+There are various of the feature detection methods. Many of them require
+prior knowledge of the board's geometry, such as the number of rows and columns,
+and require the full visibility of the board. For example, the default OpenCV
+implementation of the chessboard detection~\citep{OpenCVCameraCalibration}.
+
+Because of that, other methods were proposed, such as
+\cite{fuersattelOCPADOccludedCheckerboard2016} and
+\cite{geigerAutomaticCameraRange2012}. Those method can detect the board under
+the partial occlusion and do not require prior knowledge of the board's geometry.

### 2023-05-27 calibration/feature_detector/visualization.py

@@ -15,7 +15,8 @@ def show_corners(
 
 
 # TODO: Pass lists of np.ndarray instead of Corner and Board
-def show_boards(img: np.ndarray, corners: np.ndarray, board: np.ndarray) -> go.Figure:
+def show_boards(img: np.ndarray, corners: np.ndarray, board: np.ndarray
+) -> go.Figure:
     fig1 = px.imshow(img, binary_string=True)
 
     points = [

### 2023-05-27 calibration/feature_refiner/classifier.py

@@ -10,6 +10,7 @@ def prune_corners(
     cornerness = detect_corners(np.array(ImageOps.grayscale(image)))
 
     corners = corners.astype(int)[mask]
+    # 0: original, 1: new
     mask = mask.astype(int)
 
     out_of_img = ((corners < 0) | (corners >= image.size)).any(axis=1).astype(int)

### 2023-05-27 calibration/feature_refiner/refine.py

@@ -16,12 +16,14 @@ class RefinedResult:
     features: Features
     refined_features: Features
     responses: np.ndarray
+    # Mask:
+    # 0 - unchanged
+    # 1 - filtered out
+    # 2 - new corner
+    # 3 - out of image
     new_board_mask: np.ndarray
     prediction: Projector
-    error: float = field(init=False)
-
-    def __post_init__(self):
-        self.error = calc_error(self.prediction, self.refined_features)
+    error: float
 
 
 # https://stackoverflow.com/a/45313353/ @Divakar
@@ -33,7 +35,7 @@ def view1D(a, b):  # a, b are arrays
 
 
 def refine_features_single(
-    r: BenchmarkResult, solver_name: str, pan_size: int = 1, thr=13.8
+    r: BenchmarkResult, solver_name: str="Optimization", pan_size: int = 1, thr=13.8
 ) -> RefinedResult | None:
     assert isinstance(r.input, Entry) and r.input.image is not None
     board = r.features.board.astype(int)
@@ -56,15 +58,25 @@ def refine_features_single(
         new_corners = proj.project(new_board)
     except ValueError:
         return None
+    print(new_corners.shape)
+    print(board.shape)
+    print(new_board.shape)
     responses, new_mask = prune_corners(new_corners, mask, r.input.image, thr)
+    print(new_corners.shape)
     return RefinedResult(
-        r.input, r.features, Features(new_board, new_corners), responses, new_mask, proj
+        r.input,
+        r.features,
+        Features(new_board, new_corners),
+        responses,
+        new_mask,
+        proj,
+        r.errors[solver_name],
     )
 
 
 def refine_features(
     results: list[BenchmarkResult], solver_name: str = "Optimization", pan_size: int = 1
-) -> list[RefinedResult|None]:
+) -> list[RefinedResult | None]:
     return process_map(
         partial(refine_features_single, solver_name=solver_name, pan_size=pan_size),
         results,

### 2023-05-27 calibration/feature_refiner/visualization.py

@@ -1,0 +1,45 @@
+import numpy as np
+import pandas as pd
+import plotly.express as px
+import plotly.graph_objects as go
+
+
+def show_refined_corners(
+    img: np.ndarray,
+    corners: np.ndarray,
+    board: np.ndarray,
+    mask: np.ndarray,
+    responses: np.ndarray,
+) -> go.Figure:
+    fig1 = px.imshow(img, binary_string=True)
+
+    mask_mapping = {
+        0: "unchanged",
+        1: "filtered out",
+        2: "new corner",
+        3: "out of image",
+    }
+
+    responses_all = np.full_like(mask, -1)
+    responses_all[(mask > 0) & (mask < 3)] = responses
+    points = [
+        {
+            "n": i,
+            "i": feature[0],
+            "j": feature[1],
+            "x": corner[0],
+            "y": corner[1],
+            "mask": mask_mapping[mask_v],
+            "resp": resp,
+        }
+        for i, (corner, feature, mask_v, resp) in enumerate(
+            zip(corners, board, mask, responses_all)
+        )
+    ]
+    df = pd.DataFrame(points)
+    fig2 = px.scatter(
+        # df, x="x", y="y", color="resp", symbol="mask", hover_data=["i", "j"]
+        df, x="x", y="y", color="mask", hover_data=["i", "j", "resp"]
+    )
+    assert isinstance(fig1.data, tuple) and isinstance(fig2.data, tuple)
+    return go.Figure(data=fig1.data+ fig2.data)

### 2023-05-27 calibration/solver/optimization/solve.py

@@ -4,10 +4,12 @@ import optax
 import jax.numpy as jnp
 import numpy as np
 import jax
+from scipy.spatial.transform import Rotation
 from calibration.projector.camera import Camera
 from calibration.projector.projector import Projector
 from calibration.solver.optimization.backproject import backprojection_loss
 from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+from calibration.solver.scaramuzza.solve import solve as solve_scaramuzza
 
 jArr = jax.Array
 nArr = np.ndarray
@@ -43,13 +45,16 @@ def optimize_optax(
     step_size=0.001,
     patience=100,
 ) -> dict[str, jArr]:
-    optimizer = optax.rmsprop(step_size)
-    # optimizer = optax.adam(step_size)
+    # optimizer = optax.rmsprop(step_size)
+    optimizer = optax.adam(step_size)
+    # start_optimizing_during_phase = [
+    #     ["t"],
+    #     ["theta_z"],
+    #     ["theta_x", "theta_y"],
+    #     ["lambdas", "focal_length", "sensor_size"],
+    # ]
     start_optimizing_during_phase = [
-        ["t"],
-        ["theta_z"],
-        ["theta_x", "theta_y"],
-        ["lambdas", "focal_length", "sensor_size"],
+        ["t", "theta_z", "theta_x", "theta_y", "lambdas", "focal_length", "sensor_size"]
     ]
     phase_when_optimize = {
         p: i for i, ps in enumerate(start_optimizing_during_phase) for p in ps
@@ -79,14 +84,14 @@ def optimize_optax(
             updates, _ = phases[phase].update(updates, inits[phase])
         params_ = optax.apply_updates(params, updates)
 
-        # jax.lax.cond(
-        #     i % 1000 == 0,
-        #     lambda _: jax.debug.print(
-        #         "iteration: {}, loss {}, phase: {}", i, loss_val, phase
-        #     ),
-        #     lambda _: None,
-        #     None,
-        # )
+        jax.lax.cond(
+            i % 1000 == 0,
+            lambda _: jax.debug.print(
+                "iteration: {}, loss {}, phase: {}", i, loss_val, phase
+            ),
+            lambda _: None,
+            None,
+        )
 
         # Update the loss history
         loss_history = loss_history.at[i % patience].set(loss_val)
[…]

### 2023-05-27 main.py

@@ -16,12 +16,12 @@ from calibration.solver.optimization.solve import solve
 
 
 def run_benchmark():
-    if not os.path.isfile("babelcalib_results.pkl"):
-        babelcalib_results = benchmark_babelcalib()
-        with open("babelcalib_results.pkl", "wb") as f:
-            pkl.dump(babelcalib_results, f)
-        # with open("babelcalib_results_old.pkl", "rb") as f:
-        #     babelcalib_results = pkl.load(f)
+    if True or not os.path.isfile("babelcalib_results.pkl"):
+        # babelcalib_results = benchmark_babelcalib()
+        # with open("babelcalib_results.pkl", "wb") as f:
+        #     pkl.dump(babelcalib_results, f)
+        with open("babelcalib_results.pkl", "rb") as f:
+            babelcalib_results = pkl.load(f)
         refined_babelcalib_results = refine_features(babelcalib_results)
         with open("refined_babelcalib_results.pkl", "wb") as f:
             pkl.dump(refined_babelcalib_results, f)

### 2023-05-27 calibration/feature_detector/checkerboard.py
Update the solver

@@ -1,7 +1,8 @@
 import numpy as np
+import cv2
 from scipy import signal
 
-# from scipy.spatial import cKDTree
+from scipy.spatial import cKDTree
 from numpy import pi
 
 # from scipy.cluster.vq import kmeans
@@ -118,53 +119,53 @@ def detect_corners(gray, radiuses=RADIUS):
     return out
 
 
-#
-# def get_corner_candidates(corr, step=40, thres=0.01):
-#     out = []
-#     check = set()
-#     for i in range(0, corr.shape[0], step//2):
-#         for j in range(0, corr.shape[1], step//2):
-#             region = corr[i:i+step, j:j+step]  # type: ignore
-#             ix = np.argmax(region)
-#             r, c = np.unravel_index(ix, region.shape)
-#             val = region[r, c]
-#             if val > thres and (r+i, c+j) not in check:
-#                 out.append( (r+i, c+j, val) )
-#                 check.add( (r+i, c+j) )
-#     return np.array(out)
-#
-# def non_maximum_suppression(corners, dist=40):
-#     tree = cKDTree(corners[:, :2])
-#     good = np.ones(len(corners), dtype='bool')
-#     for (a, b) in tree.query_pairs(dist):
-#         if not good[a] or not good[b]:
-#             continue
-#         sa = corners[a, 2]
-#         sb = corners[b, 2]
-#         if sa >= sb:
-#             good[b] = False
-#         else:
-#             good[a] = False
-#     return corners[good]
-#
-# def solve_patch_corner(dx, dy):
-#     matsum = np.zeros((2,2))
-#     pointsum = np.zeros(2)
-#     for i in range(dx.shape[0]):
-#         for j in range(dx.shape[1]):
-#             vec = [dy[i,j], dx[i,j]]
-#             pos = (i,j)
-#             mat = np.outer(vec, vec)
-#             pointsum += mat.dot(pos)
-#             matsum += mat
-#
-#     try:
-#         minv = np.linalg.inv(matsum)
-#     except np.linalg.LinAlgError:
-#         return None
-#
-#     newp = minv.dot(pointsum)
-#     return newp
+
+def get_corner_candidates(corr, step=40, thres=0.01):
+    out = []
+    check = set()
+    for i in range(0, corr.shape[0], step//2):
[…]

### 2023-05-27 calibration/feature_refiner/classifier.py

@@ -1,7 +1,104 @@
 import numpy as np
 from PIL import ImageOps
 from PIL.Image import Image
+from tqdm.auto import tqdm
 from calibration.feature_detector.checkerboard import detect_corners
+import cv2
+from sklearn.cluster import MeanShift, estimate_bandwidth
+import scipy.ndimage as ndi
+
+
+def find_modes_meanshift(hist):
+    # samples = np.array([[i] * int(v) for i, v in enumerate(hist)]).reshape(-1, 1)
+
+    hist = hist.astype(int)
+    samples = np.repeat(np.arange(len(hist)), hist).reshape(-1, 1)
+    bandwidth = estimate_bandwidth(samples, quantile=0.2, n_samples=500)
+    ms = MeanShift(bandwidth=bandwidth, bin_seeding=True).fit(samples)
+
+    # Retrieve unique labels and cluster centers
+    labels_unique = np.unique(ms.labels_)
+    cluster_centers = ms.cluster_centers_
+
+    modes = sorted(
+        [
+            (cluster_centers[k][0], np.mean(samples[ms.labels_ == k]))
+            for k in labels_unique
+        ],
+        key=lambda x: x[1],
+        reverse=True,
+    )
+
+    return modes
+
+
+def compute_orientation(img, positions, window_size):
+    def sobel_filters(img):
+        Kx = np.array([[-1, 0, 1], [-2, 0, 2], [-1, 0, 1]], np.float32)
+        Ky = np.array([[1, 2, 1], [0, 0, 0], [-1, -2, -1]], np.float32)
+
+        Ix = ndi.filters.convolve(img, Kx)
+        Iy = ndi.filters.convolve(img, Ky)
+
+        G = np.hypot(Ix, Iy)
+        G = G / G.max() * 255
+        theta = np.arctan2(Iy, Ix)
+
+        return (G, theta)
+
+    # G, theta = sobel_filters(img)
+    Ix = ndi.sobel(img.astype(int), axis=0)
+    Iy = ndi.sobel(img.astype(int), axis=1)
+    G = np.hypot(Ix, Iy)
+    G = G / G.max() * 255
+    theta = np.arctan2(Iy, Ix)
+    # import plotly.express as px
+    # px.imshow(G).show()
+    # px.imshow(theta).show()
+
+    # histogram_modes = []
+    passes = []
+    i = 0
+    for position in tqdm(positions):
+        i += 1
+        x, y = position
+        if (
+            x - window_size // 2 >= 0
[…]

### 2023-05-27 calibration/solver/optimization/backproject.py

@@ -68,4 +68,7 @@ def backprojection_loss(
     intrinsic_matrix = jnp.array([[fx, 0, cx], [0, fy, cy], [0, 0, 1]])
 
     board_ = backproject(corners, R, t, lambdas, intrinsic_matrix)
-    return jnp.mean(jnp.square(board_ - board))
+    weights = jnp.abs(corners / resolution - 0.5).mean(axis=1)**2
+    # weights /= jnp.square(resolution / 2)
+    return jnp.mean(jnp.abs(board_ - board) * (1 + weights * 10).reshape(-1, 1))
+    # return jnp.mean(jnp.square(board_ - board))

### 2023-05-27 calibration/solver/optimization/solve.py

@@ -41,21 +41,21 @@ def optimize_optax(
     corners: jArr,
     board: jArr,
     resolution: jArr,
-    # step_size=0.05,
+    # step_size=0.005,
     step_size=0.001,
     patience=100,
 ) -> dict[str, jArr]:
     # optimizer = optax.rmsprop(step_size)
     optimizer = optax.adam(step_size)
-    # start_optimizing_during_phase = [
-    #     ["t"],
-    #     ["theta_z"],
-    #     ["theta_x", "theta_y"],
-    #     ["lambdas", "focal_length", "sensor_size"],
-    # ]
     start_optimizing_during_phase = [
-        ["t", "theta_z", "theta_x", "theta_y", "lambdas", "focal_length", "sensor_size"]
+        ["t", "theta_z"],
+        ["theta_x", "theta_y"],
+        ["lambdas"],
+        ["focal_length", "sensor_size"],
     ]
+    # start_optimizing_during_phase = [
+    #     ["t", "theta_z", "theta_x", "theta_y", "lambdas", "focal_length", "sensor_size"]
+    # ]
     phase_when_optimize = {
         p: i for i, ps in enumerate(start_optimizing_during_phase) for p in ps
     }
@@ -135,7 +135,7 @@ def optimize_optax(
 
             phase += 1
             loss_history = jnp.full(patience, jnp.inf)
-            if phase > len(phases):
+            if phase >= len(phases):
                 break
 
         i += 1

### 2023-05-27 calibration/solver/optimization/backproject.py
Update solver

@@ -48,6 +48,7 @@ def backproject(
 def psi(lambdas: jax.Array, r: jax.Array) -> jax.Array:
     l1, l2 = lambdas
     return 1 + l1 * r**2 + l2 * r**4
+    # return 1 + l1 * r**2
 
 
 @jax.jit

### 2023-05-27 calibration/solver/optimization/solve.py

@@ -41,12 +41,14 @@ def optimize_optax(
     corners: jArr,
     board: jArr,
     resolution: jArr,
-    # step_size=0.005,
-    step_size=0.001,
+    # step_size=0.001,
+    step_size=0.005,
     patience=100,
 ) -> dict[str, jArr]:
     # optimizer = optax.rmsprop(step_size)
-    optimizer = optax.adam(step_size)
+    # optimizer = optax.adam(step_size)
+    optimizer = optax.amsgrad(step_size)
+
     start_optimizing_during_phase = [
         ["t", "theta_z"],
         ["theta_x", "theta_y"],
@@ -148,19 +150,22 @@ def solve(corners: nArr, board: nArr, camera: Camera) -> Projector | None:
     resolution = camera.resolution
     init_params = solve_scaramuzza(corners, board, camera)
     theta = Rotation.from_matrix(init_params.R).as_euler("xyz")
+    # init_params = {
+    # "theta_x": jnp.array([0.0]),
+    # "theta_y": jnp.array([0.0]),
+    # "theta_z": jnp.array([0.0]),
+    # "t": jnp.array([1.0, 1.0, 1.0]),
+    # "lambdas": jnp.array([0.0, 0.0]),
+    # "focal_length": jnp.array([35.0]),
+    # "sensor_size": jnp.array([36.0, 24.0]),
+    # }
     init_params = {
-        # "theta_x": jnp.array([0.0]),
-        # "theta_y": jnp.array([0.0]),
-        # "theta_z": jnp.array([th_z]),
-        # "t": jnp.array([1.0, 1.0, 1.0]),
-        # "lambdas": jnp.array([0.0, 0.0]),
-        # "focal_length": jnp.array([35.0]),
-        # "sensor_size": jnp.array([36.0, 24.0]),
         "theta_x": jnp.array([theta[0]]),
         "theta_y": jnp.array([theta[1]]),
         "theta_z": jnp.array([theta[2]]),
         "t": jnp.array(init_params.t),
         "lambdas": jnp.array(init_params.lambdas),
+        # "lambdas": jnp.array([init_params.lambdas[0], 0.]),
         "focal_length": jnp.array([camera.focal_length]),
         "sensor_size": jnp.array(camera.sensor_size),
     }

### 2023-05-27 calibration/benchmark/benchmark.py
Add augmentations

@@ -1,5 +1,6 @@
 import numpy as np
 from tqdm.contrib.concurrent import process_map
+from calibration.augmentations.augmentations import overlay_img, prune_corners
 from calibration.benchmark.benchmark_result import BenchmarkResult
 
 from calibration.benchmark.calib import calibrate
@@ -7,6 +8,7 @@ from calibration.benchmark.calib import calibrate
 from calibration.benchmark.features import (
     BABELCALIB_INP,
     SIMUL_INP,
+    Features,
     babelcalib_features,
     simul_features,
 )
@@ -56,7 +58,9 @@ def get_camera_from_entry(entry: Entry) -> Camera:
     )
 
 
-def benchmark_babelcalib(dataset: list[Dataset] | None = None) -> list[BenchmarkResult]:
+def benchmark_babelcalib(
+    dataset: list[Dataset] | None = None, aug: str | None = None
+) -> list[BenchmarkResult]:
     if dataset is None:
         dataset = load_babelcalib()
         # Skip aprilgrid
@@ -64,7 +68,17 @@ def benchmark_babelcalib(dataset: list[Dataset] | None = None) -> list[Benchmark
         dataset = [
             ds for ds in dataset if not any(map(ds.name.startswith, aprilgrid_datasets))
         ]
+    if aug == "overlay":
+        for ds in dataset:
+            for subds in [ds.train, ds.test]:
+                for e in subds:
+                    if e.image is not None:
+                        e.image = overlay_img(e.image)
     ents_and_feats = babelcalib_features(dataset)
+    if aug == "prune_corners":
+        ents_and_feats = [
+            (e, prune_corners(f) if f is not None else None) for e, f in ents_and_feats
+        ]
     solvers_args = [
         (f, get_camera_from_entry(e)) if f else None for e, f in ents_and_feats
     ]

### 2023-05-27 main.py

@@ -16,15 +16,18 @@ from calibration.solver.optimization.solve import solve
 
 
 def run_benchmark():
-    if True or not os.path.isfile("babelcalib_results.pkl"):
-        # babelcalib_results = benchmark_babelcalib()
-        # with open("babelcalib_results.pkl", "wb") as f:
-        #     pkl.dump(babelcalib_results, f)
-        with open("babelcalib_results.pkl", "rb") as f:
-            babelcalib_results = pkl.load(f)
-        refined_babelcalib_results = refine_features(babelcalib_results)
-        with open("refined_babelcalib_results.pkl", "wb") as f:
-            pkl.dump(refined_babelcalib_results, f)
+    for aug in [None, "overlay", "prune_corners"]:
+        path = f"babelcalib_results_{aug}.pkl"
+        if True or not os.path.isfile(path):
+            babelcalib_results = benchmark_babelcalib(aug=aug)
+
+            with open(path, "wb") as f:
+                pkl.dump(babelcalib_results, f)
+            # with open(path, "rb") as f:
+            #     babelcalib_results = pkl.load(f)
+            refined_babelcalib_results = refine_features(babelcalib_results)
+            with open(f"refined_babelcalib_results_{aug}.pkl", "wb") as f:
+                pkl.dump(refined_babelcalib_results, f)
     if not os.path.isfile("simul_results.pkl"):
         simul_results = benchmark_simul(int(1e3))
         with open("simul_results.pkl", "wb") as f:
@@ -42,8 +45,11 @@ def run_corner_refinement():
         assert isinstance(r.input, Entry)
         assert r.input.image is not None
         assert r.features is not None
-    solve(r.features.corners, r.features.board,
-          Camera(resolution=np.array(r.input.image.size)))
+    solve(
+        r.features.corners,
+        r.features.board,
+        Camera(resolution=np.array(r.input.image.size)),
+    )
     # show_boards(np.array(r.input.image), r.features.corners, r.features.board).show()
 
 

### 2023-05-27 calibration/augmentations/augmentations.py
Add augmenations

@@ -1,0 +1,23 @@
+from PIL import Image
+import numpy as np
+
+from calibration.benchmark.features import Features
+
+
+def overlay_img(img: Image.Image, path: str = "data/octopus.png") -> Image.Image:
+    img_ = Image.open(path).convert("RGBA")
+    size_ = np.array(img_.size) // 8
+    img_ = img_.resize(tuple(size_))
+    pos = np.array(img.size) // 2 - size_ // 2
+    print(pos)
+
+    img.paste(img_, tuple(pos), img_)
+    return img
+
+
+def prune_corners(f: Features, p: float = 0.2) -> Features:
+    mask = np.random.rand(f.board.shape[0]) > p
+    print(mask.shape, f.corners.shape)
+    f.board = f.board[mask]
+    f.corners = f.corners[mask]
+    return f

### 2023-05-28 calibration/solver/optimization/backproject.py
WIP

@@ -69,7 +69,7 @@ def backprojection_loss(
     intrinsic_matrix = jnp.array([[fx, 0, cx], [0, fy, cy], [0, 0, 1]])
 
     board_ = backproject(corners, R, t, lambdas, intrinsic_matrix)
-    weights = jnp.abs(corners / resolution - 0.5).mean(axis=1)**2
-    # weights /= jnp.square(resolution / 2)
+    weights = jnp.abs(corners / resolution - 0.5).mean(axis=1)
+    weights = 1
     return jnp.mean(jnp.abs(board_ - board) * (1 + weights * 10).reshape(-1, 1))
     # return jnp.mean(jnp.square(board_ - board))

### 2023-05-28 calibration/solver/optimization/solve.py

@@ -5,6 +5,8 @@ import jax.numpy as jnp
 import numpy as np
 import jax
 from scipy.spatial.transform import Rotation
+from calibration.benchmark.benchmark_result import calc_error
+from calibration.benchmark.features import Features
 from calibration.projector.camera import Camera
 from calibration.projector.projector import Projector
 from calibration.solver.optimization.backproject import backprojection_loss
@@ -42,22 +44,33 @@ def optimize_optax(
     board: jArr,
     resolution: jArr,
     # step_size=0.001,
-    step_size=0.005,
-    patience=100,
+    step_size=0.05,
+    patience=1000,
 ) -> dict[str, jArr]:
     # optimizer = optax.rmsprop(step_size)
     # optimizer = optax.adam(step_size)
-    optimizer = optax.amsgrad(step_size)
+    # schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.05, 1000, 2000,
+    #                                               0.001)
 
-    start_optimizing_during_phase = [
-        ["t", "theta_z"],
-        ["theta_x", "theta_y"],
-        ["lambdas"],
-        ["focal_length", "sensor_size"],
-    ]
+    schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.000001)
+    schedule2 = optax.warmup_cosine_decay_schedule(
+        0.000001, 0.001, 1000, 5000, 0.000001
+    )
+    # schedule2=    optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.001)
+    schedule = optax.join_schedules([schedule1, schedule2], [5000] * 3)
+    # schedule = optax.join_schedules([schedule1, schedule2], [5000])
+    # optimizer = optax.amsgrad(step_size)
+    optimizer = optax.amsgrad(schedule)
+
     # start_optimizing_during_phase = [
-    #     ["t", "theta_z", "theta_x", "theta_y", "lambdas", "focal_length", "sensor_size"]
+    #     ["t", "theta_z"],
+    #     ["theta_x", "theta_y"],
+    #     ["lambdas"],
+    #     ["focal_length", "sensor_size"],
     # ]
+    start_optimizing_during_phase = [
+        ["t", "theta_z", "theta_x", "theta_y", "lambdas", "focal_length", "sensor_size"]
+    ]
     phase_when_optimize = {
[…]

### 2023-05-28 main.py

@@ -28,10 +28,10 @@ def run_benchmark():
             refined_babelcalib_results = refine_features(babelcalib_results)
             with open(f"refined_babelcalib_results_{aug}.pkl", "wb") as f:
                 pkl.dump(refined_babelcalib_results, f)
-    if not os.path.isfile("simul_results.pkl"):
-        simul_results = benchmark_simul(int(1e3))
-        with open("simul_results.pkl", "wb") as f:
-            pkl.dump(simul_results, f)
+    # if not os.path.isfile("simul_results.pkl"):
+    #     simul_results = benchmark_simul(int(1e3))
+    #     with open("simul_results.pkl", "wb") as f:
+    #         pkl.dump(simul_results, f)
 
 
 def run_corner_refinement():

### 2023-05-28 paper/Chapters/Chapter4.tex
WIP
Update the paper and the evaluation

@@
 
+For the feature detection, we used the approach proposed by
+\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
+	feature_detection}).
+\missingfigure{Show the feature detection results.}
+
 \section{Camera calibration}\label{sec:camera_calibration}
+
+In this work, we obtained the camera calibration in two steps: first, we
+used the approach, proposed by \cite{scaramuzzaToolboxEasilyCalibrating2006} to
+obtain the initial approximation of the camera parameters. Then, we used the
+optimization to minimize the reprojection error between the board and the
+back-projected corners.
 
@@
 back-projection of the detected corners and the board are
-equivalent\todo{Doesn't sound very rigorous to me.}.
+equivalent\todo{Doesn't sound very rigorous to me.}. We minimized the error
+between the board and the back-projected corners because back-projection does
+not require the root finding.
 
@@
 
+\subsection{Initial approximation}\label{sub:initial_approximation}
+
+\cite{scaramuzzaToolboxEasilyCalibrating2006} proposed an automatic method for
+camera calibration, which consisted of the following steps:
+\begin{itemize}
+	\item Solving for the camera extrinsic parameters
+	\item Solving for the camera intrinsic parameters
+	\item Linear refinement of the intrinsic and extrinsic parameters
+	\item Iterative center detection
+	\item Non-linear refinement
+\end{itemize}
+
+In this work, we focused on the single image, while the original approach relied
+on the multiple images. Therefore, we used only the first two steps of the
+algorithm.
+
+\subsubsection{Solving for the camera extrinsic parameters}\label{ssub:solving_for_the_camera_extrinsic_parameters}
+
+To derive the solver for the camera extrinsic parameters, start from
+\cref{eq:projection}:
+\begin{align}
+	\alpha \mathbf{u}                                  & = K f(H\mathbf{X})                  \\
+	\alpha K^{-1} \mathbf{u}                           & = f(H\mathbf{X})    &  &
+	\text{Move \(K\) to the left side}                                                       \\
+	\alpha g( K^{-1}\mathbf{u})                        & = g(f(H\mathbf{X})) &  &
+	\text{Set \(\mathbf{\widehat{u}} = K^{-1}\mathbf{u}\); apply \(g(\cdot)\) to both sides} \\
+	\alpha \begin{pmatrix}
+		       \widehat{u}_x \\ \widehat{u}_y \\ \psi(r(\mathbf{\widehat{u}}))
+	       \end{pmatrix}^{T} & = H\mathbf{X}                                 \\
+\end{align}
+
+For \(K\) we used the placeholder values. \(f\) was set to a constant value for
+the typical consumer camera, and \(c_x, c_y\) were set to the center of the
+image.
+The correct values will be computed during the optimization \cref{sub:optimization}.
+
+To eliminate the dependency on the scale \(\alpha\), multiply both sides
+vectorially by \(g(\mathbf{\widehat{u}})\):
+\begin{equation}
+	\alpha g(\mathbf{\widehat{u}}) \times g(\mathbf{\widehat{u}})
+	= g(\mathbf{\widehat{u}}) \times H\mathbf{X}
+	= 0 \implies
+	\begin{pmatrix}
+		\widehat{u}, \widehat{v}, \psi(r(\mathbf{\widehat{u}}))
+	\end{pmatrix}^{T} \times \begin{bmatrix}
+		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
+	\end{bmatrix}^{T} \mathbf{X} = 0
+	\label{eq:eq_no_multiplier}
+\end{equation}.
+
+From \cref{eq:eq_no_multiplier}, we can see that a point contributes to three
+homogeneous equations:
+\begin{align}
+	\widehat{v} (t_1X + t_2 Y + t_3) -
+	g(r(\mathbf{\widehat{u}})) (r_{12}X + r_{22}Y + t_2 ) & = 0
+	\label{eq:scaramuzza_system_1}                              \\
+	g(r(\mathbf{\widehat{u}})) (r_{11}X + r_{12}Y + t_1) -
+	\widehat{u} (t_1X + t_2 Y + t_3)                      & = 0
+	\label{eq:scaramuzza_system_2}                              \\
+	\widehat{u} (r_{12}X + r_{22}Y + t_2 ) -
+	\widehat{v} (r_{11}X + r_{12}Y + t_1)                 & = 0
+	\label{eq:scaramuzza_system_3}
+\end{align}
+
+Only \cref{eq:scaramuzza_system_3} is linear in the unknowns. Each point gives a
+single equation. Now, by rewriting the equation in the matrix form
+\(M \cdot H = 0\), where \(H = \begin{pmatrix}
+	r_{11}, r_{12}, r_{12}, r_{22}, t_1, t_2
+\end{pmatrix}\) we get:
+
+\begin{equation}
+	M = \begin{bmatrix}
+		-\widehat{v}_1 X_1 & -\widehat{v}_1 Y_1 & -\widehat{u}_1 X_1 & -\widehat{u}_1 Y_1 & -\widehat{v}_1 & -\widehat{u}_1 \\
+		\vdots             & \vdots             & \vdots             & \vdots             & \vdots         & \vdots         \\
+		-\widehat{v}_N X_N & -\widehat{v}_N Y_N & -\widehat{u}_N X_N & -\widehat{u}_N Y_N & -\widehat{v}_N & -\widehat{u}_N
+	\end{bmatrix}
+\end{equation}, where \(N\) is the number of points.
+
+The linear estimate of \(H\) is found by minimizing \(\left\lVert M \cdot H
+\right\rVert ^{2}\) using SVD. The solution is known up to a scale factor.
+
+To find \(t_1\) and \(t_2 \), note that \(\mathbf{r_1}\) and
+\(\mathbf{r_2}\) are orthonormal:
+\begin{subnumcases}{}
+	\lambda^{2} r_{11} r_{12} + \lambda^{2} r_{12} r_{22} + \lambda^{2} t_1
+	t_2  = 0
+	\label{eq:orthonormality_1}                                                     \\
+	\lambda \sqrt{r_{11}^{2} + r_{12}^{2} + t_1^{2}}                            = 1
+	\label{eq:orthonormality_2}                                                     \\
+	\lambda \sqrt{r_{12}^{2} + r_{22}^{2} + t_2 ^{2}}                            = 1
+	\label{eq:orthonormality_3}
+\end{subnumcases},
+where \(\lambda\) is non-zero multiplier.
+
+Now, to solve for \(t_1\) and \(t_2 \), first find possible values for
+\(t_2 ^{2}\):
+\begin{align}
+	- \frac{r_{11} r_{12} + r_{12} r_{22}}{t_2 }                  & = t_1 &  &
+	\text{Solve eq. (\ref{eq:orthonormality_1}) for \(t_1\)}
+	\label{eq:orthonormality_4}                                                \\
+	\\
+	\sqrt{\lambda^{2} \left( \frac{r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
+	r_{11}^{2} + r_{12}^{2}\right)}                               & = 1   &  &
+	\text{Substitute into eq. (\ref{eq:orthonormality_2})}                     \\
+	\lambda^{2} (\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
+	r_{11}^{2} + r_{12}^{2})                                      & = 1   &  &
+	\text{Square both sides}                                                   \\
+	\lambda^{2} (\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
+	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2}) & = 0   &  &
+	\text{Subtract eq. (\ref{eq:orthonormality_3})}
+	\label{eq:orthonormality_5}
+	\\
+	\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
+	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2}  & = 0   &  &
+	\text{Divide both by \(\lambda ^{2}\)}                                     \\
+	t_2 ^{4} - (r_{11}^{2} + r_{12}^{2} - r_{12}^{2} -
+	r_{22}^{2}) t_2 ^{2} - (r_{11} r_{12} + r_{12} r_{22})^{2}    & = 0   &  &
+	\text{Multiply by \(t_2 ^{2}\)}
+	\label{eq:orthonormality_6}
+\end{align}
+
+Now, solve \cref{eq:orthonormality_6} for \(t_2 ^{2}\), and take a root to find
+possible values for \(t_2 \).
+
+To find \(t_1\), substitute the found values for \(t_2 \) into
+\cref{eq:orthonormality_4} or \cref{eq:orthonormality_5} depending on the value
+of \(t_2 \):
+\begin{subnumcases}{}
+	t_1  = - \frac{r_{11} r_{12} + r_{12} r_{22}}{t_2 } &
+	\text{\(t_2  \neq 0\)} \\
+	t_1  =  r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} &
+	\text{\(t_2  = 0\)}
+\end{subnumcases}
+
+Now, it's possible to find \(H\) for each of the pairs of \(t_1\) and
+\(t_2 \).
+
+Lastly, to select the correct \(H\), the author assumes that one of the boards'
+corners has the coordinates \( \begin{pmatrix}
+	0, 0
+\end{pmatrix}^{T}\). Then, the rotation wouldn't affect this
+point, and it would be projected to   \(\begin{pmatrix}
+	t_1, t_2
+\end{pmatrix}^{T}\). Hence, the best matrix would be such that has the closest
+\(\begin{pmatrix}
+	t_1, t_2
+\end{pmatrix}^{T}\) to \(\begin{pmatrix}
+	X, Y
+\end{pmatrix}^{T}\) of the corner, which is associated with the board's corner
+with corrdinates \(\begin{pmatrix}
+	0, 0
+\end{pmatrix}^{T}\).
+
+However, often the algorithm finds who matrices \(H\) such that they have the
+same \(t_1\) and \(t_2 \), but different \(r_{11}\), \(r_{12}\), \(r_{21}\). To
+find the best matrix, we found the intrinsic values for each of them, and
+backprojected the board's corners using both matrices.
+Then, we used the one which gave the smallest reprojection error.
+
+\subsubsection{Solving for the camera intrinsic parameters}\label{subsub:solving_for_the_camera_intrinsic_parameters}
+
+Now, to find the rest of the parameters, we substitute the values, found in the
+previous step into \cref{eq:scaramuzza_system_1} and
+\cref{eq:scaramuzza_system_2}. We assumed the number of the division model's
+parameter to be equal to 2, and the scalar multiplier to be equal to 1
+\cref{subsub:back_projection_using_the_division_model}:
+
+\begin{equation}
+	\begin{bmatrix}
+		A_1 \rho_1^{2} & A_1 \rho_1^{4} & -v_1   \\
+		C_1 \rho_1^{2} & C_1 \rho_1^{4} & -v_1   \\
+		\cdots         & \cdots         & \cdots \\
+		A_N \rho_N^{2} & A_N \rho_N^{4} & -v_N   \\
+		C_N \rho_N^{2} & C_N \rho_N^{4} & -v_N
+	\end{bmatrix} \cdot \begin{bmatrix}
+		\lambda_1 \\
+		\lambda_2 \\
+		t_3
+	\end{bmatrix} = \begin{bmatrix}
+		B_1 - A_1 \\
+		D_1 - C_1 \\
+		\cdots    \\
+		B_N - A_N \\
+		D_N - C_N
+	\end{bmatrix}
+\end{equation},
+where
+\begin{align}
+	A_i & = r_{21} X_i + r_{22} Y_i + t_2 \\
+	B_i & = v_i (r_{31} X_i + r_{32} Y_i) \\
+	C_i & = r_{11} X_i + r_{12} Y_i + t_1 \\
+	D_i & = u_i (r_{31} X_i + r_{32} Y_i) \\
+\end{align}
+
+The solution can be found using the least squares method.
+
 \subsection{Optimization}\label{sub:optimization}
@@
 
-\section{Feature detection}\label{sec:feature_detection}
+\section{Additional features detection}\label{sec:additional_features_detection}
 
@@
 
-Given the possible positions of the previously undetected corners, we used a
-classifier, proposed by \cite{geigerAutomaticCameraRange2012}.
-By convolving the image with the templates of the board corners\todo{I have to
-reference it from the related work section}, we obtained the
-probability\todo{It's not probability} of
-each pixel being a corner.\todo{Also, explain in details + math how it's done}
+In this work, we used the method, proposed by
+\cite{geigerAutomaticCameraRange2012} as it didn't require the whole board to be
+visible, automatically determines the board's number of rows and columns and
+worked quite well on highly-distorted images.
+
+In this work, we directly used the following steps from the algorithm:
+\begin{enumerate}
+	\item Corner detection
+	\item Sub-pixel corner and orientation refinement
+\end{enumerate}
+
+\subsection{Corner detection}\label{sub:corner_detection}
+
+% \begin{multicols}{2}
+%
+% 	According to \cite{geigerAutomaticCameraRange2012}, the following approach proved to be
+% 	more robust to image clutter and blur than other common choices
+% 	\citep{harrisCombinedCornerEdge1988, shiGoodFeaturesTrack2000}.
+%
+% 	To detect corners in a grayscale image $I$, the author used two $n \times n$ prototypes
+% 	for axis-aligned and $45^{\circ}$ rotated corners, respectively.
+% 	Each prototype
+% 	is constructed using four filter kernels $\{A, B, C, D\}$. The corner likelihood
+% 	$c$ at each pixel is computed by:
+%
+% 	\columnbreak
+%
+% 	\begin{figure}[H]
+% 		\centering
+%
+% 		\begin{subfigure}{0.48\textwidth}
+% 			\centering
+% 			\includegraphics[width=0.23\textwidth]{./template_1_a.png}
+% 			\includegraphics[width=0.23\textwidth]{./template_1_b.png}
+% 			\includegraphics[width=0.23\textwidth]{./template_1_c.png}
+% 			\includegraphics[width=0.23\textwidth]{./template_1_d.png}
+% 			\caption{Corner prototype 1 (A, B, C, D)}
+% 		\end{subfigure}
+%
+%     \vspace{0.5cm}
+%
+% 		\begin{subfigure}{0.48\textwidth}
+% 			\centering
+% 			\includegraphics[width=0.23\textwidth]{./template_2_a.png}
+% 			\includegraphics[width=0.23\textwidth]{./template_2_b.png}
+% 			\includegraphics[width=0.23\textwidth]{./template_2_c.png}
+% 			\includegraphics[width=0.23\textwidth]{./template_2_d.png}
+% 			\caption{Corner prototype 2 (A, B, C, D)}
+% 		\end{subfigure}
+%
+% 		\caption{Corner prototypes}
+% 	\end{figure}
+%
+% \end{multicols}
+
+\begin{figure}[h]
+	\centering
+
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\begin{minipage}{\textwidth}
+			\includegraphics[width=0.24\textwidth]{./template_1_a.png}
+			\includegraphics[width=0.24\textwidth]{./template_1_b.png}
+			\includegraphics[width=0.24\textwidth]{./template_1_c.png}
+			\includegraphics[width=0.24\textwidth]{./template_1_d.png}
+		\end{minipage}
+		\caption{Corner prototype 1 (A, B, C, D)}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\begin{minipage}{\textwidth}
+			\includegraphics[width=0.24\textwidth]{./template_2_a.png}
+			\includegraphics[width=0.24\textwidth]{./template_2_b.png}
+			\includegraphics[width=0.24\textwidth]{./template_2_c.png}
+			\includegraphics[width=0.24\textwidth]{./template_2_d.png}
+		\end{minipage}
+		\caption{Corner prototype 2 (A, B, C, D)}
+	\end{subfigure}
+
+	\caption{Corner prototypes \citep{geigerAutomaticCameraRange2012}}
+	\label{fig:corner_prototypes}
+\end{figure}
+
+According to \cite{geigerAutomaticCameraRange2012}, the following approach proved to be
+more robust to image clutter and blur than other common choices
+\citep{harrisCombinedCornerEdge1988, shiGoodFeaturesTrack2000}.
+
+To detect corners in a grayscale image $I$, the author used two $n \times n$ prototypes
+for axis-aligned and $45^{\circ}$ rotated corners, respectively.
+Each prototype
+is constructed using four filter kernels $\{A, B, C, D\}$ (\cref{fig:corner_prototypes}). The corner likelihood
+$c$ at each pixel is computed by:
+
+\begin{equation}
+	\begin{aligned}
+		c     & =\max \left(s_1^1, s_2^1, s_1^2, s_2^2\right)                                             \\
+		s_1^i & =\min \left(\min \left(f_A^i, f_B^i\right)-\mu, \mu-\min \left(f_C^i, f_D^i\right)\right) \\
+		s_2^i & =\min \left(\mu-\min \left(f_A^i, f_B^i\right), \min \left(f_C^i, f_D^i\right)-\mu\right) \\
+		\mu   & =0.25\left(f_A^i+f_B^i+f_C^i+f_D^i\right)
+	\end{aligned}
+\end{equation}
+
+Then, the authors apply the conservative non-maximum suppression to the
+response map, and additionally filter the corners by assuring that there are two
+modes of the gradient directions.
+
+\subsection{Sub-pixel Corner and Orientation Refinement}\label{sub:sub_pixel_corner_and_orientation_refinement}
+
+Sub-pixel accurate corner locations and edge orientations are refined using the following optimizations:
+
+For sub-pixel corner localization, the corner $\mathbf{c}$ in a 2D space
+$\mathbb{R}^2$ is refined using the assumption that the gradient direction
+\(\mathbf{g_{p}}\) at
+each pixel  \(\mathbf{p}\) in the small neighbourhood around the corner is
+orthogonal to \(\mathbf{p} - \mathbf{c}\).
+
+\begin{equation}
+	\mathbf{c}=\arg \min _{\mathbf{c}^{\prime}} \sum_{\mathbf{p} \in
+	\mathcal{N}_{\mathbf{I}}\left(\mathbf{c}^{\prime}\right)}\left(\mathbf{g}_{\mathbf{p}}^T\left(\mathbf{p}-\mathbf{c}^{\prime}\right)\right)^2
+\end{equation}
+
+For the orientation refinement, authors minimize the distance from the
+orientation vectors \(\mathbf{e_1}, \mathbf{e_2}\) to the gradient directions
+\(\mathbf{g_p}\) in the neighbourhood of the corner.
+
+\begin{equation}
+	\mathbf{e}_i=\arg \min _{\mathbf{e}_i^{\prime}} \sum_{\mathbf{p} \in
+		\mathcal{M}_i}\left(\mathbf{g}_{\mathbf{p}}^T \mathbf{e}_i^{\prime}\right)^2
+	\quad \text { s.t. } \mathbf{e}_i^{\prime T} \mathbf{e}_i^{\prime}=1
+\end{equation}.
 

### 2023-05-28 calibration/feature_refiner/classifier.py

@@ -13,8 +13,8 @@ def find_modes_meanshift(hist):
 
     hist = hist.astype(int)
     samples = np.repeat(np.arange(len(hist)), hist).reshape(-1, 1)
-    bandwidth = estimate_bandwidth(samples, quantile=0.2, n_samples=500)
-    ms = MeanShift(bandwidth=bandwidth, bin_seeding=True).fit(samples)
+    # bandwidth = estimate_bandwidth(samples, quantile=0.2, n_samples=500)
+    ms = MeanShift(bin_seeding=True).fit(samples)
 
     # Retrieve unique labels and cluster centers
     labels_unique = np.unique(ms.labels_)
@@ -81,7 +81,7 @@ def compute_orientation(img, positions, window_size):
                 window, bins=32, weights=weights, range=(-np.pi, np.pi)
             )
 
-            if histogram.sum() == 0:
+            if np.allclose(histogram, 0):
                 passes.append(False)
                 continue
             # ms = MeanShift(bin_seeding=True)

### 2023-05-28 calibration/feature_refiner/refine.py

@@ -35,7 +35,8 @@ def view1D(a, b):  # a, b are arrays
 
 
 def refine_features_single(
-    r: BenchmarkResult, solver_name: str="Optimization", pan_size: int = 1, thr=13.8
+    r: BenchmarkResult, solver_name: str="Optimization", pan_size: int = 1,
+    thr=28.7
 ) -> RefinedResult | None:
     assert isinstance(r.input, Entry) and r.input.image is not None
     board = r.features.board.astype(int)
@@ -56,13 +57,19 @@ def refine_features_single(
     proj = r.predictions[solver_name]
     try:
         new_corners = proj.project(new_board)
+        # new_corners = proj.project(r.features.board)
     except ValueError:
         return None
-    print(new_corners.shape)
-    print(board.shape)
-    print(new_board.shape)
+    # import plotly.express as px
+    # px.scatter(x=new_corners[:, 0],
+    #                y=new_corners[:, 1]).show()
+    # px.scatter(x=r.features.corners[:, 0],
+    #            y=r.features.corners[:, 1]).show()
+    # print(new_corners.shape)
+    # print(board.shape)
+    # print(new_board.shape)
     responses, new_mask = prune_corners(new_corners, mask, r.input.image, thr)
-    print(new_corners.shape)
+    # print(new_corners.shape)
     return RefinedResult(
         r.input,
         r.features,

### 2023-05-28 calibration/feature_refiner/visualization.py

@@ -21,7 +21,7 @@ def show_refined_corners(
     }
 
     responses_all = np.full_like(mask, -1)
-    responses_all[(mask > 0) & (mask < 3)] = responses
+    # responses_all[(mask > 0) & (mask < 3)] = responses
     points = [
         {
             "n": i,

### 2023-05-28 calibration/solver/optimization/backproject.py

@@ -70,6 +70,6 @@ def backprojection_loss(
 
     board_ = backproject(corners, R, t, lambdas, intrinsic_matrix)
     weights = jnp.abs(corners / resolution - 0.5).mean(axis=1)
-    weights = 1
+    weights = jnp.array([1])
     return jnp.mean(jnp.abs(board_ - board) * (1 + weights * 10).reshape(-1, 1))
     # return jnp.mean(jnp.square(board_ - board))

### 2023-05-28 calibration/solver/optimization/helpers.py

@@ -1,0 +1,29 @@
+import numpy as np
+import jax.numpy as jnp
+import jax
+from calibration.projector.camera import Camera
+
+from calibration.projector.projector import Projector
+from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+
+jArr = jax.Array
+nArr = np.ndarray
+
+def params_to_proj(jparams: dict[str, jArr], resolution: nArr) -> Projector | None:
+    if any(np.isnan(v).any() for v in jparams.values()):
+        return None
+    params = {k: np.array(v) for k, v in jparams.items()}
+
+    camera = Camera(
+        float(jparams["focal_length"]), params["sensor_size"], np.array(resolution)
+    )
+
+    theta = jnp.concatenate(
+        [jparams["theta_x"], jparams["theta_y"], jparams["theta_z"]]
+    )
+    params["R"] = np.array(euler_angles_to_rotation_matrix(theta))
+
+    for p in ["focal_length", "sensor_size", "theta_x", "theta_y", "theta_z"]:
+        del params[p]
+
+    return Projector(**params, camera=camera)

### 2023-05-28 calibration/solver/optimization/optimize.py

@@ -1,0 +1,159 @@
+from functools import partial
+import numpy as np
+import jax.numpy as jnp
+import optax
+import jax
+from calibration.benchmark.benchmark_result import calc_error
+from calibration.benchmark.features import Features
+
+from calibration.solver.optimization.backproject import backproject, backprojection_loss
+from calibration.solver.optimization.helpers import params_to_proj
+from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+
+jArr = jax.Array
+
+
+def optimize_optax(
+    params: dict[str, jArr],
+    corners: jArr,
+    board: jArr,
+    resolution: jArr,
+    # step_size=0.001,
+    step_size=0.05,
+    patience=1000,
+) -> dict[str, jArr]:
+    # optimizer = optax.rmsprop(step_size)
+    # optimizer = optax.adam(step_size)
+    # schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.05, 1000, 2000,
+    #                                               0.001)
+
+    schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.000001)
+    schedule2 = optax.warmup_cosine_decay_schedule(
+        0.000001, 0.001, 1000, 5000, 0.000001
+    )
+    # schedule2=    optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.001)
+    schedule = optax.join_schedules([schedule1, schedule2], [5000] * 1)
+    # schedule = optax.join_schedules([schedule1, schedule2], [5000])
+    # optimizer = optax.amsgrad(step_size)
+    optimizer = optax.amsgrad(schedule)
+
+    phase_l = [
+        ["t", "theta_z"],
+        ["theta_x", "theta_y"],
+        ["lambdas"],
+        ["focal_length", "sensor_size"],
+    ]
+    phase_l = [list(params)]
+    param_to_phase = {p: i for i, ps in enumerate(phase_l) for p in ps}
+    mask_for_phase = [
+        {p: phase_ > phase for p, phase_ in param_to_phase.items()}
+        for phase in range(len(phase_l))
+    ]
+    phases = [optax.masked(optax.set_to_zero(), mask) for mask in mask_for_phase]
+    inits = [v.init(params) for v in phases]
+    opt_state = optimizer.init(params)
+
+    loss_history = jnp.full(patience, jnp.inf)
+
+    # Define a function to compute the gradient and update the parameters
[…]

### 2023-05-28 calibration/solver/optimization/solve.py

@@ -1,6 +1,3 @@
-from functools import partial
-import optax
-
 import jax.numpy as jnp
 import numpy as np
 import jax
@@ -9,191 +6,12 @@ from calibration.benchmark.benchmark_result import calc_error
 from calibration.benchmark.features import Features
 from calibration.projector.camera import Camera
 from calibration.projector.projector import Projector
-from calibration.solver.optimization.backproject import backprojection_loss
-from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+from calibration.solver.optimization.helpers import params_to_proj
+from calibration.solver.optimization.optimize import optimize_optax
 from calibration.solver.scaramuzza.solve import solve as solve_scaramuzza
 
 jArr = jax.Array
 nArr = np.ndarray
-
-
-def params_to_proj(jparams: dict[str, jArr], resolution: nArr) -> Projector | None:
-    if any(np.isnan(v).any() for v in jparams.values()):
-        return None
-    params = {k: np.array(v) for k, v in jparams.items()}
-
-    camera = Camera(
-        int(jparams["focal_length"]), params["sensor_size"], np.array(resolution)
-    )
-
-    theta = jnp.concatenate(
-        [jparams["theta_x"], jparams["theta_y"], jparams["theta_z"]]
-    )
-    params["R"] = np.array(euler_angles_to_rotation_matrix(theta))
-
-    for p in ["focal_length", "sensor_size", "theta_x", "theta_y", "theta_z"]:
-        del params[p]
-
-    return Projector(**params, camera=camera)
-
-
-# @partial(jax.jit, static_argnames=("step_size", "num_steps"))
-def optimize_optax(
-    params: dict[str, jArr],
-    corners: jArr,
-    board: jArr,
-    resolution: jArr,
-    # step_size=0.001,
-    step_size=0.05,
-    patience=1000,
-) -> dict[str, jArr]:
-    # optimizer = optax.rmsprop(step_size)
-    # optimizer = optax.adam(step_size)
-    # schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.05, 1000, 2000,
-    #                                               0.001)
-
-    schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.000001)
-    schedule2 = optax.warmup_cosine_decay_schedule(
-        0.000001, 0.001, 1000, 5000, 0.000001
-    )
[…]

### 2023-05-28 main.py

@@ -16,15 +16,16 @@ from calibration.solver.optimization.solve import solve
 
 
 def run_benchmark():
-    for aug in [None, "overlay", "prune_corners"]:
+    # for aug in [None, "overlay", "prune_corners"]:
+    for aug in [None]:
         path = f"babelcalib_results_{aug}.pkl"
         if True or not os.path.isfile(path):
-            babelcalib_results = benchmark_babelcalib(aug=aug)
-
-            with open(path, "wb") as f:
-                pkl.dump(babelcalib_results, f)
-            # with open(path, "rb") as f:
-            #     babelcalib_results = pkl.load(f)
+            # babelcalib_results = benchmark_babelcalib(aug=aug)
+            #
+            # with open(path, "wb") as f:
+            #     pkl.dump(babelcalib_results, f)
+            with open(path, "rb") as f:
+                babelcalib_results = pkl.load(f)
             refined_babelcalib_results = refine_features(babelcalib_results)
             with open(f"refined_babelcalib_results_{aug}.pkl", "wb") as f:
                 pkl.dump(refined_babelcalib_results, f)

### 2023-05-28 paper/Chapters/Chapter2.tex
Update the paper and the evaluation
2AM woo-hoo

@@
 ~\citep{garrido-juradoAutomaticGenerationDetection2014} (\cref{fig:gboriginal}) and
-AprilTag~\citep{olsonAprilTagRobustFlexible2011a} (\cref{fig:apriltag})
+AprilTag~\citep{olsonAprilTagRobustFlexible2011} (\cref{fig:apriltag})
 allowed detecting the
@@
 multiple new approaches have arisen.
+\cite{scaramuzzaToolboxEasilyCalibrating2006} proposed an automatic algorithm
+for camera calibration, which did not use any model of the specific omnidirectional
+sensor.
 \cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
@@
 approaches for wide-angle cameras.
-
-\todo{Add the paper about the feature detection}
 
@@
 \cite{fuersattelOCPADOccludedCheckerboard2016} and
-\cite{geigerAutomaticCameraRange2012}. Those method can detect the board under
+\cite{geigerAutomaticCameraRange2012}. Those method can detect the board and
+associate the corners with the borders' corners under
 the partial occlusion and do not require prior knowledge of the board's geometry.
+
+\cite{chenNewSubPixelDetector2005} proposed using Hessian to find pixel
+positions of the corners.

### 2023-05-28 paper/Chapters/Chapter4.tex
2AM woo-hoo

@@
 
-For the feature detection, we used the approach proposed by
+For the feature detection, we used the approach, proposed by
 \cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
-	feature_detection}).
-\missingfigure{Show the feature detection results.}
+	sec:feature_detection}).
 
@@
 optimization to minimize the reprojection error between the board and the
-back-projected corners.
+back-projected corners. A division model is very powerful, and is able to
+express a wide number of range of distortions
+\citep{prittsMinimalSolversRectifying2021}. In this work, we used a model with
+two parameters to allow for a better flexibility during the optimization.
 
@@
 	\lambda_1, \lambda_2
-\end{pmatrix}^{T}\)\todo{Justify why we used 2} is the intrinsic parameters vector, \(\) is the focal
+\end{pmatrix}^{T}\) is the intrinsic parameters vector, \(\) is the focal
 length, and \(\mathbf{s} = \begin{pmatrix}
 	s_x, s_y
-\end{pmatrix}^{T}\) is the sensor size\todo{Make sure I'm using the correct terms.}.
+\end{pmatrix}^{T}\) is the sensor size.
 From the input image, we know the resolution \(\mathbf{r} = \begin{pmatrix}
@@
 
-\missingfigure{Show the distribution of the reprojection error}.
-
 \section{Additional features detection}\label{sec:additional_features_detection}
@@
 
-\missingfigure{Show the image, the respective board, and the imputed points}
-
 We used the obtained camera parameters to then project the imputed board points
@@
 
-In this work, we used the method, proposed by
+In this work, one of the methods we used was proposed by
 \cite{geigerAutomaticCameraRange2012} as it didn't require the whole board to be
@@
 
-\subsection{Sub-pixel Corner and Orientation Refinement}\label{sub:sub_pixel_corner_and_orientation_refinement}
+% \subsection{Sub-pixel Corner and Orientation Refinement}\label{sub:sub_pixel_corner_and_orientation_refinement}
+%
+% Sub-pixel accurate corner locations and edge orientations are refined using the following optimizations:
+%
+% For sub-pixel corner localization, the corner $\mathbf{c}$ in a 2D space
+% $\mathbb{R}^2$ is refined using the assumption that the gradient direction
+% \(\mathbf{g_{p}}\) at
+% each pixel  \(\mathbf{p}\) in the small neighbourhood around the corner is
+% orthogonal to \(\mathbf{p} - \mathbf{c}\).
+%
+% \begin{equation}
+% 	\mathbf{c}=\arg \min _{\mathbf{c}^{\prime}} \sum_{\mathbf{p} \in
+% 	\mathcal{N}_{\mathbf{I}}\left(\mathbf{c}^{\prime}\right)}\left(\mathbf{g}_{\mathbf{p}}^T\left(\mathbf{p}-\mathbf{c}^{\prime}\right)\right)^2
+% \end{equation}
+%
+% For the orientation refinement, authors minimize the distance from the
+% orientation vectors \(\mathbf{e_1}, \mathbf{e_2}\) to the gradient directions
+% \(\mathbf{g_p}\) in the neighbourhood of the corner.
+%
+% \begin{equation}
+% 	\mathbf{e}_i=\arg \min _{\mathbf{e}_i^{\prime}} \sum_{\mathbf{p} \in
+% 		\mathcal{M}_i}\left(\mathbf{g}_{\mathbf{p}}^T \mathbf{e}_i^{\prime}\right)^2
+% 	\quad \text { s.t. } \mathbf{e}_i^{\prime T} \mathbf{e}_i^{\prime}=1
+% \end{equation}.
 
-Sub-pixel accurate corner locations and edge orientations are refined using the following optimizations:
+\subsection{Classifier training}\label{sub:classifier_training}
 
-For sub-pixel corner localization, the corner $\mathbf{c}$ in a 2D space
-$\mathbb{R}^2$ is refined using the assumption that the gradient direction
-\(\mathbf{g_{p}}\) at
-each pixel  \(\mathbf{p}\) in the small neighbourhood around the corner is
-orthogonal to \(\mathbf{p} - \mathbf{c}\).
-
-\begin{equation}
-	\mathbf{c}=\arg \min _{\mathbf{c}^{\prime}} \sum_{\mathbf{p} \in
-	\mathcal{N}_{\mathbf{I}}\left(\mathbf{c}^{\prime}\right)}\left(\mathbf{g}_{\mathbf{p}}^T\left(\mathbf{p}-\mathbf{c}^{\prime}\right)\right)^2
-\end{equation}
-
-For the orientation refinement, authors minimize the distance from the
-orientation vectors \(\mathbf{e_1}, \mathbf{e_2}\) to the gradient directions
-\(\mathbf{g_p}\) in the neighbourhood of the corner.
-
-\begin{equation}
-	\mathbf{e}_i=\arg \min _{\mathbf{e}_i^{\prime}} \sum_{\mathbf{p} \in
-		\mathcal{M}_i}\left(\mathbf{g}_{\mathbf{p}}^T \mathbf{e}_i^{\prime}\right)^2
-	\quad \text { s.t. } \mathbf{e}_i^{\prime T} \mathbf{e}_i^{\prime}=1
-\end{equation}.
-
-The original paper then used a number of checks to further prune the detected
-corners, and extending line by line the initial board, formed from the
-random close points which made a square \todo{Make sure that's accurate, and
-	reference. Also, the sentence is too compicated}.
-We did not require that, since we already had the board, and we directly used
-the response map to find the corners.
-
-\missingfigure{Show the map of responses, and the detected corners}
+We tested the approach of \cite{geigerAutomaticCameraRange2012}, and,
+alternatively, the Hessian responses for the image, as proposed by
+\cite{chenNewSubPixelDetector2005}.
 
 To create a training dataset, we collected the true and false positives from the
-corners we already had:
+corners we already detected.
 
@@
 response function at the previously detected corners, and around them.
-We didn't collect the values of all of the pixels, because then we would have
-got too optimistic values for selecting the true positives\todo{Rephrase}.
+We didn't collect the values of all of the pixels, in order to reduce the number
+of very simple examples.
 
-\missingfigure{Show the distribution of the response function}
+To determine the threshold for the classification, we used the ROC curve, and
+found the threshold which maximizes
+the geometric mean of the true positive rate and the false positive rate.
 
-We trained a binary classifier, using the collected data, and then used it to
-detect the true corners.
+We used both of the approaches to train the classifier, and compared the
+results in \cref{sec:classification}.

### 2023-05-28 paper/Chapters/Chapter5.tex
2AM woo-hoo

@@
 
-We created a symulator to generate distorted points. We used it to test the
+We created a symulator to generate distorted points as described in
+\cref{sub:complete_projection_and_backprojection}. We used it to test the
 solver, and test the correctness of projection and back-projection points.
@@
 
+For this project, we required a highly distorted dataset of chessboard images.
+We collected a number of datasets, but the feature detector we used supports
+detecting only the boards with the constant tile size, therefore we cannot use
+AprilGrid nor CharuCO boards. The feature detector is the only limiting factor.
+
 \textcite{lochmanBabelCalibUniversalApproach2021} collected a wide number of
@@
 
-\textbf{Kalibr} contains several established datasets that are commonly used for testing
+\textbf{Kalibr} \citep{mayeSelfsupervisedCalibrationRobotic2013} contains several established datasets that are commonly used for testing
 the accuracy of camera calibration frameworks: Double Sphere
@@
 
-\textbf{OCamCalib} \cite{scaramuzzaFlexibleTechniqueAccurate2006} is a dataset
+\textbf{OCamCalib} \citep{scaramuzzaFlexibleTechniqueAccurate2006} is a dataset
 of approximately 300 images.
@@
 
-\textbf{UZH} \cite{AreWeReady} is a dataset of approximately 800 images
+\textbf{UZH} \citep{AreWeReady} is a dataset of approximately 800 images
 collected using the following cameras:
@@
 
-\textbf{OV} \cite{duisterhofTartanCalibIterativeWideAngle2022} is a dataset of
+\textbf{OV} \citep{lochmanBabelCalibUniversalApproach2021} is a dataset of
 approximately 1400 images. It was collected using eight stereo cameras.
@@
 \textcite{duisterhofTartanCalibIterativeWideAngle2022} also provide their
-dataset from the TartanCalib project, but it is quite challenging to use it as it
-comes in the Robot Operating System (ROS) .bag format.
+dataset from the TartanCalib project. Currently, the dataset contains only
+AprilGrid patterns, as the toolchain doesn't support chessboard.
 
-\begin{figure}[h!]
+\begin{figure}[h]
 	\centering
@@
 		\includegraphics[width=\linewidth]{OCamCalib.png}
-		\caption{OCamCalib}
+		\caption{\textbf{OCamCalib}}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{OV.png}
-		\caption{OV}
+		\caption{\textbf{OV}}
 	\end{subfigure}
@@
 
-\todo{Probably, remove everything but BabelCalib, as we didn't use AprilGrid}
+\section{Camera calibration}\label{sec:camera_calibration}
+
+\begin{minipage}{0.5\linewidth}
+	In order to get accurate predictions for the possibly missing points, we need
+	very accurate camera calibration. We used the reprojection error as a metric
+	for the calibration quality.
+	In order to calculate the reprojection error, we have to perform the
+	rootfinding \cref{subsub:back_projection_using_the_division_model}. We assume
+	that all of the points lay within the image, or they get out of the borders
+	a little bit (we use the constant \(1.1\) of the maximum radius). If the
+	camera calibration is poor, the rootfinding might fail. On the initial
+	calibration the number of the failed rootfindings was much higher.
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\linewidth}
+	\resizebox{\linewidth}{!}{
+		\begin{tikzpicture}
+			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
+				115/Correctly detected,
+				80/Reprojection error > 10,
+				254/Not correctly detected
+			}
+		\end{tikzpicture}
+	}
+	\captionsetup{width=.9\linewidth}
+	\captionof{figure}{Initial calibration}
+	\resizebox{\linewidth}{!}{
+		\begin{tikzpicture}
+			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
+				658/Correctly detected,
+				19/Reprojection error > 10,
+				115/Not correctly detected
+			}
+		\end{tikzpicture}
+	}
+	\captionsetup{width=.9\linewidth}
+	\captionof{figure}{Final calibration}
+\end{minipage}
+
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Initial calibration}
+			]
+			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/reprojection_error_init.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Initial calibration's reprojection error histogram}
+\end{figure}
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Reprojection error}
+			]
+			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/reprojection_error_final.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Final calibration's reprojection error histogram}
+\end{figure}
+
+\section{Additional features detection}\label{sec:additional_features_detection}
+
+As discussed in \cref{sec:additional_features_detection}, we filled the gaps in
+the originally detected board points, and then padded it for 1 additional
+element.
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{0.55\linewidth}
+		\begin{subfigure}[b]{\linewidth}
+			\includegraphics[width=\linewidth]{extended_board_img.png}
+			\label{fig:extended_board_img}
+			\caption{Extended board, new points are marked as blue}
+		\end{subfigure}
+	\end{minipage}
+	\begin{minipage}{0.35\linewidth}
+		\resizebox{\linewidth}{!}{
+			\begin{tikzpicture}
+				\begin{axis}[
+						xlabel={$x$},
+						ylabel={$y$},
+						grid=major,
+						title={Original board},
+					]
+					\addplot[
+						only marks,
+					] table {data/original_board.txt};
+				\end{axis}
+			\end{tikzpicture}
+		}
+		\vfill
+		\resizebox{\linewidth}{!}{
+			\centering
+			\begin{tikzpicture}
+				\begin{axis}[
+						xlabel={$x$},
+						ylabel={$y$},
+						grid=major,
+						title={Extended board},
+					]
+					\addplot[
+						only marks,
+					] table {data/extended_board.txt};
+				\end{axis}
+			\end{tikzpicture}
+		}
+	\end{minipage}
+	\caption{Board extension}
+\end{figure}
+
+\section{Classification}\label{sec:classification}
+
+\begin{minipage}[t]{0.3\linewidth}
+	We compared both responses, as discussed in \cref{sec:classifier}.
+	The Hessian proved to be more robust. The approach, proposed by
+	\cite{geigerAutomaticCameraRange2012} gave too many false positives,
+	especially for the edges.
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.6\linewidth}
+	\includegraphics[width=\linewidth]{response_hessian.png}
+	\captionof{figure}{Hessian response}
+	\includegraphics[width=\linewidth]{response_other.png}
+	\captionof{figure}{Response used by \cite{geigerAutomaticCameraRange2012}}
+	% \end{figure}
+\end{minipage}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[t]{\linewidth}
+		\includegraphics[width=\linewidth]{hist_response_hessian.png}
+		\caption{Histogram of Hessian response}
+	\end{subfigure}
+	\begin{subfigure}[t]{\linewidth}
+		\includegraphics[width=\linewidth]{hist_response_other.png}
+		\caption{Histogram of response used by \cite{geigerAutomaticCameraRange2012}}
+	\end{subfigure}
+	\caption{Distributions of the responses for the image on the
+		\cref{fig:extended_board_img}. Note the log y-scale! Most of the points have
+		the response 0.}
+\end{figure}
+
+\section{Evaluation}\label{sec:evaluation}
+
+\missingfigure{Compare the number of points with the provided by babelcalib}
+\missingfigure{Compare the reprojection error}

### 2023-05-28 paper/paper.tex
OMG it's horrible
WIP
Update the paper and the evaluation
2AM woo-hoo

@@
 \usepackage{subcaption}
+\usepackage{hyperref}
+\usepackage{enumitem}
+\usepackage{booktabs}
+\usepackage{amsmath}
+\usepackage{cleveref}
+\usepackage{xfrac}
+\usepackage{multicol}
+\usepackage{float}
+\usepackage{cases}
+\usepackage{pgfplots}
+\usepackage{pgf-pie}
 \graphicspath{ {images/} }
@@
 	\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-	The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
+	% The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
 
-	Camera calibration is a crucial step in many computer vision applications.
-  Typically, it involves taking a set of images of a calibration pattern,
-  detecting its' features, and estimating the camera parameters. However, under
-  certain conditions (including occlusions, bad lightning, highly distorted
-  images etc.), feature detectors might fail to detect some of the
-  features.\todo{Do I have to justify it?}.
-
-  In this paper, we propose a novel approach to feature detection in the context
-  of camera calibration. After the initial feature detection and calibration,
-  we use the intermediate camera parameters to predict the possible positions
-  of the previously undetected features. Those features are filtered using the
-  binary classifier, and the remaining features are used to further constrain
-  the camera calibration.
+	Current state-of-the-art techniques occasionally fail to accurately estimate
+	the camera parameters for wide-angle lenses, as most of the algorithms assume
+	lens with medium to small distortion. Partially it occurs due to extreme
+	distortion at the edges of the image, which poses additional challenges to
+	feature detection algorithms. We propose a novel approach for detecting
+	additional features on the imaged calibration pattern using intermediate
+	camera calibration. Utilizing the prior information about the calibration
+	pattern's geometry, we can estimate the possible positions of the previously
+	undetected features. Those features are filtered using the binary classifier,
+	and the remaining ones are used to further constrain the camera calibration.
+	The proposed method consists of three key steps: \((1)\) feature
+	detection and estimation of the lattice geometry, \((2)\) initial camera
+	calibration by solving the two-steps linear minimization problem, and \((3)\)
+	estimation the possible positions of the undetected features by projecting the
+	imputed and extended lattice geometry onto the image plane, and filtering them
+	using the binary classifier.
 
@@
 
+\include{Chapters/Plan}
 \include{Chapters/Chapter1}

### 2023-05-28 calibration/feature_detector/checkerboard.py

@@ -98,8 +98,8 @@ TPROPS = [
     [0, pi / 2],
     [pi / 4, -pi / 4],
     # [0, pi/4], [0, -pi/4],
-    [pi / 4, pi / 2],
-    [-pi / 4, pi / 2],
+    # [pi / 4, pi / 2],
+    # [-pi / 4, pi / 2],
 ]
 # [-3*pi/8, 3*pi/8], [-pi/8, pi/8],
 # [-pi/8, -3*pi/8], [pi/8, 3*pi/8]]
@@ -113,6 +113,9 @@ def detect_corners(gray, radiuses=RADIUS):
     for angle_1, angle_2 in TPROPS:
         for radius in radiuses:
             temp = create_correlation_patch(angle_1, angle_2, radius)
+            import plotly.express as px
+            # for t_i, t in enumerate(temp):
+            #     px.imshow(t, title=f"{angle_1=}, {angle_2=}, {radius=}, {t_i=}").show()
             corr = detect_corners_template(gray, temp)
             out = np.max([corr, out], axis=0)
 

### 2023-05-28 calibration/feature_refiner/classifier.py

@@ -1,7 +1,10 @@
 import numpy as np
 from PIL import ImageOps
 from PIL.Image import Image
+from cbdetect_py import hessian_response
 from tqdm.auto import tqdm
+from calibration.benchmark.benchmark_result import BenchmarkResult
+from calibration.data.babelcalib.entry import Entry
 from calibration.feature_detector.checkerboard import detect_corners
 import cv2
 from sklearn.cluster import MeanShift, estimate_bandwidth
@@ -104,7 +107,12 @@ def compute_orientation(img, positions, window_size):
 def prune_corners(
     corners: np.ndarray, mask: np.ndarray, image: Image, thr: float
 ) -> tuple[np.ndarray, np.ndarray]:
-    cornerness = detect_corners(np.array(ImageOps.grayscale(image)))
+    # cornerness = detect_corners(np.array(ImageOps.grayscale(image)))
+    cornerness = hessian_response(np.array(ImageOps.grayscale(image)))
+    if cornerness.shape[0] == image.size[1] // 2:
+        assert cornerness.shape[1] == image.size[0] // 2
+        cornerness = cornerness.repeat(2, axis=0).repeat(2, axis=1)
+    # assert cornerness.shape == ImageOps.grayscale(image).size
 
     corners = corners.astype(int)[mask]
     # 0: original, 1: new
@@ -127,3 +135,41 @@ def prune_corners(
     # 2 - new corner
     # 3 - out of image
     return responses, mask
+
+
+def get_corner_responses(r: BenchmarkResult):
+    assert isinstance(r.input, Entry)
+    assert r.input.image is not None
+    assert r.features is not None
+    cornerness = detect_corners(np.array(ImageOps.grayscale(r.input.image)))
+    # cornerness = hessian_response(np.array(ImageOps.grayscale(r.input.image)))
+    if cornerness.shape[0] == r.input.image.size[1] // 2:
+        assert cornerness.shape[1] == r.input.image.size[0] // 2
+        cornerness = cornerness.repeat(2, axis=0).repeat(2, axis=1)
+
+    corners = r.features.corners.astype(int)
+
+    # Preparing output array
+    outputs = []
+
+    # Padding image to handle edge cases
+    pad_image = np.pad(cornerness, ((5, 5), (5, 5)), mode="constant")
+
+    # Shifting corners because of padding
+    corners += 5
+
+    # Iterate over corners
+    for corner in corners:
+        x, y = corner
[…]

### 2023-05-28 calibration/feature_refiner/refine.py

@@ -36,7 +36,7 @@ def view1D(a, b):  # a, b are arrays
 
 def refine_features_single(
     r: BenchmarkResult, solver_name: str="Optimization", pan_size: int = 1,
-    thr=28.7
+    thr=0.0019
 ) -> RefinedResult | None:
     assert isinstance(r.input, Entry) and r.input.image is not None
     board = r.features.board.astype(int)

### 2023-05-28 calibration/feature_refiner/visualization.py

@@ -20,8 +20,15 @@ def show_refined_corners(
         3: "out of image",
     }
 
+    mask_mapping = {
+        0: "Original feature",
+        1: "Possible new feature",
+        2: "Possible new feature",
+        3: "Possible new feature",
+    }
+
     responses_all = np.full_like(mask, -1)
-    # responses_all[(mask > 0) & (mask < 3)] = responses
+    responses_all[(mask > 0) & (mask < 3)] = responses
     points = [
         {
             "n": i,
@@ -40,6 +47,7 @@ def show_refined_corners(
     fig2 = px.scatter(
         # df, x="x", y="y", color="resp", symbol="mask", hover_data=["i", "j"]
         df, x="x", y="y", color="mask", hover_data=["i", "j", "resp"]
-    )
+        # df, x="x", y="y", hover_data=["i", "j", "resp"]
+    ).update_traces(marker=dict(size=12))
     assert isinstance(fig1.data, tuple) and isinstance(fig2.data, tuple)
     return go.Figure(data=fig1.data+ fig2.data)

### 2023-05-28 calibration/solver/optimization/optimize.py

@@ -102,17 +102,17 @@ def optimize_optax(
                 fx, fy = params["focal_length"] / pixel_size
                 cx, cy = resolution / 2
                 intrinsic_matrix = jnp.array([[fx, 0, cx], [0, fy, cy], [0, 0, 1]])
-                print(f"R: {np.linalg.norm(R - proj_.R)}, "
-                      f"t: {np.linalg.norm(t - proj_.t)}, "
-                      f"lambdas: {np.linalg.norm(lambdas - proj_.lambdas)}, "
-                      f"intrinsics: {np.linalg.norm(intrinsic_matrix - proj_.camera.intrinsic_matrix)}")
-                print(f"Resolution: {np.linalg.norm(resolution - proj_.camera.resolution)}"
-                      f"Sensor size: {np.linalg.norm(params['sensor_size'] - proj_.camera.sensor_size)}"
-                      f"Focal length: {np.linalg.norm(params['focal_length'] - proj_.camera.focal_length)}"
-                      f"Skew: {proj_.camera.skew}")
+                # print(f"R: {np.linalg.norm(R - proj_.R)}, "
+                #       f"t: {np.linalg.norm(t - proj_.t)}, "
+                #       f"lambdas: {np.linalg.norm(lambdas - proj_.lambdas)}, "
+                #       f"intrinsics: {np.linalg.norm(intrinsic_matrix - proj_.camera.intrinsic_matrix)}")
+                # print(f"Resolution: {np.linalg.norm(resolution - proj_.camera.resolution)}"
+                #       f"Sensor size: {np.linalg.norm(params['sensor_size'] - proj_.camera.sensor_size)}"
+                #       f"Focal length: {np.linalg.norm(params['focal_length'] - proj_.camera.focal_length)}"
+                #       f"Skew: {proj_.camera.skew}")
 
                 board__ = backproject(corners, R, t, lambdas, intrinsic_matrix)
-                print(f"Board error: {np.linalg.norm(board_ - board__)}")
+                # print(f"Board error: {np.linalg.norm(board_ - board__)}")
                 board_error = np.linalg.norm(board_ - board)
                 # print(f"Board error: {np.linalg.norm(board_ - board)}")
 
@@ -123,12 +123,12 @@ def optimize_optax(
                     jnp.abs(board_ - board) * (1 + weights * 10).reshape(-1, 1)
                 )
 
-                print(
-                    f"iteration: {i}, loss {loss_val}/{np.array(loss_)}, phase: {phase}, "
[…]

### 2023-05-28 calibration/solver/optimization/solve.py

@@ -54,5 +54,5 @@ def solve(corners: nArr, board: nArr, camera: Camera) -> Projector | None:
     # losses = [backprojection_loss(params, *args) for params in paramss]
     # params = paramss[np.argmin(losses)]
     ret = params_to_proj(params, resolution)
-    print(f"Final error: {calc_error(ret, Features(board, corners)):0.3f}")
+    # print(f"Final error: {calc_error(ret, Features(board, corners)):0.3f}")
     return ret, hist

### 2023-05-28 main.py

@@ -16,8 +16,8 @@ from calibration.solver.optimization.solve import solve
 
 
 def run_benchmark():
-    # for aug in [None, "overlay", "prune_corners"]:
-    for aug in [None]:
+    for aug in [None, "overlay", "prune_corners"]:
+    # for aug in [None]:
         path = f"babelcalib_results_{aug}.pkl"
         if True or not os.path.isfile(path):
             # babelcalib_results = benchmark_babelcalib(aug=aug)

### 2023-05-28 paper/Chapters/Chapter1.tex
2AM woo-hoo
WIP paper

@@
 methods
-\citep{olsonAprilTagRobustFlexible2011a, schopsWhyHaving102020,
+\citep{olsonAprilTagRobustFlexible2011, schopsWhyHaving102020,
 	krogiusFlexibleLayoutsFiducial2019}
@@
 the accuracy of the calibration parameters.
-\todo{Explain why more features is better}
-\missingfigure{Show the example of the calibration board and the image}
+
+\begin{figure}
+	\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=3cm, connect spies}]
+		\node[anchor=south west,inner sep=0] (image) at (0,0)
+    % {\includegraphics[width=0.6\textwidth]{distorted_image}};
+    {\includegraphics[width=0.8\textwidth]{distorted_image}};
+		\begin{scope}[x={(image.south east)},y={(image.north west)}]
+			\spy[red] on (3.3,1.7) in node [left] at (10.1,1.7);
+			\spy[blue] on (4.6,3.2) in node [right] at (8.1,5.3);
+		\end{scope}
+	\end{tikzpicture}
+  \caption{Example of corners near the center of the image and near the edge}
+\end{figure}
 

### 2023-05-28 paper/paper.tex
WIP paper

@@
 singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
-%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
+draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
 %nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
@@
 \usepackage{pgf-pie}
+\usetikzlibrary{spy,arrows}
 \graphicspath{ {images/} }
@@
 
-\include{Chapters/Plan}
+% \include{Chapters/Plan}
 \include{Chapters/Chapter1}

### 2023-05-28 calibration/feature_refiner/classifier.py

@@ -109,6 +109,8 @@ def prune_corners(
 ) -> tuple[np.ndarray, np.ndarray]:
     # cornerness = detect_corners(np.array(ImageOps.grayscale(image)))
     cornerness = hessian_response(np.array(ImageOps.grayscale(image)))
+    import plotly.express as px
+    px.imshow(cornerness).show()
     if cornerness.shape[0] == image.size[1] // 2:
         assert cornerness.shape[1] == image.size[0] // 2
         cornerness = cornerness.repeat(2, axis=0).repeat(2, axis=1)
@@ -141,8 +143,8 @@ def get_corner_responses(r: BenchmarkResult):
     assert isinstance(r.input, Entry)
     assert r.input.image is not None
     assert r.features is not None
-    cornerness = detect_corners(np.array(ImageOps.grayscale(r.input.image)))
-    # cornerness = hessian_response(np.array(ImageOps.grayscale(r.input.image)))
+    # cornerness = detect_corners(np.array(ImageOps.grayscale(r.input.image)))
+    cornerness = hessian_response(np.array(ImageOps.grayscale(r.input.image)))
     if cornerness.shape[0] == r.input.image.size[1] // 2:
         assert cornerness.shape[1] == r.input.image.size[0] // 2
         cornerness = cornerness.repeat(2, axis=0).repeat(2, axis=1)

### 2023-05-28 calibration/feature_refiner/visualization.py

@@ -20,12 +20,12 @@ def show_refined_corners(
         3: "out of image",
     }
 
-    mask_mapping = {
-        0: "Original feature",
-        1: "Possible new feature",
-        2: "Possible new feature",
-        3: "Possible new feature",
-    }
+    # mask_mapping = {
+    #     0: "Original feature",
+    #     1: "Possible new feature",
+    #     2: "Possible new feature",
+    #     3: "Possible new feature",
+    # }
 
     responses_all = np.full_like(mask, -1)
     responses_all[(mask > 0) & (mask < 3)] = responses
@@ -48,6 +48,6 @@ def show_refined_corners(
         # df, x="x", y="y", color="resp", symbol="mask", hover_data=["i", "j"]
         df, x="x", y="y", color="mask", hover_data=["i", "j", "resp"]
         # df, x="x", y="y", hover_data=["i", "j", "resp"]
-    ).update_traces(marker=dict(size=12))
+    ).update_traces(marker=dict(size=6))
     assert isinstance(fig1.data, tuple) and isinstance(fig2.data, tuple)
     return go.Figure(data=fig1.data+ fig2.data)

### 2023-05-29 paper/Chapters/Chapter1.tex
WIP on paper

@@
 calibration pattern, which is then used to estimate the camera parameters.
-Alternatively, some methods do not use a calibration pattern but instead infer
+Alternatively, some methods do not use a calibration pattern but instead, infer
 geometric constraints directly from the scene. However, this approach is
@@
 
-This additional points will further constrain the camera calibration, improving
+These additional points will further constrain the camera calibration, improving
 the accuracy of the calibration parameters.
@@
 	\end{tikzpicture}
-  \caption{Example of corners near the center of the image and near the edge}
+	\caption{Example of corners near the center of the image and the edge}
 \end{figure}
@@
 \todo{Update}
-
-\endinput
+\todo{add the link to the repo}

### 2023-05-29 paper/Chapters/Chapter2.tex
WIP on paper

@@
 camera calibration pipeline. The detection accuracy directly affects the
-calibration accuracy. Besides the feature detection, it's also important to
+calibration accuracy. Besides feature detection, it's also important to
 associate the detected features with the board's corners.
 
-There are various of the feature detection methods. Many of them require
+There are various feature detection methods. Many of them require
 prior knowledge of the board's geometry, such as the number of rows and columns,
@@
 \cite{fuersattelOCPADOccludedCheckerboard2016} and
-\cite{geigerAutomaticCameraRange2012}. Those method can detect the board and
+\cite{geigerAutomaticCameraRange2012}. Those methods can detect the board and
 associate the corners with the borders' corners under

### 2023-05-29 paper/Chapters/Chapter4.tex
WIP paper
WIP on paper

@@
 
-For the feature detection, we used the approach, proposed by
+For feature detection, we used the approach, proposed by
 \cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
@@
 used the approach, proposed by \cite{scaramuzzaToolboxEasilyCalibrating2006} to
-obtain the initial approximation of the camera parameters. Then, we used the
+obtain the initial approximation of the camera parameters. Then, we used 
 optimization to minimize the reprojection error between the board and the
-back-projected corners. A division model is very powerful, and is able to
-express a wide number of range of distortions
+back-projected corners. A division model is very powerful and can
+express a wide range of distortions
 \citep{prittsMinimalSolversRectifying2021}. In this work, we used a model with
-two parameters to allow for a better flexibility during the optimization.
+two parameters to allow for better flexibility during the optimization.
 
@@
 
-In this work, we focused on the single image, while the original approach relied
-on the multiple images. Therefore, we used only the first two steps of the
+In this work, we focused on a single image, while the original approach relied
+on multiple images. Therefore, we used only the first two steps of the
 algorithm.
@@
 \end{pmatrix}^{T}\) of the corner, which is associated with the board's corner
-with corrdinates \(\begin{pmatrix}
+with coordinates \(\begin{pmatrix}
 	0, 0
@@
 same \(t_1\) and \(t_2 \), but different \(r_{11}\), \(r_{12}\), \(r_{21}\). To
-find the best matrix, we found the intrinsic values for each of them, and
-backprojected the board's corners using both matrices.
+find the best matrix, we found the intrinsic values for each of them and
+back-projected the board's corners using both matrices.
 Then, we used the one which gave the smallest reprojection error.
@@
 using the Scaramuzza solver, unless the initial guess was very degenerate (i.e.
-\(R\) was such that the board plane passed through the principal point, and all
-backprojected points were projected onto the same line).
+\(R\) was such that the board plane passed through the principal point and all
+back-projected points were projected onto the same line).
 
-This issue also occured with random small initial values, due to the best
+This issue also occurred with random small initial values, due to the best
 approximation for \(R\) which minimizes \(L\) when the distance from the
-back-projected board from the measure one was high (i.e., the \(t\) was far from
+back-projected board from measure one was high (i.e., the \(t\) was far from
 the true value) being the degenerate solution\todo{Am I using the term
-	correctly?}. In order to avoid this issue, we first optimized only the \(t\),
+	correctly?}. To avoid this issue, we first optimized only the \(t\),
 until the loss function converged, meaning that \(t\) is close to the true
@@
 \(180^{\circ}\), \(R\) once again converged to the degenerate solution. In order
-to avoid this issue, we found the solution with initial \(\theta_z\) set to
+to avoid this issue, we found the solution with the initial \(\theta_z\) set to
 value, close to \(0^{\circ}\) and \(180^{\circ}\), and then used the solution
@@
 assumed that the whole board was detected, and imputed the missing points in the
-board space.\todo{Add ref to the figure}. Then, we tried extending the board
+board space \cref{fig:extended_board_img}. Then, we tried extending the board
 points.
@@
 response function at the previously detected corners, and around them.
-We didn't collect the values of all of the pixels, in order to reduce the number
+We didn't collect the values of all of the pixels, to reduce the number
 of very simple examples.
@@
 
-We used both of the approaches to train the classifier, and compared the
+We used both approaches to train the classifier and compared the
 results in \cref{sec:classification}.

### 2023-05-29 paper/Chapters/Chapter5.tex
WIP on paper

@@
 
-We created a symulator to generate distorted points as described in
+We created a simulator to generate distorted points as described in
 \cref{sub:complete_projection_and_backprojection}. We used it to test the
-solver, and test the correctness of projection and back-projection points.
+solver and test the correctness of projection and back-projection points.
+However, since the simulator used the same camera model as the solver, the
+initial camera calibration was perfect.
 
@@
 
-\begin{itemize}
-	\item Reprojection error
-	\item Number of detected corners
-\end{itemize}
+As noted by \cite{duisterhofTartanCalibIterativeWideAngle2022}, the evaluation
+of the camera calibration is not straightforward. No ground truth exists for
+feature detection or camera calibration.
+
+Typically, the reprojection error is used as a metric for the camera
+calibration, but it depends on multiple factors: type of the calibration
+pattern, the camera model, and the types of the lens.
+
+Also, by using more features, we can get better calibration, as we have more
+constraints, but the reprojection error might be higher.
+
+As currently the algorithm only supports processing a single checkerboard, we
+cannot compare to \cite{duisterhofTartanCalibIterativeWideAngle2022}, which uses
+AprilTags, nor to the \cite{lochmanBabelCalibUniversalApproach2021}, who
+provides the detected corners for all of the boards.
+\todo{Should I maybe tell less about it?}
+
+Because of that, we instead artificially removed some of the points from the
+detections, to ensure that we can recover them. We also created
+artificially occluded points by overlaying a separate image, as it poses
+problems for the feature detector.
+
+Lastly, we evaluated the newly detected points on real-world datasets.
 
@@
 For this project, we required a highly distorted dataset of chessboard images.
-We collected a number of datasets, but the feature detector we used supports
+We collected several datasets, but the feature detector we used supports
 detecting only the boards with the constant tile size, therefore we cannot use
@@
 dataset from the TartanCalib project. Currently, the dataset contains only
-AprilGrid patterns, as the toolchain doesn't support chessboard.
+AprilGrid patterns, as the toolchain doesn't support a chessboard.
 
@@
 \begin{minipage}{0.5\linewidth}
-	In order to get accurate predictions for the possibly missing points, we need
+	To get accurate predictions for the possibly missing points, we need
 	very accurate camera calibration. We used the reprojection error as a metric
 	for the calibration quality.
-	In order to calculate the reprojection error, we have to perform the
+	To calculate the reprojection error, we have to perform the
 	rootfinding \cref{subsub:back_projection_using_the_division_model}. We assume
@@
 	a little bit (we use the constant \(1.1\) of the maximum radius). If the
-	camera calibration is poor, the rootfinding might fail. On the initial
-	calibration the number of the failed rootfindings was much higher.
+	camera calibration is poor, the root-finding might fail. On the initial
+	calibration the number of the failed root-findings was much higher.
 \end{minipage}
@@
 
-\begin{figure}[h]
-	\begin{tikzpicture}
-		\begin{axis}[
-				ybar interval,
-				ymin=0,
-				ylabel={Frequency},
-				xlabel={Value},
-				height=0.3\linewidth,
-				width=\linewidth,
-				ticklabel style = {font=\tiny},
-				% title={Initial calibration}
-			]
-			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
-				% \addplot+ [hist={bins=30}] table [y index=0]
-				{data/reprojection_error_init.txt};
-		\end{axis}
-	\end{tikzpicture}
-	\caption{Initial calibration's reprojection error histogram}
-\end{figure}
-\begin{figure}[h]
-	\begin{tikzpicture}
-		\begin{axis}[
-				ybar interval,
-				ymin=0,
-				ylabel={Frequency},
-				xlabel={Value},
-				height=0.3\linewidth,
-				width=\linewidth,
-				ticklabel style = {font=\tiny},
-				% title={Reprojection error}
-			]
-			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
-				% \addplot+ [hist={bins=30}] table [y index=0]
-				{data/reprojection_error_final.txt};
-		\end{axis}
-	\end{tikzpicture}
-	\caption{Final calibration's reprojection error histogram}
-\end{figure}
+% \begin{figure}[h]
+% 	\begin{tikzpicture}
+% 		\begin{axis}[
+% 				ybar interval,
+% 				ymin=0,
+% 				ylabel={Frequency},
+% 				xlabel={Value},
+% 				height=0.3\linewidth,
+% 				width=\linewidth,
+% 				ticklabel style = {font=\tiny},
+% 				% title={Initial calibration}
+% 			]
+% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
+% 				% \addplot+ [hist={bins=30}] table [y index=0]
+% 				{data/reprojection_error_init.txt};
+% 		\end{axis}
+% 	\end{tikzpicture}
+% 	\caption{Initial calibration's reprojection error histogram}
+% \end{figure}
+% \begin{figure}[h]
+% 	\begin{tikzpicture}
+% 		\begin{axis}[
+% 				ybar interval,
+% 				ymin=0,
+% 				ylabel={Frequency},
+% 				xlabel={Value},
+% 				height=0.3\linewidth,
+% 				width=\linewidth,
+% 				ticklabel style = {font=\tiny},
+% 				% title={Reprojection error}
+% 			]
+% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
+% 				% \addplot+ [hist={bins=30}] table [y index=0]
+% 				{data/reprojection_error_final.txt};
+% 		\end{axis}
+% 	\end{tikzpicture}
+% 	\caption{Final calibration's reprojection error histogram}
+% \end{figure}
+\todo{Add data and enable}
 
@@
 
+\subsection{Recovery of artificially removed points}\label{sub:recovery_of_artificially_removed_points}
+
+We removed 20\% of the points from the original board, and then tried to recover
+them.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{refined_pruned_corners.png}
+  \caption{Recovered occluded points}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Initial calibration}
+			]
+			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/pruned_number_of_features.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Initial calibration's reprojection error histogram}
+\end{figure}
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Reprojection error}
+			]
+			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/recovered_pruned_number_of_features.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Final calibration's reprojection error histogram}
+\end{figure}
+
+\subsection{Performance under occlusion}\label{sub:performance_under_occlusion}
+
+Occlusions pose additional complications for the feature detection. We added an
+image on top of the board, and tried to recover additional points. Often the
+initial feature detector failed to detect points near the occlusion.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{refined_overlayed_corners.png}
+  \caption{Recovered occluded points}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Initial calibration}
+			]
+			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/occluded_number_of_features.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Initial calibration's reprojection error histogram}
+\end{figure}
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Reprojection error}
+			]
+			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/recovered_occluded_number_of_features.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Final calibration's reprojection error histogram}
+\end{figure}
+
+\subsection{Recovery of previously undetected points}\label{sub:recovery_of_previously_undetected_points}
+
 \missingfigure{Compare the number of points with the provided by babelcalib}

### 2023-05-29 paper/Chapters/Chapter6.tex
WIP on paper

\chapter{Conclusions}\label{cha:conclusions}

In this thesis, we have presented a new approach for feature detection
improvement. We used the feature detector, proposed by
\cite{geigerAutomaticCameraRange2012}, to detect the initial features. Then, we
found the camera calibration for the camera model, proposed by
\cite{scaramuzzaToolboxEasilyCalibrating2006}, and then improved it by
minimizing the reprojection error between the back-projection of the detected
features and the board. Lastly, we used the improved camera calibration to
project the imputed and extended board back into the image and used a binary
classification to find the previously undetected features. We tested the method
on a real-world dataset and showed that it can improve the feature detection.

\subsection{Future work}\label{sub:future_work}

The method, presented in this thesis can be improved in several ways. First, the
feature detection algorithm can be tweaked to use alternating step sizes while
constructing the board. It would allow to also match other types of the boars,
such as ArUco or AprilTag. Second, the method can be extended to multiple boards
on the same image, and multiple images. It would improve the robustness of the
camera calibration, and reduce the number of detected points on the wrong board
when there is overlap. Lastly, additional improvements can be made to the corner
classification algorithm, specifically to the response function. One thing that
could work is resizing the image, to find the corners of different sizes.

### 2023-05-29 paper/paper.tex
WIP on paper

--- 2023-05-28 paper/paper.tex
@@
 singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
-%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
+% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
 %nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
@@
 	the camera parameters for wide-angle lenses, as most of the algorithms assume
-	lens with medium to small distortion. Partially it occurs due to extreme
+	lenses with medium to small distortion. Partially it occurs due to extreme
 	distortion at the edges of the image, which poses additional challenges to

### 2023-05-29 calibration/benchmark/calib.py

@@ -33,6 +33,7 @@ def calibrate(
         partial(_calibrate_helper, solvers=solvers),
         feature_and_camera,
         chunksize=10,
+        max_workers=8,
         leave=False,
         desc="Calibrating",
     )

### 2023-05-29 calibration/feature_refiner/classifier.py

@@ -109,8 +109,8 @@ def prune_corners(
 ) -> tuple[np.ndarray, np.ndarray]:
     # cornerness = detect_corners(np.array(ImageOps.grayscale(image)))
     cornerness = hessian_response(np.array(ImageOps.grayscale(image)))
-    import plotly.express as px
-    px.imshow(cornerness).show()
+    # import plotly.express as px
+    # px.imshow(cornerness).show()
     if cornerness.shape[0] == image.size[1] // 2:
         assert cornerness.shape[1] == image.size[0] // 2
         cornerness = cornerness.repeat(2, axis=0).repeat(2, axis=1)

### 2023-05-29 calibration/feature_refiner/visualization.py

@@ -44,10 +44,29 @@ def show_refined_corners(
         )
     ]
     df = pd.DataFrame(points)
+    colors = [
+        "#1f77b4",  ## muted blue
+        "#ff7f0e",  ## safety orange
+        "#2ca02c",  ## cooked asparagus green
+        "#d62728",  ## brick red
+        "#9467bd",  ## muted purple
+        "#8c564b",  ## chestnut brown
+        "#e377c2",  ## raspberry yogurt pink
+        "#7f7f7f",  ## middle gray
+        "#bcbd22",  ## curry yellow-green
+        "#17becf",  ## blue-teal
+    ]
+
     fig2 = px.scatter(
         # df, x="x", y="y", color="resp", symbol="mask", hover_data=["i", "j"]
-        df, x="x", y="y", color="mask", hover_data=["i", "j", "resp"]
+        df,
+        x="x",
+        y="y",
+        color="mask",
+        hover_data=["i", "j", "resp"],
         # df, x="x", y="y", hover_data=["i", "j", "resp"]
-    ).update_traces(marker=dict(size=6))
+        color_discrete_sequence=colors,
+        category_orders={"mask": list(mask_mapping.values())},
+    ).update_traces(marker=dict(size=10))
     assert isinstance(fig1.data, tuple) and isinstance(fig2.data, tuple)
-    return go.Figure(data=fig1.data+ fig2.data)
+    return go.Figure(data=fig1.data + fig2.data)

### 2023-05-29 calibration/solver/optimization/optimize.py

@@ -19,23 +19,24 @@ def optimize_optax(
     board: jArr,
     resolution: jArr,
     # step_size=0.001,
-    step_size=0.05,
-    patience=1000,
+    step_size=0.005,
+    patience=100,
 ) -> dict[str, jArr]:
     # optimizer = optax.rmsprop(step_size)
     # optimizer = optax.adam(step_size)
+    optimizer = optax.amsgrad(step_size)
     # schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.05, 1000, 2000,
     #                                               0.001)
 
-    schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.000001)
-    schedule2 = optax.warmup_cosine_decay_schedule(
-        0.000001, 0.001, 1000, 5000, 0.000001
-    )
+    # schedule1 = optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.000001)
+    # schedule2 = optax.warmup_cosine_decay_schedule(
+    #     0.000001, 0.001, 1000, 5000, 0.000001
+    # )
     # schedule2=    optax.warmup_cosine_decay_schedule(0.001, 0.1, 1000, 5000, 0.001)
-    schedule = optax.join_schedules([schedule1, schedule2], [5000] * 1)
+    # schedule = optax.join_schedules([schedule1, schedule2], [5000] * 1)
     # schedule = optax.join_schedules([schedule1, schedule2], [5000])
     # optimizer = optax.amsgrad(step_size)
-    optimizer = optax.amsgrad(schedule)
+    # optimizer = optax.amsgrad(schedule)
 
     phase_l = [
         ["t", "theta_z"],
@@ -82,46 +83,46 @@ def optimize_optax(
             i, params, opt_state, loss_history, phase
         )
         loss_val = loss_history[i % patience]
-        if i % 1000 == 0:
-            proj_ = params_to_proj(params.copy(), np.array(resolution))
-            if proj_ is not None:
-                try:
-                    corners_ = proj_.project(np.array(board))
-                    corners_error = np.linalg.norm(corners_ - corners)
-                    # print(f"Corners error: {np.linalg.norm(corners_ - corners)}")
-                except Exception:
-                    corners_error = np.inf
-                    # print("failed projecting")
-                board_ = proj_.backproject(np.array(corners).astype(np.float32))
[…]

### 2023-05-29 paper/paper.tex
Updates

@@
 
-% \begin{declaration}
-% 	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
-% 	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
-%
-% 	\begin{itemize}
-% 		\item This work was done wholly or mainly while in candidature for a research degree at this University.
-% 		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
-% 		\item Where I have consulted the published work of others, this is always clearly attributed.
-% 		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
-% 		\item I have acknowledged all main sources of help.
-% 		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
-% 	\end{itemize}
-%
-% 	\noindent Signed:\\
-% 	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
-%
-% 	\noindent Date:\\
-% 	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
-% \end{declaration}
-%
-% \cleardoublepage
-\todo{Enable}
+\begin{declaration}
+	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
+	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
+
+	\begin{itemize}
+		\item This work was done wholly or mainly while in candidature for a research degree at this University.
+		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
+		\item Where I have consulted the published work of others, this is always clearly attributed.
+		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
+		\item I have acknowledged all main sources of help.
+		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
+	\end{itemize}
+
+	\noindent Signed:\\
+	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
+
+	\noindent Date:\\
+	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
+\end{declaration}
+
+\cleardoublepage
 
@@
 %
-% \noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
+% \noindent\enquote{\itshape Thanks to my solid academic training, today I can
+% write hundreds of words on virtually any topic without possessing a shred of
+% information, which is how I got a good job in journalism.}\bigbreak
 %
 % \hfill Dave Barry
-\todo{Enable}
 
@@
 	detection and estimation of the lattice geometry, \((2)\) initial camera
-	calibration by solving the two-steps linear minimization problem, and \((3)\)
-	estimation the possible positions of the undetected features by projecting the
+	calibration by solving the two-step linear minimization problem, and \((3)\)
+	estimation of the possible positions of the undetected features by projecting the
 	imputed and extended lattice geometry onto the image plane, and filtering them
@@
 
-% \begin{acknowledgements}
-% 	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
+\begin{acknowledgements}
+	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
+  I wish to thank the Armed Forces of Ukraine for protecting us. Thanks to those
+  brave people I was able to study and work on this thesis. I want to thank my
 	% The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
-%
+
 	% \noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
-% \end{acknowledgements}
-\todo{Enable}
+\end{acknowledgements}
 

### 2023-05-29 paper/Chapters/Chapter1.tex
WIP

@@
 
-This paper has the following structure: in \autoref{sec:related_work}, we will describe the related work, including the
-literature search method and methodology, various subtopics of the camera
-calibration, mention conjugate translations, and outline the state-of-the-art
-solutions. We define the research gap in \autoref{sec:gap_analysis} and outline
-the proposed approach to solution and evaluation in
-\autoref{sec:problem_setting_and_approach_to_solution}. We will describe the
-early results in \autoref{sec:early_results_and_discussion}, including the
-dataset analysis, feature detector, and conjugately translated points simulator.
-In \autoref{sec:summary_and_future_work}, we will summarize the results and
-outline future work.
-\todo{Update}
-\todo{add the link to the repo}
+This paper has the following structure: in \cref{related_work}, we will describe
+various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
+In \cref{cha:background}, we will describe the key concepts of the camera
+calibration. Also, there we provide additional details on the underlying math,
+for example, the derivation of the division model invertion. In
+\cref{cha:approach}, we will describe the steps of the proposed method in
+details, including the feature detection, initial camera calibration, camera
+parameters estimation via minimization of the reprojection error, and the
+process of searching and filtering the previously undetected features. In
+\cref{Experiments}, we will describe the metrics we used, provide details about
+the datasets, show the results of each of the algorithm's steps, and evaluate it
+on multiple metrics. Finally, in \cref{cha:conclusions}, we will summarize the
+results and outline future work.

### 2023-05-29 paper/Chapters/Chapter5.tex
WIP

@@
 
-% \begin{figure}[h]
-% 	\begin{tikzpicture}
-% 		\begin{axis}[
-% 				ybar interval,
-% 				ymin=0,
-% 				ylabel={Frequency},
-% 				xlabel={Value},
-% 				height=0.3\linewidth,
-% 				width=\linewidth,
-% 				ticklabel style = {font=\tiny},
-% 				% title={Initial calibration}
-% 			]
-% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
-% 				% \addplot+ [hist={bins=30}] table [y index=0]
-% 				{data/reprojection_error_init.txt};
-% 		\end{axis}
-% 	\end{tikzpicture}
-% 	\caption{Initial calibration's reprojection error histogram}
-% \end{figure}
-% \begin{figure}[h]
-% 	\begin{tikzpicture}
-% 		\begin{axis}[
-% 				ybar interval,
-% 				ymin=0,
-% 				ylabel={Frequency},
-% 				xlabel={Value},
-% 				height=0.3\linewidth,
-% 				width=\linewidth,
-% 				ticklabel style = {font=\tiny},
-% 				% title={Reprojection error}
-% 			]
-% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
-% 				% \addplot+ [hist={bins=30}] table [y index=0]
-% 				{data/reprojection_error_final.txt};
-% 		\end{axis}
-% 	\end{tikzpicture}
-% 	\caption{Final calibration's reprojection error histogram}
-% \end{figure}
-\todo{Add data and enable}
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Initial calibration}
+			]
+			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/reprojection_error_init.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Initial calibration's reprojection error histogram}
+\end{figure}
+\begin{figure}[h]
+	\begin{tikzpicture}
+		\begin{axis}[
+				ybar interval,
+				ymin=0,
+				ylabel={Frequency},
+				xlabel={Value},
+				height=0.3\linewidth,
+				width=\linewidth,
+				ticklabel style = {font=\tiny},
+				% title={Reprojection error}
+			]
+			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
+				% \addplot+ [hist={bins=30}] table [y index=0]
+				{data/reprojection_error_final.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Final calibration's reprojection error histogram}
+\end{figure}
 
@@
 	\centering
-	\begin{subfigure}[t]{\linewidth}
+	\begin{subfigure}[t]{0.45\linewidth}
 		\includegraphics[width=\linewidth]{hist_response_hessian.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[t]{\linewidth}
+	\begin{subfigure}[t]{0.45\linewidth}
 		\includegraphics[width=\linewidth]{hist_response_other.png}
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{refined_pruned_corners.png}
-  \caption{Recovered occluded points}
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[h]{0.45\linewidth}
+		\begin{tikzpicture}
+			\begin{axis}[
+					ybar interval,
+					ymin=0,
+					ylabel={Frequency},
+					xlabel={Value},
+					height=0.5\linewidth,
+					width=\linewidth,
+					ticklabel style = {font=\tiny},
+					title={Histogram of the points before refinement}
+				]
+				\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
+					% \addplot+ [hist={bins=30}] table [y index=0]
+					{data/pruned_number_of_features.txt};
+			\end{axis}
+		\end{tikzpicture}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[h]{0.45\linewidth}
+		% \centering
+		\begin{tikzpicture}
+			\begin{axis}[
+					ybar interval,
+					ymin=0,
+					ylabel={Frequency},
+					xlabel={Value},
+					height=0.5\linewidth,
+					width=\linewidth,
+					ticklabel style = {font=\tiny},
+					title={Histogram of the points after refinement}
+				]
+				\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
+					% \addplot+ [hist={bins=30}] table [y index=0]
+					{data/recovered_pruned_number_of_features.txt};
+			\end{axis}
+		\end{tikzpicture}
+	\end{subfigure}
+	\begin{subfigure}[h]{\linewidth}
+		\centering
+		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
+		\caption{Recovered pruned points
+			(\textcolor[HTML]{1f77b4}{unchanged}
+			\textcolor[HTML]{ff7f0e}{filtered out}
+			\textcolor[HTML]{2ca02c}{new corner}
+			\textcolor[HTML]{d62728}{out of image})}
+	\end{subfigure}
+	\hfill
+	\caption{Feature refinement on the board with 80\% of the points}
 \end{figure}
+
+\newpage
+\subsection{Performance under occlusion}\label{sub:performance_under_occlusion}
+
+Occlusions pose additional complications for the feature detection. We added an
+image on top of the board, and tried to recover additional points. Often the
+initial feature detector failed to detect points near the occlusion.
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[h]{0.45\linewidth}
+		\begin{tikzpicture}
+			\begin{axis}[
+					ybar interval,
+					ymin=0,
+					ylabel={Frequency},
+					xlabel={Value},
+					height=0.5\linewidth,
+					width=\linewidth,
+					ticklabel style = {font=\tiny},
+					title={Histogram of the points before the refinement}
+				]
+				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+					% \addplot+ [hist={bins=30}] table [y index=0]
+					{data/occluded_number_of_features.txt};
+			\end{axis}
+		\end{tikzpicture}
+		\caption{}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[h]{0.45\linewidth}
+		% \centering
+		\begin{tikzpicture}
+			\begin{axis}[
+					ybar interval,
+					ymin=0,
+					ylabel={Frequency},
+					xlabel={Value},
+					height=0.5\linewidth,
+					width=\linewidth,
+					ticklabel style = {font=\tiny},
+					title={Histogram of the points after the refinement}
+				]
+				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+					% \addplot+ [hist={bins=30}] table [y index=0]
+					{data/recovered_occluded_number_of_features.txt};
+			\end{axis}
+		\end{tikzpicture}
+	\end{subfigure}
+	\begin{subfigure}[h]{\linewidth}
+		\centering
+		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
+		\caption{Recovered pruned points
+			(\textcolor[HTML]{1f77b4}{unchanged}
+			\textcolor[HTML]{ff7f0e}{filtered out}
+			\textcolor[HTML]{2ca02c}{new corner}
+			\textcolor[HTML]{d62728}{out of image})}
+	\end{subfigure}
+	\hfill
+	\caption{Feature refinement on the board with partial board occlusion}
+\end{figure}
+
+\newpage
+\subsection{Recovery of previously undetected points}\label{sub:recovery_of_previously_undetected_points}
+
+\begin{minipage}[t]{0.3\linewidth}
+	Lastly, we recovered the points that were not detected by the initial feature
+	detector.
+	From a visual inspection, most of the points were recovered correctly
+	\cref{fig:recovered_good_points}.
+	On the top image, for example, there are green points close to the edge.
+	Those corners weren't detected initially due to high distortion. On the bottom
+	image, the algorithm found another row of the corners, which weren't detected previously.
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.6\linewidth}
+	\includegraphics[width=\linewidth]{refined_corners1.png}
+	\includegraphics[width=\linewidth]{refined_corners2.png}
+
+	\captionof{figure}{Recovered points
+		(\textcolor[HTML]{1f77b4}{unchanged}
+		\textcolor[HTML]{ff7f0e}{filtered out}
+		\textcolor[HTML]{2ca02c}{new corner}
+		\textcolor[HTML]{d62728}{out of image})}
+	\label{fig:recovered_good_points}
+\end{minipage}
+
+\begin{minipage}[t]{0.3\linewidth}
+	However,
+	because of the occlusions, or similar to the board patterns in the background,
+	there were false positives \cref{fig:recovered_bad_points}. Many images didn't
+	have undetected corners, hence it's hard to make a general statement about the
+	performance of the feature detector solely based on this experiment
+	\cref{fig:recovered_points_histogram}.
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.6\linewidth}
+	\includegraphics[width=\linewidth]{refined_corners_bad.png}
+	\captionof{figure}{Occlusion on the board with distinct features}
+	\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
+	\captionof{figure}{Similar pattern to the board in the background}
+	\label{fig:recovered_bad_points}
+\end{minipage}
 
@@
 	\begin{tikzpicture}
-		\begin{axis}[
+		\begin{axis}			[
+				ymode=log,
 				ybar interval,
@@
 			]
-			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+			\addplot+ [hist={data min=0,data max=100,bins=20}] table [y index=0]
 				% \addplot+ [hist={bins=30}] table [y index=0]
-				{data/pruned_number_of_features.txt};
+				{data/number_of_refined_points.txt};
 		\end{axis}
 	\end{tikzpicture}
-	\caption{Initial calibration's reprojection error histogram}
+	\caption{Histogram of the newly recovered features}
+	\label{fig:recovered_points_histogram}
 \end{figure}
-\begin{figure}[h]
-	\begin{tikzpicture}
-		\begin{axis}[
-				ybar interval,
-				ymin=0,
-				ylabel={Frequency},
-				xlabel={Value},
-				height=0.3\linewidth,
-				width=\linewidth,
-				ticklabel style = {font=\tiny},
-				% title={Reprojection error}
-			]
-			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
-				% \addplot+ [hist={bins=30}] table [y index=0]
-				{data/recovered_pruned_number_of_features.txt};
-		\end{axis}
-	\end{tikzpicture}
-	\caption{Final calibration's reprojection error histogram}
-\end{figure}
-
-\subsection{Performance under occlusion}\label{sub:performance_under_occlusion}
-
-Occlusions pose additional complications for the feature detection. We added an
-image on top of the board, and tried to recover additional points. Often the
-initial feature detector failed to detect points near the occlusion.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{refined_overlayed_corners.png}
-  \caption{Recovered occluded points}
-\end{figure}
-
-\begin{figure}[h]
-	\begin{tikzpicture}
-		\begin{axis}[
-				ybar interval,
-				ymin=0,
-				ylabel={Frequency},
-				xlabel={Value},
-				height=0.3\linewidth,
-				width=\linewidth,
-				ticklabel style = {font=\tiny},
-				% title={Initial calibration}
-			]
-			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
-				% \addplot+ [hist={bins=30}] table [y index=0]
-				{data/occluded_number_of_features.txt};
-		\end{axis}
-	\end{tikzpicture}
-	\caption{Initial calibration's reprojection error histogram}
-\end{figure}
-\begin{figure}[h]
-	\begin{tikzpicture}
-		\begin{axis}[
-				ybar interval,
-				ymin=0,
-				ylabel={Frequency},
-				xlabel={Value},
-				height=0.3\linewidth,
-				width=\linewidth,
-				ticklabel style = {font=\tiny},
-				% title={Reprojection error}
-			]
-			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
-				% \addplot+ [hist={bins=30}] table [y index=0]
-				{data/recovered_occluded_number_of_features.txt};
-		\end{axis}
-	\end{tikzpicture}
-	\caption{Final calibration's reprojection error histogram}
-\end{figure}
-
-\subsection{Recovery of previously undetected points}\label{sub:recovery_of_previously_undetected_points}
-
-\missingfigure{Compare the number of points with the provided by babelcalib}
-\missingfigure{Compare the reprojection error}

### 2023-05-29 paper/Chapters/Chapter1.tex
Final strokes

@@
 detection is performed on the undistorted image.
-% \todo{Probably remove the emphasis on TartanCalib, if I am not going to compare
-% with it}
 
@@
 
-The objective of this research is to improve the accuracy of the camera
+The objective of this research is to add additional constrains to the camera
 calibration by finding previously undetected features on the calibration
-board \todo{Probably rephrase if I won't compare the actual calibration}. For
-that, we formulate the set of research questions:
+board. For that, we formulate the set of research questions:
 \begin{itemize}
@@
 	\item How to filter out falsely detected features?
-	      \todo{Add more}
+  \item Is there a need for finding additional features on the calibration
+    board? Are all of the points detected?
 \end{itemize}
@@
 various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
-In \cref{cha:background}, we will describe the key concepts of the camera
+In \cref{cha:background}, we will describe the key concepts of camera
 calibration. Also, there we provide additional details on the underlying math,
-for example, the derivation of the division model invertion. In
+for example, the derivation of the division model inversion. In
 \cref{cha:approach}, we will describe the steps of the proposed method in
-details, including the feature detection, initial camera calibration, camera
+detail, including feature detection, initial camera calibration, camera
 parameters estimation via minimization of the reprojection error, and the

### 2023-05-29 paper/Chapters/Chapter4.tex
WIP
Final strokes

@@
 
-For feature detection, we used the approach, proposed by
-\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
-	sec:feature_detection}).
+For feature detection, we used the approach, proposed
+by~\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
+	sec:classifier}).
 
@@
 In this work, we obtained the camera calibration in two steps: first, we
-used the approach, proposed by \cite{scaramuzzaToolboxEasilyCalibrating2006} to
+used the approach, proposed by~\cite{scaramuzzaToolboxEasilyCalibrating2006} to
 obtain the initial approximation of the camera parameters. Then, we used
@@
 	R = R(\theta_x) R(\theta_y) R(\theta_z)
-\end{equation} \todo{Is the notation ok?}
+\end{equation}
 
@@
 
-For \(K\) we used the placeholder values. \(f\) was set to a constant value for
+For \(K\) we used the placeholder values.\ \(f\) was set to a constant value for
 the typical consumer camera, and \(c_x, c_y\) were set to the center of the
@@
 single equation. Now, by rewriting the equation in the matrix form
-\(M \cdot H = 0\), where \(H = \begin{pmatrix}
+\(M \cdot H = 0\), where
+\[
+	H = \begin{pmatrix}
 		r_{11}, r_{12}, r_{12}, r_{22}, t_1, t_2
-\end{pmatrix}\) we get:
-
+	\end{pmatrix}
+\]
+we get:
 \begin{equation}
@@
 	\\
-	\sqrt{\lambda^{2} \left( \frac{r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
+  \sqrt{\lambda^{2} \left( \frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
 	r_{11}^{2} + r_{12}^{2}\right)}                               & = 1   &  &
 	\text{Substitute into eq. (\ref{eq:orthonormality_2})}                     \\
-	\lambda^{2} (\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
-	r_{11}^{2} + r_{12}^{2})                                      & = 1   &  &
+  \lambda^{2} \left( \frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}}\right) +
+	r_{11}^{2} + r_{12}^{2}                                      & = 1   &  &
 	\text{Square both sides}                                                   \\
-	\lambda^{2} (\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
-	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2}) & = 0   &  &
+  \lambda^{2} \left(\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} \right) +
+	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2} & = 0   &  &
 	\text{Subtract eq. (\ref{eq:orthonormality_3})}
@@
 back-projected board from measure one was high (i.e., the \(t\) was far from
-the true value) being the degenerate solution\todo{Am I using the term
-	correctly?}. To avoid this issue, we first optimized only the \(t\),
+the true value) being the degenerate solution. To avoid this issue, we first optimized only the \(t\),
 until the loss function converged, meaning that \(t\) is close to the true
@@
 assumed that the whole board was detected, and imputed the missing points in the
-board space \cref{fig:extended_board_img}. Then, we tried extending the board
+board space (\cref{fig:extended_board_img}). Then, we tried extending the board
 points.
@@
 	\end{subfigure}
+	\begin{subfigure}{0.3\linewidth}
+		\includegraphics[width=\textwidth]{10.png}
+		\caption{Input image}
+	\end{subfigure}
+	\begin{subfigure}{0.3\linewidth}
+		\includegraphics[width=\textwidth]{11.png}
+		\caption{Corner likelihood}
+	\end{subfigure}
 

### 2023-05-29 paper/Chapters/Chapter5.tex
Final strokes

@@
 original publications cited above, hence the name of the dataset.
-As a calibration pattern, AprilGrid with 6x6 tags of 88 mm size was used.
+As a calibration pattern, AprilGrid with  \(6\times_6\) tags of 88 mm size was used.
 In total, the datasets contain approximately 800 images.
@@
 collected using the following cameras:
-As a calibration pattern, AprilGrid with 4x5 tags of 75 mm size was used.
+As a calibration pattern, AprilGrid with \(4\times_5\) tags of 75 mm size was used.
 The dataset contains approximately 800 images.
@@
 approximately 1400 images. It was collected using eight stereo cameras.
-As a calibration pattern, the checkerboard pattern with 9x6 tags of 22 mm size
+As a calibration pattern, the checkerboard pattern with \(9\times_6\) tags of 22 mm size
 was used.
@@
 	camera calibration is poor, the root-finding might fail. On the initial
-	calibration the number of the failed root-findings was much higher.
+	calibration the number of failed root-findings was much higher.
 \end{minipage}
@@
 
-We removed 20\% of the points from the original board, and then tried to recover
+We removed 20\% of the points from the original board and then tried to recover
 them.
@@
 
-Occlusions pose additional complications for the feature detection. We added an
-image on top of the board, and tried to recover additional points. Often the
+Occlusions pose additional complications for feature detection. We added an
+image on top of the board and tried to recover additional points. Often the
 initial feature detector failed to detect points near the occlusion.
@@
 	Those corners weren't detected initially due to high distortion. On the bottom
-	image, the algorithm found another row of the corners, which weren't detected previously.
+	image, the algorithm found another row of corners, which weren't detected previously.
 \end{minipage}

### 2023-05-29 paper/paper.tex
WIP
Final strokes

@@
 
+  The code for this paper is available at
+  \url{https://github.com/anstadnik/camera_calibration}.
+
 	% In this paper, we propose a novel approach to camera calibration. We want to
@@
 	brave people I was able to study and work on this thesis. I want to thank my
+	supervisor, Dr. James Pritts, for his guidance and support throughout the whole
+	process of writing this thesis. I also want to express my gratitude to all of
+	the people who encouraged me to keep going and inspired me to do my best: my
+	groupmates, my friends, and my girlfriend.
 	% The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
@@
 
-% \tableofcontents % Prints the main table of contents
-\todo{Enable}
+\tableofcontents % Prints the main table of contents
 %
 % \listoffigures % Prints the list of figures
-\todo{Enable}
 %
 % \listoftables % Prints the list of tables
-\todo{Enable}
 
@@
 % \dedicatory{For/Dedicated to/To my\ldots}
-\todo{Enable}
 

### 2023-05-29 paper/Chapters/Chapter1.tex
Final updates

@@
 
-This paper has the following structure: in \cref{related_work}, we will describe
+This paper has the following structure: in \cref{cha:related_work}, we will describe
 various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
@@
 process of searching and filtering the previously undetected features. In
-\cref{Experiments}, we will describe the metrics we used, provide details about
+\cref{cha:experiments}, we will describe the metrics we used, provide details about
 the datasets, show the results of each of the algorithm's steps, and evaluate it

### 2023-05-29 paper/Chapters/Chapter4.tex
Final updates

@@
 For feature detection, we used the approach, proposed
-by~\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
-	sec:classifier}).
+by~\cite{geigerAutomaticCameraRange2012} (see
+\cref{sec:boards_features_detection,sec:classifier}).
 
@@
 back-projection of the detected corners and the board are
-equivalent\todo{Doesn't sound very rigorous to me.}. We minimized the error
+equivalent. We minimized the error
 between the board and the back-projected corners because back-projection does

### 2023-05-29 paper/Chapters/Chapter1.tex
Updates

@@
 This paper has the following structure: in \cref{cha:related_work}, we will describe
-various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
+subtopics of the camera calibration, and outline the current state-of-the-art solutions.
 In \cref{cha:background}, we will describe the key concepts of camera

### 2023-05-29 paper/Chapters/Chapter2.tex
Updates

@@
 orientation of the pattern, as well as uniquely identifying each located pattern
-even under occlusion. Based on ArUco,
+even under occlusion. Later, based on ArUco pattern,
 ChArUcO~\citep{OpenCVCameraCalibration} (\cref{fig:charuco}) was
@@
 of the camera model is the division
-model~\citep{fitzgibbonSimultaneousLinearEstimation2001}.
+model~\citep{fitzgibbonSimultaneousLinearEstimation2001}. This model is
+discussed in details in \cref{sub:distortion}.
 However, \cite{schopsWhyHaving102020} shows that they tend to have
@@
 % hence many methods were proposed to solve this problem (e.g.,
-% ~\cite{brownCloseRangeCameraCalibration1971},
-% ~\cite{heikkilaFourstepCameraCalibration1997},
-% ~\cite{fitzgibbonSimultaneousLinearEstimation2001},
-% ~\cite{sturmGenericConceptCamera2004},
-% ~\cite{clausRationalFunctionLens2005},
-% ~\cite{meiSingleViewPoint2007},
-% ~\cite{ramalingamUnifyingModelCamera2017}).
+% ~\cite{brownCloseRangeCameraCalibration1971,
+% heikkilaFourstepCameraCalibration1997,
+% fitzgibbonSimultaneousLinearEstimation2001,
+% sturmGenericConceptCamera2004,
+% clausRationalFunctionLens2005,
+% meiSingleViewPoint2007,
+% ramalingamUnifyingModelCamera2017}).
 
@@
 for camera calibration, which did not use any model of the specific omnidirectional
-sensor.
+sensor. Is is described in details in \cref{sub:initial_approximation}.
 \cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
@@
 \cite{fuersattelOCPADOccludedCheckerboard2016} and
-\cite{geigerAutomaticCameraRange2012}. Those methods can detect the board and
+\cite{geigerAutomaticCameraRange2012} (\cref{sub:corner_detection}). Those methods can detect the board and
 associate the corners with the borders' corners under
@@
 
-\cite{chenNewSubPixelDetector2005} proposed using Hessian to find pixel
+\cite{chenNewSubPixelDetector2005} (\cref{sub:corner_detection}) proposed using Hessian to find pixel
 positions of the corners.

### 2023-05-29 paper/Chapters/Chapter5.tex
Final updates
Updates

@@
 provides the detected corners for all of the boards.
-\todo{Should I maybe tell less about it?}
 
@@
 calibration. They're provided in a Deltille \cite{DeltilleDetector2023} format,
-and are well documented:
+and are well documented.
 
@@
 
-\section{Camera calibration}\label{sec:camera_calibration}
+\section{Camera calibration}\label{sec:camera_calibration_exp}
 
@@
 
-\section{Additional features detection}\label{sec:additional_features_detection}
+\section{Additional features detection}\label{sec:additional_features_detection_exp}
 
@@
 	\begin{subfigure}[h]{0.45\linewidth}
+		\resizebox{\linewidth}{!}{
 			\begin{tikzpicture}
@@
 						ticklabel style = {font=\tiny},
-					title={Histogram of the points before refinement}
+						title={Histogram of points before refinement}
 					]
@@
 			\end{tikzpicture}
+		}
 	\end{subfigure}
@@
 		% \centering
+		\resizebox{\linewidth}{!}{
 			\begin{tikzpicture}
@@
 						ticklabel style = {font=\tiny},
-					title={Histogram of the points after refinement}
+						title={Histogram of points after refinement}
 					]
@@
 						ticklabel style = {font=\tiny},
-					title={Histogram of the points before the refinement}
+						title={Histogram of points before refinement}
 					]
-				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
 						% \addplot+ [hist={bins=30}] table [y index=0]
@@
 			\end{tikzpicture}
-		\caption{}
+		}
 	\end{subfigure}
@@
 						ticklabel style = {font=\tiny},
-					title={Histogram of the points after the refinement}
+						title={Histogram of points after refinement}
 					]
-				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
+					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
 						% \addplot+ [hist={bins=30}] table [y index=0]
@@
 
-\begin{minipage}[t]{0.3\linewidth}
 Lastly, we recovered the points that were not detected by the initial feature
@@
 image, the algorithm found another row of corners, which weren't detected previously.
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.6\linewidth}
-	\includegraphics[width=\linewidth]{refined_corners1.png}
-	\includegraphics[width=\linewidth]{refined_corners2.png}
 
-	\captionof{figure}{Recovered points
+% \begin{minipage}[t]{0.80\linewidth}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.75\linewidth]{refined_corners1.png}
+	\includegraphics[width=0.75\linewidth]{refined_corners2.png}
+
+	\caption{Recovered points
 		(\textcolor[HTML]{1f77b4}{unchanged}
@@
 	\label{fig:recovered_good_points}
-\end{minipage}
+\end{figure}
+% \end{minipage}
 
-\begin{minipage}[t]{0.3\linewidth}
+\newpage
 However,
 because of the occlusions, or similar to the board patterns in the background,
-	there were false positives \cref{fig:recovered_bad_points}. Many images didn't
+there were false positives (\cref{fig:recovered_bad_points}). Many images didn't
 have undetected corners, hence it's hard to make a general statement about the
 performance of the feature detector solely based on this experiment
-	\cref{fig:recovered_points_histogram}.
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.6\linewidth}
-	\includegraphics[width=\linewidth]{refined_corners_bad.png}
-	\captionof{figure}{Occlusion on the board with distinct features}
-	\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
-	\captionof{figure}{Similar pattern to the board in the background}
-	\label{fig:recovered_bad_points}
-\end{minipage}
+(\cref{fig:recovered_points_histogram}.)
 
 \begin{figure}[h]
+	\centering
+	\begin{subfigure}[h]{0.6\linewidth}
+		\includegraphics[width=\linewidth]{refined_corners_bad.png}
+		\caption{Occlusion on the board with distinct features}
+	\end{subfigure}
+	\begin{subfigure}[h]{0.6\linewidth}
+		\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
+		\caption{Similar pattern to the board in the background}
+	\end{subfigure}
+	\label{fig:recovered_bad_points}
+\end{figure}
+
+\begin{figure}[h!]
 	\begin{tikzpicture}
@@
 				ybar interval,
-				ymin=0,
 				ylabel={Frequency},
@@
 			]
-			\addplot+ [hist={data min=0,data max=100,bins=20}] table [y index=0]
+			\addplot+ [hist={data min=0,data max=50,bins=20}] table [y index=0]
 				% \addplot+ [hist={bins=30}] table [y index=0]

### 2023-05-29 paper/paper.tex
Final updates
Updates

@@
 11pt, % The default document font size, options: 10pt, 11pt, 12pt
-%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
+%oneside, % Two sides (alternating margins) for binding by default, uncomment to switch to one side
 english, % ngerman for German
@@
 %chapterinoneline, % Uncomment to place the chapter title next to the number on one line
-%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
+%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgments pages to match the default layout
 openany
@@
 
-\usepackage[textwidth=20mm]{todonotes}
 \setlength{\marginparwidth}{2.5cm}
@@
 \usepackage{pgfplots}
+\pgfplotsset{compat=1.18}
 \usepackage{pgf-pie}
+\usepackage{microtype}
 \usetikzlibrary{spy,arrows}
@@
 \author{Andrii \textsc{Stadnik}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
-\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
+\addresses{} % Your address, is not currently used anywhere in the template, print it elsewhere with \addressname
 
-\subject{Data Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
+\subject{Data Science} % Your subject area, is not currently used anywhere in the template, print it elsewhere with \subjectname
 \keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
@@
 \begin{document}
-\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages
+\frontmatter % Use Roman page numbering style (i, ii, iii, iv...) for the pre-content pages
 
@@
 				\emph{Author:}\\
-				% \href{http://www.johnsmith.com}{\authorname} % Author name - remove the \href bracket to remove the link
-				\authorname % Author name - remove the \href bracket to remove the link
+				\href{https://www.linkedin.com/in/anstadnik/}{\authorname} % Author name - remove the \href bracket to remove the link
+				% \authorname % Author name - remove the \href bracket to remove the link
 			\end{flushleft}
@@
 		\vfill
-		\includegraphics[height=3cm]{UCU-Apps 2022.png} % University/department logo - uncomment to place it
+		\includegraphics[height=3cm]{UCU-Apps2022_.png} % University/department logo - uncomment to place it
 
 		\vfill
-		{\large Lviv 2022}\\[4cm] % Date
+		{\large Lviv 2023}\\[4cm] % Date
 
@@
 
-	Current state-of-the-art techniques occasionally fail to accurately estimate
-	the camera parameters for wide-angle lenses, as most of the algorithms assume
-	lenses with medium to small distortion. Partially it occurs due to extreme
-	distortion at the edges of the image, which poses additional challenges to
-	feature detection algorithms. We propose a novel approach for detecting
-	additional features on the imaged calibration pattern using intermediate
-	camera calibration. Utilizing the prior information about the calibration
-	pattern's geometry, we can estimate the possible positions of the previously
-	undetected features. Those features are filtered using the binary classifier,
-	and the remaining ones are used to further constrain the camera calibration.
-	The proposed method consists of three key steps: \((1)\) feature
-	detection and estimation of the lattice geometry, \((2)\) initial camera
-	calibration by solving the two-step linear minimization problem, and \((3)\)
-	estimation of the possible positions of the undetected features by projecting the
-	imputed and extended lattice geometry onto the image plane, and filtering them
-	using the binary classifier.
+	% Current state-of-the-art techniques occasionally fail to accurately estimate
+	% the camera parameters for wide-angle lenses, as most of the algorithms assume
+	% lenses with medium to small distortion. Partially it occurs due to extreme
+	% distortion at the edges of the image, which poses additional challenges to
+	% feature detection algorithms. We propose a novel approach to detecting
+	% additional features on the imaged calibration pattern using intermediate
+	% camera calibration. Utilizing the prior information about the calibration
+	% pattern's geometry, we can estimate the possible positions of the previously
+	% undetected features. Those features are filtered using the binary classifier,
+	% and the remaining ones are used to further constrain the camera calibration.
+	% The proposed method consists of three key steps: \((1)\) feature
+	% detection and estimation of the lattice geometry, \((2)\) initial camera
+	% calibration by solving the two-step linear minimization problem, and \((3)\)
+	% estimation of the possible positions of the undetected features by projecting the
+	% imputed and extended lattice geometry onto the image plane, and filtered them
+	% using the binary classifier.
 
-  The code for this paper is available at
-  \url{https://github.com/anstadnik/camera_calibration}.
+  This thesis proposes a model-based approach to improve the detection of
+  calibration board fiducials from calibration imagery taken by wide-angle or
+  fisheye lenses. From a single image, we estimate the camera model and project
+  the calibration board into the image to guide the search for missed detections
+  and reject spurious detections. In addition, we propose a classifier to label
+  ambiguous detections that are geometrically plausible given the estimated
+  camera model and imaged board. The proposed method addresses shortcomings of
+  the state-of-the-art, which struggle to reliably detect board fiducials at the
+  extents of the image, where the lens distortion is most observable. The
+  proposed method recovers additional corners that can be used to place
+  additional constraints on the non-convex camera calibration problem, which
+  improves the likelihood of convergence to a global minimum.
+
+  The code for this paper is available on GitHub
+  \footnote{\url{https://github.com/anstadnik/camera_calibration}}.
 
@@
 
-	% \noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
+	% \noindent If you were supported with the scholarship, please thank your donor organization or a person who supported you.
 \end{acknowledgements}
@@
 
-% \begin{symbols}{lll} % Include a list of Symbols (a three column table)
+% \begin{symbols}{lll} % Include a list of Symbols (a three-column table)
 %
@@
 
-\pagestyle{thesis} % Return the page headers back to the "thesis" style
-
-\listoftodos{1}
-\todo{Remove list of todos}
+\pagestyle{thesis} % Return the page headers to the "thesis" style
 
@@
 
+% \emergencystretch=1em
+% \Urlmuskip=0mu plus 1mu\relax
+
+\setcounter{biburllcpenalty}{7000}
+\setcounter{biburlucpenalty}{8000}
 \printbibliography[heading=bibintoc]

### 2023-06-11 paper/Chapters/Chapter4.tex
Updates
Update the paper

@@
 
-We chose to minimize the reprojection error between the board and back-projected
+We minimized the reprojection error between the board and back-projected
 corners, which were initially detected. The projection and back-projection are
@@
 \begin{equation}
-	R = R(\theta_x) R(\theta_y) R(\theta_z)
+	R = R(\theta_x) R(\theta_y) R(\theta_z),
 \end{equation}
@@
 		0              & 0               & 1
-	\end{bmatrix}
+	\end{bmatrix}.
 \end{align}
@@
 \begin{equation}
-	K = \begin{pmatrix}
+	K = \begin{bmatrix}
 		\frac{f r_x}{s_x} & 0                 & \frac{r_x}{2} \\
@@
 		0                 & 0                 & 1
-	\end{pmatrix},
-\end{equation}.
+	\end{bmatrix}.
+\end{equation}
 
@@
 		       \widehat{u}_x \\ \widehat{u}_y \\ \psi(r(\mathbf{\widehat{u}}))
-	       \end{pmatrix}^{T} & = H\mathbf{X}                                 \\
+	       \end{pmatrix}^{T} & = H\mathbf{X}.
 \end{align}
@@
 	\end{bmatrix}^{T} \mathbf{X} = 0
-	\label{eq:eq_no_multiplier}
-\end{equation}.
+	\label{eq:eq_no_multiplier}.
+\end{equation}
 
@@
 \begin{align}
-	\widehat{v} (t_1X + t_2 Y + t_3) -
-	g(r(\mathbf{\widehat{u}})) (r_{12}X + r_{22}Y + t_2 ) & = 0
+	\widehat{v} (r_{31}X + r_{32} Y + t_3) -
+	g(r(\mathbf{\widehat{u}})) (r_{21}X + r_{22}Y + t_2 ) & = 0
 	\label{eq:scaramuzza_system_1}                              \\
 	g(r(\mathbf{\widehat{u}})) (r_{11}X + r_{12}Y + t_1) -
-	\widehat{u} (t_1X + t_2 Y + t_3)                      & = 0
+	\widehat{u} (r_{31}X + r_{32} Y + t_3)                      & = 0
 	\label{eq:scaramuzza_system_2}                              \\
-	\widehat{u} (r_{12}X + r_{22}Y + t_2 ) -
+	\widehat{u} (r_{21}X + r_{22}Y + t_2 ) -
 	\widehat{v} (r_{11}X + r_{12}Y + t_1)                 & = 0
-	\label{eq:scaramuzza_system_3}
+	\label{eq:scaramuzza_system_3}.
 \end{align}
@@
 single equation. Now, by rewriting the equation in the matrix form
-\(M \cdot H = 0\), where
+\(M \cdot \mathbf{h} = 0\), where
 \[
-	H = \begin{pmatrix}
-		r_{11}, r_{12}, r_{12}, r_{22}, t_1, t_2
-	\end{pmatrix}
+	\mathbf{h} = \begin{pmatrix}
+		r_{11}, r_{12}, r_{21}, r_{22}, t_1, t_2
+	\end{pmatrix}^{T},
 \]
@@
 
-The linear estimate of \(H\) is found by minimizing \(\left\lVert M \cdot H
-\right\rVert ^{2}\) using SVD. The solution is known up to a scale factor.
+The linear estimate of \(\mathbf{h}\) is found by minimizing \(\left\lVert M \cdot
+\mathbf{h} \right\rVert ^{2}\) using SVD. The solution is known up to a scale factor.
 
@@
 \begin{subnumcases}{}
-	\lambda^{2} r_{11} r_{12} + \lambda^{2} r_{12} r_{22} + \lambda^{2} t_1
-	t_2  = 0
+	\lambda^{2} r_{11} r_{12} + \lambda^{2} r_{21} r_{22} + \lambda^{2} r_{31}
+	r_{32}  = 0
 	\label{eq:orthonormality_1}                                                     \\
-	\lambda \sqrt{r_{11}^{2} + r_{12}^{2} + t_1^{2}}                            = 1
+	\lambda \sqrt{r_{11}^{2} + r_{21}^{2} + r_{31}^{2}}                            = 1
 	\label{eq:orthonormality_2}                                                     \\
-	\lambda \sqrt{r_{12}^{2} + r_{22}^{2} + t_2 ^{2}}                            = 1
-	\label{eq:orthonormality_3}
-\end{subnumcases},
+	\lambda \sqrt{r_{12}^{2} + r_{22}^{2} + r_{32} ^{2}}                            = 1
+	\label{eq:orthonormality_3},
+\end{subnumcases}
 where \(\lambda\) is non-zero multiplier.
 
-Now, to solve for \(t_1\) and \(t_2 \), first find possible values for
-\(t_2 ^{2}\):
+Now, to solve for \(r_{31}\) and \(r_{32} \), first find possible values for
+\(r_{32} ^{2}\):
 \begin{align}
-	- \frac{r_{11} r_{12} + r_{12} r_{22}}{t_2 }                  & = t_1 &  &
-	\text{Solve eq. (\ref{eq:orthonormality_1}) for \(t_1\)}
-	\label{eq:orthonormality_4}                                                \\
+	- \frac{r_{11} r_{12} + r_{21} r_{22}}{r_{32} }                         & = r_{31} &  &
+	\text{Solve eq. (\ref{eq:orthonormality_1}) for \(r_{31}\)}
+	\label{eq:orthonormality_4}
 	\\
-  \sqrt{\lambda^{2} \left( \frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
-	r_{11}^{2} + r_{12}^{2}\right)}                               & = 1   &  &
+	\sqrt{\lambda^{2} \left( \frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
+	r_{11}^{2} + r_{21}^{2}\right)}                                      & = 1   &  &
 	\text{Substitute into eq. (\ref{eq:orthonormality_2})}                            \\
-  \lambda^{2} \left( \frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}}\right) +
-	r_{11}^{2} + r_{12}^{2}                                      & = 1   &  &
+	\lambda^{2} \left( \frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
+	r_{11}^{2} + r_{21}^{2}\right)                                       & = 1   &  &
 	\text{Square both sides}                                                          \\
-  \lambda^{2} \left(\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} \right) +
-	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2} & = 0   &  &
+	\lambda^{2} \left(\frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
+	r_{11}^{2} + r_{21}^{2} - r_{12}^{2} - r_{22}^{2} - r_{32} ^{2} \right) & = 0   &  &
 	\text{Subtract eq. (\ref{eq:orthonormality_3})}
@@
 	\\
-	\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
-	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2}  & = 0   &  &
+	\frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
+	r_{11}^{2} + r_{21}^{2} - r_{12}^{2} - r_{22}^{2} - r_{32} ^{2}         & = 0   &  &
 	\text{Divide both by \(\lambda ^{2}\)}                                            \\
-	t_2 ^{4} - (r_{11}^{2} + r_{12}^{2} - r_{12}^{2} -
-	r_{22}^{2}) t_2 ^{2} - (r_{11} r_{12} + r_{12} r_{22})^{2}    & = 0   &  &
-	\text{Multiply by \(t_2 ^{2}\)}
-	\label{eq:orthonormality_6}
+	r_{32} ^{4} - (r_{11}^{2} + r_{21}^{2} - r_{12}^{2} -
+	r_{22}^{2}) r_{32} ^{2} - (r_{11} r_{12} + r_{21} r_{22})^{2}           & = 0   &  &
+	\text{Multiply by \(r_{32} ^{2}\)}
+	\label{eq:orthonormality_6}.
 \end{align}
 
-Now, solve \cref{eq:orthonormality_6} for \(t_2 ^{2}\), and take a root to find
-possible values for \(t_2 \).
+Now, solve \cref{eq:orthonormality_6} for \(r_{32} ^{2}\), and take a root to find
+possible values for \(r_{32} \).
 
-To find \(t_1\), substitute the found values for \(t_2 \) into
-\cref{eq:orthonormality_4} or \cref{eq:orthonormality_5} depending on the value
-of \(t_2 \):
+To find \(r_{31}\), substitute the found values for \(r_{32} \) into
+\cref{eq:orthonormality_4} or subtract \cref{eq:orthonormality_3} from
+\cref{eq:orthonormality_2} and solve for \(r_{31}\) depending on the value
+of \(r_{32} \):
 \begin{subnumcases}{}
-	t_1  = - \frac{r_{11} r_{12} + r_{12} r_{22}}{t_2 } &
-	\text{\(t_2  \neq 0\)} \\
-	t_1  =  r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} &
-	\text{\(t_2  = 0\)}
+	r_{31}  = - \frac{r_{11} r_{12} + r_{21} r_{22}}{r_{32} } &
+	\text{\(r_{32}  \neq 0\)} \\
+	r_{31}  =  r_{11}^{2} + r_{21}^{2} - r_{12}^{2} - r_{22}^{2} &
+	\text{\(r_{32}  = 0\)}.
 \end{subnumcases}
 
-Now, it's possible to find \(H\) for each of the pairs of \(t_1\) and
-\(t_2 \).
+Now, it's possible to find \(H\) for each of the pairs of \(r_{31}\) and
+\(r_{32} \).
 
@@
 point, and it would be projected to   \(\begin{pmatrix}
-	t_1, t_2
+	r_{31}, r_{32}
 \end{pmatrix}^{T}\). Hence, the best matrix would be such that has the closest
 \(\begin{pmatrix}
-	t_1, t_2
+	r_{31}, r_{32}
 \end{pmatrix}^{T}\) to \(\begin{pmatrix}
@@
 However, often the algorithm finds who matrices \(H\) such that they have the
-same \(t_1\) and \(t_2 \), but different \(r_{11}\), \(r_{12}\), \(r_{21}\). To
+same \(r_{31}\) and \(r_{32} \), but different \(r_{11}\), \(r_{21}\), \(r_{12}\). To
 find the best matrix, we found the intrinsic values for each of them and
@@
 		D_N - C_N
-	\end{bmatrix}
-\end{equation},
+	\end{bmatrix},
+\end{equation}
 where
@@
 	C_i & = r_{11} X_i + r_{12} Y_i + t_1  \\
-	D_i & = u_i (r_{31} X_i + r_{32} Y_i) \\
+	D_i & = u_i (r_{31} X_i + r_{32} Y_i).
 \end{align}
@@
 		\mu   & =0.25\left(f_A^i+f_B^i+f_C^i+f_D^i\right)
-	\end{aligned}
+	\end{aligned}.
 \end{equation}

### 2023-06-11 paper/Chapters/Chapter5.tex
Update the paper

@@
 
-Also, by using more features, we can get better calibration, as we have more
-constraints, but the reprojection error might be higher.
+% Also, by using more features, we can get better calibration, as we have more
+% constraints, but the reprojection error might be higher.
 
@@
 
-Because of that, we instead artificially removed some of the points from the
+The paper's main contribution is finding additional calibration boards' features, which
+then can be used as an input to any other camera calibration algorithm. The
+measurements' error is assumed to be Gaussian with zero mean and a constant
+variance \citep{hartleyMultipleViewGeometry2004}. As calibration process
+minimizes the geometric distance between the projected and the measured points,
+it is equivalent to performing the maximum likelihood estimation
+\citep{hartleyMultipleViewGeometry2004}. As the number of the measurement grows,
+the estimated camera parameters converge to the true values, hence adding
+additional measurements improves the calibration (especially from the edge of
+the image, where the distortion is the highest).
+
+However, the above statement assumes that the measurements are true positives.
+To evaluate that, we instead artificially removed some of the points from the
 detections, to ensure that we can recover them. We also created
@@
 	\end{subfigure}
+  \caption{Examples of false positives}
 	\label{fig:recovered_bad_points}

### 2023-06-12 paper/Chapters/Chapter5.tex
Add presentation, updates

@@
 approximately 1400 images. It was collected using eight stereo cameras.
-As a calibration pattern, the checkerboard pattern with \(9\times_6\) tags of 22 mm size
+As a calibration pattern, the checkerboard pattern with \(9\times 6\) tags of 22 mm size
 was used.
@@
 			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
-				115/Correctly detected,
+				254/Correctly detected,
 				80/Reprojection error > 10,
-				254/Not correctly detected
+				458/Not correctly detected
 			}
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
+		\includegraphics[width=0.7\linewidth]{refined_overlayed_corners.png}
 		\caption{Recovered pruned points

### 2023-06-12 paper/presentation.tex
Add presentation, updates

\documentclass{beamer}
% \documentclass[notes]{beamer}

\usetheme[progressbar=foot, block=fill]{metropolis}

\usepackage{graphicx}
% \usepackage{booktabs}
% \usepackage{algorithm}
% \usepackage{algpseudocode}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{pgf-pie}
% \usepackage{tikz}
% \usepackage{upgreek}
\usepackage{appendixnumberbeamer}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{pgfplots}
% \usepackage{url}
\usepackage{xfrac}
\usepackage{appendixnumberbeamer}

% \usetikzlibrary{calc}
% \usetikzlibrary{3d}
\usetikzlibrary{spy,arrows}

% \usepackage{biblatex}
\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\addbibresource{references.bib}

\graphicspath{ {images/} }

\title{Corner Localization and Camera Calibration from Imaged Lattices}
% \subtitle{A Novel Approach to Camera Calibration}
\author{Andrii Stadnik \inst{1} \and James Pritts \inst{2}}
\institute{
  \inst{1} Faculty of Computer Science, Ukrainian Catholic University, Lviv,
  Ukraine \\
  \inst{2} Czech Institute of Informatics, Robotics and Cybernetics at Czech Technical University in Prague, Czech
}
\date{2023}

% \metroset{}

\begin{document}

\begin{frame}
	\titlegraphic{\hfill\includegraphics[height=1cm]{UCU-Apps2022_.png}}
	\titlepage
\end{frame}

\begin{frame}
	\frametitle{Structure of the presentation}
	\tableofcontents
\end{frame}

\section{Introduction}\label{sec:introduction}

\begin{frame}
	\frametitle{Camera calibration}

	Camera calibration is a necessary step for mapping from the pixel position to
	the real-world 3D position.

	\begin{alertblock}{Note}
		Here, we will use the term \textit{camera calibration} to refer to the
		geometric camera calibration.
	\end{alertblock}

	\begin{figure}
		\centering
		\includegraphics[width=0.8\textwidth]{3d_reconstruction.png}
		\caption{3D reconstruction}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Motivation}
	Accurate camera calibration is required for many applications, such as:
	\begin{itemize}
		\item 3D reconstruction
		\item Robotics and automation
		\item Augmented reality
		\item Photogrammetry
		\item Stereo vision
		\item And many more\ldots
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Challenges}
	% \begin{columns}[T,onlytextwidth]
	% \column{0.6\textwidth}
	Camera calibration is
	a challenging task, especially for highly distorted images.

	The challenges include:
	\begin{itemize}
		\item Robust keypoint detection
		\item Accurate distortion modeling
		\item Stability of the calibration
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Example}
	% \column{0.4\textwidth}
	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=3cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.8\textwidth]{distorted_image}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				\spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (3.5,3.0) in node [right] at (8.1,4.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Example of corners near the center of the image and at the edge}
	\end{figure}
	% \end{columns}
\end{frame}

\begin{frame}
	\frametitle{Research objective}

	Improve the detection of
	calibration board fiducials from calibration imagery taken by wide-angle or
	fisheye lenses.

	% Add additional constrains to the camera
	% calibration by finding previously undetected features on the calibration
	% board.

	For that, we formulate the set of research questions:
	\begin{itemize}
		\item How to find additional features on the calibration board which were not
		      detected by the feature detector?
		\item How to filter out falsely detected features?
		\item Is there a need for finding additional features on the calibration
		      board? Are all of the points detected?
	\end{itemize}
\end{frame}

\section{Background}\label{sec:background}

\begin{frame}
	\frametitle{Notation}
	The column vectors will be denoted by bold lowercase letters (e.g.
	\(\mathbf{u} = \begin{pmatrix}
		u, v, 1
	\end{pmatrix}^{T}\)), matrices will be denoted by bold uppercase letters (e.g.
	\(H = \begin{bmatrix}
		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
	\end{bmatrix}
	\)). We will use homogeneous coordinates to simplify the equations.
\end{frame}

\begin{frame}
	\frametitle{Camera model}
	Camera parameters can be divided into 3 parts:
	\begin{itemize}
		\item Extrinsic parameters
		\item Distortion parameters
		\item Intrinsic parameters
	\end{itemize}

	They define a camera model, which
	projects a homogeneous 3D scene point
	\(\mathbf{x} = \begin{pmatrix}
		x, y, z, 1
	\end{pmatrix}^{T}\) into the homogeneous image point
	\(\mathbf{u} = \begin{pmatrix}
		u, v, 1
	\end{pmatrix}^{T}\).
\end{frame}

\begin{frame}
	\frametitle{Definition of the camera model}
	\begin{exampleblock}{Definition}
		\begin{align}
			\alpha \mathbf{u} & = K f_{\boldsymbol{\lambda}}(H\mathbf{X})
			\tag{Projection} \label{eq:projection}                                            \\
			\alpha \mathbf{X} & = H^{-1} g_{\boldsymbol{\lambda}}(K^{-1}\mathbf{u}) \tag{Back
				projection} \label{eq:back_projection}.
		\end{align}
		where \(K\) is the camera matrix, \(g_{\boldsymbol{\lambda}}(\cdot)\) is the division distortion
		model \citep{fitzgibbonSimultaneousLinearEstimation2001}, \(f(\cdot)\) is the
		inverse of \(g(\cdot)\) and \(H\) is the homography matrix, and \(\alpha\)
		is a non-zero scalar.
	\end{exampleblock}

	\begin{alertblock}{Note}
		Slides with the detailed explanation can be demonstrated upon request during the Q\&A session.
		% The explanation of the used camera model does not fit into the
		% presentation duration. However, the appendix of this presentation contains
		% the detailed explanation of each element of the equation, and will be
		% happily discussed/presented during the Q\&A session.
	\end{alertblock}

\end{frame}

\section{Approach}\label{sec:approach}

\begin{frame}
	\frametitle{Pipeline overview}

	\begin{enumerate}
		\item Feature detection.
		\item Camera calibration.
		      \begin{enumerate}
			      \item Initialize camera parameters (\(R\), \(\mathbf{t}\),
			            \(\boldsymbol{\lambda}\)) using the solver.
			      \item Refine camera parameters and estimate \(K\) by optimization.
		      \end{enumerate}
		\item Impute the gaps in the board, and extend it.
		\item Get positions of new points on the image.
		\item Filter out false positives.
	\end{enumerate}
\end{frame}

\begin{frame}
	\frametitle{Feature detection}
	Use the approach, proposed by~\cite{geigerAutomaticCameraRange2012}:
	\begin{enumerate}
		\item Compute the corner likelihood map by convolving the image with two
		      \(n\times n\) prototypes.
		\item Additional filtering based on the number of the zero-crossings and
		      non-maximum suppression.
		\item Subpixel refinement of the detected corners.
		\item Board's structure refinement.
	\end{enumerate}
	\begin{figure}[h]
		\centering
		\begin{subfigure}{0.3\linewidth}
			\includegraphics[width=\textwidth]{10.png}
			\caption{Input image}
		\end{subfigure}
		\begin{subfigure}{0.3\linewidth}
			\includegraphics[width=\textwidth]{11.png}
			\caption{Corner likelihood}
		\end{subfigure}

		% \caption{Corner prototypes \citep{geigerAutomaticCameraRange2012}}
		\label{fig:corner_prototypes}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Camera calibration 1}

	\begin{enumerate}
		\item Initialize camera parameters (\(R\), \(\mathbf{t}\),
		      \(\boldsymbol{\lambda}\)) using the method, proposed by
		      \cite{scaramuzzaToolboxEasilyCalibrating2006}.
	\end{enumerate}
	\begin{exampleblock}{Overview}
		The author proposes the multistage solver for the projection equation,
		assuming that the camera matrix is known.
	\end{exampleblock}
\end{frame}

\begin{frame}
	\frametitle{Camera calibration 2}
	\begin{enumerate}
		\item Refine the values of \(R\), \(\mathbf{t}\), \(\boldsymbol{\lambda}\), and
		      estimate \(K\) by minimizing the reprojection error between the
		      board and the back-projected corners.
	\end{enumerate}

	\begin{exampleblock}{Reprojection error}
		The reprojection error is the distance between the reprojected point and the
		measured one:
		\begin{equation*}
			L = \sum_{i=1}^{N} \left\lVert
			H^{-1} g_{ \boldsymbol{\lambda}}(K^{-1} \mathbf{u_i}) -
			\mathbf{x_i} \right\rVert^2,
		\end{equation*}
		where \(\boldsymbol{\lambda}\) are the division distortion model
		parameters, \( \mathbf{x_{i}}\) and \(\mathbf{u_{i}}\) are the coordinates
		of the \(i\)-th corner in the 3D scene coordinates, and the respective
		feature on the image.
	\end{exampleblock}
\end{frame}

\begin{frame}
	\frametitle{Additional features detection}
	To find the probable positions of the previously undetected corners, we
	impute the gaps in the board, and extend it by 1 row and column from each
	side:
	\begin{figure}
		\begin{subfigure}{0.45\linewidth}
			\resizebox{\linewidth}{!}{
				\centering
				\begin{tikzpicture}
					\begin{axis}[
							xlabel={$x$},
							ylabel={$y$},
							grid=major,
							title={Original board},
						]
						\addplot[
							only marks,
						] table {data/original_board.txt};
					\end{axis}
				\end{tikzpicture}
			}
		\end{subfigure}
		\begin{subfigure}{0.45\linewidth}
			\resizebox{\linewidth}{!}{
				\centering
				\begin{tikzpicture}
					\begin{axis}[
							xlabel={$x$},
							ylabel={$y$},
							grid=major,
							title={Extended board},
						]
						\addplot[
							only marks,
						] table {data/extended_board.txt};
					\end{axis}
				\end{tikzpicture}
			}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Binary classification}
	\begin{itemize}
		\item Compute the corner likelihood map for the image.
		\item Use the ROC curve, and pick the threshold which maximizes the G-mean.
	\end{itemize}

	We tested the approach of \cite{geigerAutomaticCameraRange2012}, and,
	alternatively, the Hessian responses for the image, as proposed by
	\cite{chenNewSubPixelDetector2005}.
\end{frame}

\section{Experiments}\label{sec:experiments}

\begin{frame}
	\frametitle{Metrics}
	The paper's main contribution is finding additional calibration boards' features, which
	then can be used as an input to any other camera calibration algorithm.

	\begin{itemize}
		\item Number of recovered artificially removed points
		\item Number of recovered points under occlusion
		\item Number of recovered points on original images
	\end{itemize}

\end{frame}

\begin{frame}
	\frametitle{Dataset}
	\textbf{OV} \citep{lochmanBabelCalibUniversalApproach2021} is a dataset of
	approximately 1400 images. It was collected using eight stereo cameras.
	As a calibration pattern, the checkerboard pattern with \(9\times 6\) tags of 22 mm size
	was used.

	\begin{alertblock}{Note}
		Much more data was collected. However, the initial feature detection
		supports only checkerboard patterns for now. Other than that, the pipeline
		works with any pattern.
	\end{alertblock}
\end{frame}

\begin{frame}
	\frametitle{Camera calibration 1}
	Compare the initial camera calibration with camera calibration obtained via
	optimization of reprojection error.

	\begin{figure}
		\begin{subfigure}{0.45\linewidth}
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
						254/Correctly detected,
						80/Reprojection error > 10,
						458/Not correctly detected
					}
				\end{tikzpicture}
			}
			\caption{Initial calibration}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.45\linewidth}
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
						658/Correctly detected,
						19/Reprojection error > 10,
						115/Not correctly detected
					}
				\end{tikzpicture}
			}
			\caption{Final calibration}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Camera calibration 2}

	\begin{figure}
		% \begin{subfigure}{0.45\linewidth}
		\begin{subfigure}{\linewidth}
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\begin{axis}[
							ybar interval,
							ymin=0,
							ylabel={Frequency},
							xlabel={Value},
							height=0.3\linewidth,
							width=\linewidth,
							ticklabel style = {font=\tiny},
							% title={Initial calibration}
						]
						\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
							% \addplot+ [hist={bins=30}] table [y index=0]
							{data/reprojection_error_init.txt};
					\end{axis}
				\end{tikzpicture}
			}
			\caption{Initial calibration's reprojection error histogram}
		\end{subfigure}
		\begin{subfigure}{\linewidth}
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\begin{axis}[
							ybar interval,
							ymin=0,
							ylabel={Frequency},
							xlabel={Value},
							height=0.3\linewidth,
							width=\linewidth,
							ticklabel style = {font=\tiny},
							% title={Reprojection error}
						]
						\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
							% \addplot+ [hist={bins=30}] table [y index=0]
							{data/reprojection_error_final.txt};
					\end{axis}
				\end{tikzpicture}
			}
			\caption{Final calibration's reprojection error histogram (in px.)}
		\end{subfigure}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Additional features detection}

	\begin{columns}
		\begin{column}{0.6\textwidth}
			\begin{figure}
				\centering
				\includegraphics[width=\textwidth]{extended_board_img.png}
				\caption{Extended board, new points are marked as blue}
				\label{fig:extended_board_img}
			\end{figure}
		\end{column}
		\begin{column}{0.4\textwidth}
			\begin{figure}
				\begin{subfigure}{\textwidth}
					\resizebox{\textwidth}{!}{
						\begin{tikzpicture}
							\begin{axis}[
									xlabel={$x$},
									ylabel={$y$},
									grid=major,
									title={Original board},
								]
								\addplot[
									only marks,
								] table {data/original_board.txt};
							\end{axis}
						\end{tikzpicture}
					}
					% \caption{Original board}
				\end{subfigure}
				\begin{subfigure}{\textwidth}
					\resizebox{\textwidth}{!}{
						\begin{tikzpicture}
							\begin{axis}[
									xlabel={$x$},
									ylabel={$y$},
									grid=major,
									title={Extended board},
								]
								\addplot[
									only marks,
								] table {data/extended_board.txt};
							\end{axis}
						\end{tikzpicture}
					}
					% \caption{Extended board}
				\end{subfigure}
			\end{figure}
		\end{column}
	\end{columns}

\end{frame}

\begin{frame}
	\frametitle{Classification}

	The Hessian approach proved to be more robust, as the other gave too many false
	positives, especially for the edges.

	\begin{figure}
		\begin{subfigure}{0.30\linewidth}
			\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=10,size=3cm, connect spies}]
				\node[anchor=south west,inner sep=0] (image) at (0,0)
				% {\includegraphics[width=0.10\textwidth]{distorted_image}};
				{\includegraphics[width=\linewidth]{response_orig.png}};
				\begin{scope}[x={(image.south east)},y={(image.north west)}]
					\spy[red] on (1.7,1.4) in node [left] at (2.8,3.3);
					% \spy[blue] on (3.5,3.0) in node [right] at (8.1,4.3);
				\end{scope}
			\end{tikzpicture}
			\caption{Original image}
		\end{subfigure}
		\begin{subfigure}{0.30\linewidth}
			\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=10,size=3cm, connect spies}]
				\node[anchor=south west,inner sep=0] (image) at (0,0)
				% {\includegraphics[width=0.10\textwidth]{distorted_image}};
				{\includegraphics[width=\linewidth]{response_hessian.png}};
				\begin{scope}[x={(image.south east)},y={(image.north west)}]
					\spy[red] on (1.7,1.4) in node [left] at (2.8,3.3);
					% \spy[blue] on (3.5,3.0) in node [right] at (8.1,4.3);
				\end{scope}
			\end{tikzpicture}
			\caption{Hessian response}
		\end{subfigure}
		\begin{subfigure}{0.30\linewidth}
			\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=10,size=3cm, connect spies}]
				\node[anchor=south west,inner sep=0] (image) at (0,0)
				% {\includegraphics[width=0.6\textwidth]{distorted_image}};
				{\includegraphics[width=\linewidth]{response_other.png}};
				\begin{scope}[x={(image.south east)},y={(image.north west)}]
					\spy[red] on (1.7,1.4) in node [left] at (2.8,3.3);
					% \spy[blue] on (3.5,3.0) in node [right] at (8.1,4.3);
				\end{scope}
			\end{tikzpicture}
			\caption{\cite{geigerAutomaticCameraRange2012}}
		\end{subfigure}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Evaluation (artificially removed points)}
	We removed 20\% of the points from the original board and then tried to recover
	them.

	\begin{figure}[h]
		\centering
		\begin{subfigure}[h]{\linewidth}
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\begin{axis}[
							ybar interval,
							ymin=0,
							ylabel={Frequency},
							xlabel={Value},
							height=0.3\linewidth,
							width=\linewidth,
							ticklabel style = {font=\tiny},
							title={Histogram of points before refinement}
						]
						\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
							% \addplot+ [hist={bins=30}] table [y index=0]
							{data/pruned_number_of_features.txt};
					\end{axis}
				\end{tikzpicture}
			}
		\end{subfigure}
		\hfill
		\begin{subfigure}[h]{\linewidth}
			% \centering
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\begin{axis}[
							ybar interval,
							ymin=0,
							ylabel={Frequency},
							xlabel={Value},
							height=0.3\linewidth,
							width=\linewidth,
							ticklabel style = {font=\tiny},
							title={Histogram of points after refinement}
						]
						\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
							% \addplot+ [hist={bins=30}] table [y index=0]
							{data/recovered_pruned_number_of_features.txt};
					\end{axis}
				\end{tikzpicture}
			}
		\end{subfigure}
	\end{figure}

\end{frame}
\begin{frame}
	\frametitle{Evaluation (artificially removed points) 2}
	\begin{figure}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
		\caption{Feature refinement on the board with 80\% of the points}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Evaluation (artificial occlusion)}

	Occlusions pose additional complications for feature detection.

	\begin{figure}[h]
		\centering
		\begin{subfigure}[h]{\linewidth}
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\begin{axis}[
							ybar interval,
							ymin=0,
							ylabel={Frequency},
							xlabel={Value},
							height=0.3\linewidth,
							width=\linewidth,
							ticklabel style = {font=\tiny},
							title={Histogram of points before refinement}
						]
						\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
							% \addplot+ [hist={bins=30}] table [y index=0]
							{data/occluded_number_of_features.txt};
					\end{axis}
				\end{tikzpicture}
			}
		\end{subfigure}
		\begin{subfigure}[h]{\linewidth}
			% \centering
			\resizebox{\linewidth}{!}{
				\begin{tikzpicture}
					\begin{axis}[
							ybar interval,
							ymin=0,
							ylabel={Frequency},
							xlabel={Value},
							height=0.3\linewidth,
							width=\linewidth,
							ticklabel style = {font=\tiny},
							title={Histogram of points after refinement}
						]
						\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
							% \addplot+ [hist={bins=30}] table [y index=0]
							{data/recovered_occluded_number_of_features.txt};
					\end{axis}
				\end{tikzpicture}
			}
		\end{subfigure}
	\end{figure}

\end{frame}
\begin{frame}
	\frametitle{Evaluation (artificial occlusion) 2}
	\begin{figure}
		\begin{subfigure}[h]{\linewidth}
			\centering
			\includegraphics[width=0.7\linewidth]{refined_overlayed_corners.png}
			\caption{Recovered pruned points
				(\textcolor[HTML]{1f77b4}{unchanged}
				\textcolor[HTML]{ff7f0e}{filtered out}
				\textcolor[HTML]{2ca02c}{new corner}
				\textcolor[HTML]{d62728}{out of image})}
		\end{subfigure}
		\hfill
		\caption{Feature refinement on the board with partial board occlusion}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Evaluation (real data)}
	Lastly, we recovered the points that were not detected by the initial feature
	detector.

	% \begin{minipage}[t]{0.80\linewidth}
	\begin{figure}[h]
		\centering
		\includegraphics[width=0.75\linewidth]{refined_corners1.png}
		\includegraphics[width=0.75\linewidth]{refined_corners2.png}

		\caption{Recovered points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
		\label{fig:recovered_good_points}
	\end{figure}
	% \end{minipage}

\end{frame}

\begin{frame}
	\frametitle{Evaluation (real data, false positives) 1}

	\begin{figure}
		\includegraphics[width=0.8\linewidth]{refined_corners_bad.png}
		\caption{Occlusion on the board with distinct features}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Evaluation (real data, false positives) 2}
	\begin{figure}
		\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
		% \caption{Similar pattern to the board in the background}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Evaluation (real data)}

	\begin{figure}[h!]
		\begin{tikzpicture}
			\begin{axis}			[
					ymode=log,
					ybar interval,
					ylabel={Frequency},
					xlabel={Value},
					height=0.3\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					% title={Initial calibration}
				]
				\addplot+ [hist={data min=0,data max=50,bins=20}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/number_of_refined_points.txt};
			\end{axis}
		\end{tikzpicture}
		\caption{Histogram of the newly recovered features}
		\label{fig:recovered_points_histogram}
	\end{figure}

\end{frame}

\section{Conclusions}\label{sec:conclusions}

\begin{frame}
	\frametitle{Reviewers' comments}

	\textbf{No comparison was made to classical camera calibration results and no
		discussion why results differ.}

	The main contribution is the feature detection step. The user can use the
	found camera parameters, or pass the obtained features to any camera
	calibration toolchain.
\end{frame}

\begin{frame}[standout]
	Q\&A

\end{frame}

\appendix

\begin{frame}
	\frametitle{Extrinsic parameters}
	The extrinsic parameters represent a rigid transformation from a 3-D world
	coordinate system to the 3-D camera’s coordinate system.

	\begin{exampleblock}{Definition}
		\begin{equation*}
			\widehat{\mathbf{x}} =
			R \begin{pmatrix}
				x, y, z
			\end{pmatrix}^{T} + \mathbf{t} =
			\begin{bmatrix}
				R              & \mathbf{t} \\
				\mathbf{0}^{T} & 1
			\end{bmatrix} \begin{pmatrix}
				x, y, z, 1
			\end{pmatrix}^{T},
		\end{equation*}
		where
		\(\begin{pmatrix}
			x, y, z
		\end{pmatrix}^{T}\) is a 3D scene point,
		% \(R \begin{pmatrix}
		% 	x, y, z
		% \end{pmatrix}^{T} + \mathbf{t}\), where
		\(R\) is a \(3 \times 3\) rotation matrix
		and \(\mathbf{t}\) is
		a \(3 \times 1\) translation vector.
	\end{exampleblock}
\end{frame}

\begin{frame}
	\frametitle{Extrinsic parameters}

	When working with the coplanar scene points, we can simplify the projection
	by assuming that the scene plane is located at \(Z = 0\). In this case, the
	projection of the point becomes:
	\begin{exampleblock}{Definition for coplanar points}
		\begin{equation*}
			\alpha \begin{pmatrix}
				u \\ v \\ 1
			\end{pmatrix} = \begin{bmatrix}
				\mathbf{r_1} & \mathbf{r_2} & \mathbf{r_3} & \mathbf{t}
			\end{bmatrix} \begin{pmatrix}
				x \\ y \\ 0 \\ 1
				% \end{pmatrix} = \begin{bmatrix}
				%   \mathbf{p_1} & \mathbf{p_2} & \mathbf{p_4}
				% \end{bmatrix} \begin{pmatrix}
				%   x \\ y \\ 1
				% \end{pmatrix}.
			\end{pmatrix} = \underbrace{\begin{bmatrix}
					\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
				\end{bmatrix}}_{H} \begin{pmatrix}
				x \\ y \\ 1
			\end{pmatrix}.
		\end{equation*}
	\end{exampleblock}
\end{frame}

\begin{frame}
	\frametitle{Distortion model}
	The distortion of the image is caused by the lens not being perfectly planar.
	We used the division distortion model
	\cite{fitzgibbonSimultaneousLinearEstimation2001} which maps a
	point from a retinal plane to the
	ray direction in the camera coordinate system.
	\begin{exampleblock}{Definition}
		\begin{equation*}
			g(\mathbf{u}) = \begin{pmatrix}
				u, v, \psi(r(\mathbf{u}))
			\end{pmatrix}^{T},
			\psi(r) = 1 + \sum_{n = 1}^{N} \lambda_n r^{2n},
		\end{equation*}
		where
		\(\mathbf{u} = \begin{pmatrix}
			u, v, 1
		\end{pmatrix}^{T}\) is a point in the retinal plane
		, \(r(\mathbf{u}) = \sqrt{u^2 + v^2}\) is the radial distance from the
		principal point and \(\lambda_n\) are the distortion coefficients.
	\end{exampleblock}
\end{frame}

\begin{frame}
	\frametitle{Intrinsic parameters}
	Represent a projective transformation from the 3-D camera’s coordinates into
	the 2-D image coordinates.

	\begin{exampleblock}{Definition}
		\begin{equation*}
			K = \begin{bmatrix}
				\alpha_x & \alpha_x \cot \theta & c_x \\
				0        & \alpha_y             & c_y \\
				0        & 0                    & 1
			\end{bmatrix} \begin{bmatrix}
				f & 0 & 0 \\
				0 & f & 0 \\
				0 & 0 & 1
			\end{bmatrix} = \begin{bmatrix}
				f_x & k   & c_x \\
				0   & f_y & c_y \\
				0   & 0   & 1
			\end{bmatrix}.
		\end{equation*}
		For a typical camera, \(\theta = \sfrac{\pi}{2}\) and \(\alpha_x = \alpha_y\)
		\cite{hartleyMultipleViewGeometry2004}:
		\begin{equation*}
			K = \begin{bmatrix}
				f & 0 & c_x \\
				0 & f & c_y \\
				0 & 0 & 1
			\end{bmatrix}.
		\end{equation*}
	\end{exampleblock}

\end{frame}

\end{document}

### 2023-08-14 paper/presentation.tex
Update the notation

@@
+% \documentclass[aspectratio=169]{beamer}
 \documentclass{beamer}
@@
 \usepackage{subcaption}
+\usepackage{pifont}
+\usepackage{multirow}
+\usepackage{booktabs}
+\usepackage{tabularx}
 \usepackage{caption}
@@
 % \usetikzlibrary{3d}
-\usetikzlibrary{spy,arrows}
+\usetikzlibrary{spy,arrows,shapes, arrows, positioning}
 
@@
 \addbibresource{references.bib}
+
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+
+\newcommand\headercell[1]{%
+   \smash[b]{\begin{tabular}[t]{@{}c@{}} #1 \end{tabular}}}
+
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 
@@
 
-\begin{frame}
+\begin{frame}[plain]
 	\titlegraphic{\hfill\includegraphics[height=1cm]{UCU-Apps2022_.png}}
@@
 
-\begin{frame}
-	\frametitle{Structure of the presentation}
-	\tableofcontents
-\end{frame}
+% \begin{frame}
+% 	\frametitle{Structure of the presentation}
+% 	\tableofcontents
+% \end{frame}
 
@@
 
+% \begin{frame}
+% 	\frametitle{Motivation}
+% 	Accurate camera calibration is required for many applications, such as:
+% 	\begin{itemize}
+% 		\item 3D reconstruction
+% 		\item Robotics and automation
+% 		\item Augmented reality
+% 		\item Photogrammetry
+% 		\item Stereo vision
+% 	\end{itemize}
+% \end{frame}
+
 \begin{frame}
 	\frametitle{Motivation}
+
+	\begin{columns}[T,onlytextwidth]
+		\column{0.6\textwidth}
 		Accurate camera calibration is required for many applications, such as:
@@
 			\item Stereo vision
-		\item And many more\ldots
 		\end{itemize}
-\end{frame}
-
-\begin{frame}
-	\frametitle{Challenges}
-	% \begin{columns}[T,onlytextwidth]
-	% \column{0.6\textwidth}
-	Camera calibration is
-	a challenging task, especially for highly distorted images.
-
-	The challenges include:
-	\begin{itemize}
-		\item Robust keypoint detection
-		\item Accurate distortion modeling
-		\item Stability of the calibration
-	\end{itemize}
+
+		\column{0.4\textwidth}
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.8\textwidth]{high_distortion.png}
+			\caption{Image with a high distortion}
+		\end{figure}
+	\end{columns}
 \end{frame}
@@
 		\end{tikzpicture}
-		\caption{Example of corners near the center of the image and at the edge}
+		\caption{Corners near the center of the image and at the edge}
 	\end{figure}
@@
 	\frametitle{Research objective}
-
-	Improve the detection of
+	\textbf{Improve the detection of
 		calibration board fiducials from calibration imagery taken by wide-angle or
-	fisheye lenses.
+		fisheye lenses.}
 
@@
 
-\section{Background}\label{sec:background}
+\section{Related work}\label{sec:related_work}
+
+\begin{frame}
+	\frametitle{TartanCalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}}
+
+	\begin{columns}
+		\begin{column}{0.4\textwidth}
+			\textbf{Algorithm}
+			\begin{enumerate}
+				\item Run the calibration toolchain
+				\item Undistort the image
+				\item Subpixel refinement
+				\item Repeat
+			\end{enumerate}
+		\end{column}
+		\begin{column}{0.6\textwidth}
+			\textbf{Issues}
+			\begin{itemize}
+				\item Runs complete calibration toolchain each iteration
+				\item Does not use the geometry information
+				\item Not self-contained
+			\end{itemize}
+		\end{column}
+	\end{columns}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Models comparison}
+	\begingroup
+	\scriptsize
+
+	% \begin{figure}
+	% 	\begin{subfigure}{0.45\linewidth}
+	% 		\resizebox{\linewidth}{!}{
+	% 			\centering
+	% 			\begin{tikzpicture}
+	% 				\begin{axis}[
+	% 						xlabel={$x$},
+	% 						ylabel={$y$},
+	% 						grid=major,
+	% 						title={Original board},
+	% 					]
+	% 					\addplot[
+	% 						only marks,
+	% 					] table {data/original_board.txt};
+	% 				\end{axis}
+	% 			\end{tikzpicture}
+	% 		}
+	\setlength\tabcolsep{1.5pt} % default value: 6pt
+	\begin{table}
+		\begin{tabularx}{\textwidth}{@{} L *{5}{c} @{}}
+			\toprule
+			\multicolumn{1}{c}{\multirow{2}{*}{\centering\textbf{Supports}}}           &
+			\multicolumn{5}{c@{}}{\textbf{Name}}                                                           \\
+			\cmidrule(l){2-6}                                                          &
+			\textbf{OpenCV\footcite{dudaAccurateDetectionLocalization2018}}            &
+			\textbf{TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}} &
+			\textbf{Kalibr\footcite{mayeSelfsupervisedCalibrationRobotic2013}}         &
+			\textbf{OCamCalib\footcite{scaramuzzaToolboxEasilyCalibrating2006}}        &
+			\textbf{LIBCBDETECT\footcite{geigerAutomaticCameraRange2012}}                                  \\
+			\midrule
+			Unknown board shape                                                        & \xmark & \cmark &
+			\cmark                                                                     & \cmark & \cmark   \\
+			\hline
+			Occlusion                                                                  & \xmark & \cmark &
+			\cmark                                                                     & \cmark & \cmark   \\
+			\hline
+			Model-based extra features detection                                       & \xmark & \cmark &
+			\xmark                                                                     & \xmark & \xmark   \\
+			\hline
+			Geometry-based extra features detection                                    & \xmark & \xmark &
+			\xmark                                                                     & \xmark & \xmark   \\
+			\bottomrule
+		\end{tabularx}
+		\caption{Comparison of feature detectors}
+	\end{table}
+	\endgroup
+\end{frame}
+
+\section{Approach}\label{sec:approach}
+
+% \section*{Intuition}\label{sec:intuition}
+%
+\begin{frame}
+	\frametitle{Intuition (image)}
+	Can you guess where the missing corners could be?
+
+	% \begin{figure}
+	% 	\includegraphics[width=0.7\textwidth]{example_board.png}
+	% 	\caption{Example board detection}
+	% \end{figure}
+	\begin{figure}
+		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=3,size=5cm, connect spies}]
+			\node[anchor=south west,inner sep=0] (image) at (0,0)
+			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
+			{\includegraphics[width=0.7\linewidth]{example_board.png}};
+			\begin{scope}[x={(image.south east)},y={(image.north west)}]
+				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
+				\spy[blue] on (5.5,1.0) in node [right] at (6.5,3.3);
+			\end{scope}
+		\end{tikzpicture}
+		\caption{Example board detection}
+	\end{figure}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Intuition (corners)}
+	Can you now?
+
+	\begin{figure}
+		\resizebox{0.7\textwidth}{!}{
+			\centering
+			\begin{tikzpicture}
+				\begin{axis}[
+						xlabel={$x$},
+						ylabel={$y$},
+						grid=major,
+						title={Corners},
+					]
+					\addplot[
+						only marks,
+					] table {data/example_corners.txt};
+				\end{axis}
+			\end{tikzpicture}
+		}
+	\end{figure}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Intuition (board)}
+	What about here?
+
+	\begin{figure}
+		\resizebox{0.7\textwidth}{!}{
+			\centering
+			\begin{tikzpicture}
+				\begin{axis}[
+						xlabel={$x$},
+						ylabel={$y$},
+						grid=major,
+						title={Board},
+					]
+					\addplot[
+						only marks,
+					] table {data/example_board.txt};
+				\end{axis}
+			\end{tikzpicture}
+		}
+	\end{figure}
+\end{frame}
+
+\begin{frame}[standout]
+	Use the board's geometry to find missing corners!
+\end{frame}
+
+\section*{Method}\label{sec:method}
+
+\begin{frame}
+	\frametitle{Pipeline overview}
+
+	\begin{enumerate}
+		\item Feature detection.
+		\item Camera calibration.
+		      \begin{enumerate}
+			      \item Initialize camera parameters using the solver.
+			      \item Refine camera parameters by optimization.
+		      \end{enumerate}
+		\item Impute the gaps in the board and extend it.
+		\item Get positions of new points on the image.
+		\item Filter out false positives.
+	\end{enumerate}
+\end{frame}
 
@@
 		u, v, 1
-	\end{pmatrix}^{T}\)), matrices will be denoted by bold uppercase letters (e.g.
+	\end{pmatrix}^{T}\)), matrices will be denoted by uppercase letters (e.g.
 	\(H = \begin{bmatrix}
@@
 		\begin{align}
-			\alpha \mathbf{u} & = K f_{\boldsymbol{\lambda}}(H\mathbf{X})
+			\alpha \mathbf{u} & = K f_{\boldsymbol{\lambda}}(H\mathbf{x})
 			\tag{Projection} \label{eq:projection}                                            \\
-			\alpha \mathbf{X} & = H^{-1} g_{\boldsymbol{\lambda}}(K^{-1}\mathbf{u}) \tag{Back
+			\beta \mathbf{x}  & = H^{-1} g_{\boldsymbol{\lambda}}(K^{-1}\mathbf{u}) \tag{Back
 				projection} \label{eq:back_projection}.
@@
 		where \(K\) is the camera matrix, \(g_{\boldsymbol{\lambda}}(\cdot)\) is the division distortion
-		model \citep{fitzgibbonSimultaneousLinearEstimation2001}, \(f(\cdot)\) is the
-		inverse of \(g(\cdot)\) and \(H\) is the homography matrix, and \(\alpha\)
-		is a non-zero scalar.
+		model \footcite{fitzgibbonSimultaneousLinearEstimation2001}, \(f(\cdot)\) is the
+		inverse of \(g(\cdot)\) and \(H\) is the homography matrix, and \(\alpha,
+		\beta\) are non-zero scalars.
 	\end{exampleblock}
@@
 	\begin{alertblock}{Note}
-		Slides with the detailed explanation can be demonstrated upon request during the Q\&A session.
+		You have printed materials with the details about the camera model.
+		% Slides with the detailed explanation can be demonstrated upon request during the Q\&A session.
 		% The explanation of the used camera model does not fit into the
@@
 
-\end{frame}
-
-\section{Approach}\label{sec:approach}
-
-\begin{frame}
-	\frametitle{Pipeline overview}
-
-	\begin{enumerate}
-		\item Feature detection.
-		\item Camera calibration.
-		      \begin{enumerate}
-			      \item Initialize camera parameters (\(R\), \(\mathbf{t}\),
-			            \(\boldsymbol{\lambda}\)) using the solver.
-			      \item Refine camera parameters and estimate \(K\) by optimization.
-		      \end{enumerate}
-		\item Impute the gaps in the board, and extend it.
-		\item Get positions of new points on the image.
-		\item Filter out false positives.
-	\end{enumerate}
 \end{frame}
@@
 
-	\begin{enumerate}
-		\item Initialize camera parameters (\(R\), \(\mathbf{t}\),
+	Initialize camera parameters (\(R\), \(\mathbf{t}\),
 	\(\boldsymbol{\lambda}\)) using the method, proposed by
 	\cite{scaramuzzaToolboxEasilyCalibrating2006}.
-	\end{enumerate}
+
 	\begin{exampleblock}{Overview}
@@
 	\frametitle{Camera calibration 2}
-	\begin{enumerate}
-		\item Refine the values of \(R\), \(\mathbf{t}\), \(\boldsymbol{\lambda}\), and
+
+	Refine the values of \(R\), \(\mathbf{t}\), \(\boldsymbol{\lambda}\), and
 	estimate \(K\) by minimizing the reprojection error between the
 	board and the back-projected corners.
-	\end{enumerate}
 
@@
 		\item Compute the corner likelihood map for the image.
-		\item Use the ROC curve, and pick the threshold which maximizes the G-mean.
+		\item Use the ROC curve and pick the threshold which maximizes the G-mean.
 	\end{itemize}
@@
 	\frametitle{Camera calibration 1}
-	Compare the initial camera calibration with camera calibration obtained via
+	Compare the initial camera calibration with the camera calibration obtained via
 	optimization of reprojection error.
@@
 
-	The Hessian approach proved to be more robust, as the other gave too many false
+	The Hessian approach proved to be more robust, as the alternative gave too many false
 	positives, especially for the edges.
@@
 	\frametitle{Evaluation (artificially removed points)}
-	We removed 20\% of the points from the original board and then tried to recover
-	them.
+	We removed 20\% of the points and then tried to recover them.
 
@@
 	\frametitle{Evaluation (artificially removed points) 2}
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
-		\caption{Recovered pruned points
+
+	\begin{figure}
+		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=3,size=4cm, connect spies}]
+			\node[anchor=south west,inner sep=0] (image) at (0,0)
+			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
+			{\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}};
+			\begin{scope}[x={(image.south east)},y={(image.north west)}]
+				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
+				\spy[blue] on (3.5,3.0) in node [right] at (6.1,3.3);
+			\end{scope}
+		\end{tikzpicture}
+		\caption{Feature recovery on the board with 80\% of the points
 			(\textcolor[HTML]{1f77b4}{unchanged}
@@
 			\textcolor[HTML]{d62728}{out of image})}
-		\caption{Feature refinement on the board with 80\% of the points}
 	\end{figure}
@@
 
-	Occlusions pose additional complications for feature detection.
+	Occlusions pose complications for feature detection.
 
@@
 	\frametitle{Evaluation (artificial occlusion) 2}
-	\begin{figure}
-		\begin{subfigure}[h]{\linewidth}
-			\centering
-			\includegraphics[width=0.7\linewidth]{refined_overlayed_corners.png}
-			\caption{Recovered pruned points
+
+	\begin{figure}
+		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=3,size=5cm, connect spies}]
+			\node[anchor=south west,inner sep=0] (image) at (0,0)
+			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
+			{\includegraphics[width=0.7\linewidth]{refined_overlayed_corners.png}};
+			\begin{scope}[x={(image.south east)},y={(image.north west)}]
+				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
+				\spy[blue] on (3.5,3.0) in node [right] at (6.1,3.3);
+			\end{scope}
+		\end{tikzpicture}
+		\caption{Additional features detection on the board with partial board occlusion
 			(\textcolor[HTML]{1f77b4}{unchanged}
@@
 			\textcolor[HTML]{d62728}{out of image})}
-		\end{subfigure}
-		\hfill
-		\caption{Feature refinement on the board with partial board occlusion}
 	\end{figure}
@@
 
-	% \begin{minipage}[t]{0.80\linewidth}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.75\linewidth]{refined_corners1.png}
-		\includegraphics[width=0.75\linewidth]{refined_corners2.png}
-
-		\caption{Recovered points
+	\begin{figure}
+		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=4cm, connect spies}]
+			\node[anchor=south west,inner sep=0] (image) at (0,0)
+			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
+			{\includegraphics[width=0.6\linewidth]{refined_corners1.png}};
+			\begin{scope}[x={(image.south east)},y={(image.north west)}]
+				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
+				\spy[blue] on (4.8,2.5) in node [right] at (6.1,3.3);
+			\end{scope}
+		\end{tikzpicture}
+		\caption{Newly detected points
 			(\textcolor[HTML]{1f77b4}{unchanged}
@@
 			\textcolor[HTML]{d62728}{out of image})}
-		\label{fig:recovered_good_points}
-	\end{figure}
-	% \end{minipage}
-
-\end{frame}
-
-\begin{frame}
-	\frametitle{Evaluation (real data, false positives) 1}
-
-	\begin{figure}
-		\includegraphics[width=0.8\linewidth]{refined_corners_bad.png}
-		\caption{Occlusion on the board with distinct features}
-	\end{figure}
-
-\end{frame}
-
-\begin{frame}
-	\frametitle{Evaluation (real data, false positives) 2}
-	\begin{figure}
-		\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
-		% \caption{Similar pattern to the board in the background}
+	\end{figure}
+
+\end{frame}
+
+\begin{frame}
+	\frametitle{Evaluation (real data) 2}
+
+	\begin{figure}
+		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=5cm, connect spies}]
+			\node[anchor=south west,inner sep=0] (image) at (0,0)
+			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
+			{\includegraphics[width=0.75\linewidth]{refined_corners2.png}};
+			\begin{scope}[x={(image.south east)},y={(image.north west)}]
+				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
+				\spy[blue] on (3.0,2.4) in node [right] at (6.1,3.3);
+			\end{scope}
+		\end{tikzpicture}
+		\caption{Newly detected points
+			(\textcolor[HTML]{1f77b4}{unchanged}
+			\textcolor[HTML]{ff7f0e}{filtered out}
+			\textcolor[HTML]{2ca02c}{new corner}
+			\textcolor[HTML]{d62728}{out of image})}
+	\end{figure}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Evaluation (real data, false positives)}
+
+	\begin{figure}
+		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=5cm, connect spies}]
+			\node[anchor=south west,inner sep=0] (image) at (0,0)
+			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
+			{\includegraphics[width=0.7\linewidth]{refined_corners_bad_bad.png}};
+			\begin{scope}[x={(image.south east)},y={(image.north west)}]
+				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
+				\spy[blue] on (2.6,2.0) in node [right] at (6.1,3.3);
+			\end{scope}
+		\end{tikzpicture}
+		\caption{Example of false positives
+			(\textcolor[HTML]{1f77b4}{unchanged}
+			\textcolor[HTML]{ff7f0e}{filtered out}
+			\textcolor[HTML]{2ca02c}{new corner}
+			\textcolor[HTML]{d62728}{out of image})}
 	\end{figure}
@@
 
+\begin{frame}
+	\frametitle{Comparison}
+	\begingroup
+	\scriptsize
+
+	\setlength\tabcolsep{1.5pt} % default value: 6pt
+	\begin{table}
+		\begin{tabularx}{\textwidth}{@{} L *{6}{c} @{}}
+			\toprule
+			\multicolumn{1}{c}{\multirow{2}{*}{\centering\textbf{Supports}}}           &
+			\multicolumn{6}{c@{}}{\textbf{Name}}                                                                  \\
+			\cmidrule(l){2-7}                                                          &
+			\textbf{OpenCV\footcite{dudaAccurateDetectionLocalization2018}}            &
+			\textbf{TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}} &
+			\textbf{Kalibr\footcite{mayeSelfsupervisedCalibrationRobotic2013}}         &
+			\textbf{OCamCalib\footcite{scaramuzzaToolboxEasilyCalibrating2006}}        &
+			\textbf{LIBCBDETECT\footcite{geigerAutomaticCameraRange2012}}              &
+			{\normalsize \textbf{Ours}}                                                                           \\
+			\midrule
+			Unknown board shape                                                        & \xmark & \cmark & \cmark
+			                                                                           & \cmark & \cmark & \cmark \\
+			\hline
+			Occlusion                                                                  & \xmark & \cmark & \cmark
+			                                                                           & \cmark & \cmark & \cmark \\
+			\hline
+			Model-based extra features detection                                       & \xmark & \cmark & \xmark
+			                                                                           & \xmark & \xmark & \cmark \\
+			\hline
+			Geometry-based extra features detection                                    & \xmark & \xmark & \xmark
+			                                                                           & \xmark & \xmark & \cmark \\
+			\bottomrule
+		\end{tabularx}
+		\caption{Comparison of feature detectors}
+	\end{table}
+	\endgroup
+\end{frame}
+
 \section{Conclusions}\label{sec:conclusions}
@@
 \begin{frame}
-	\frametitle{Reviewers' comments}
-
-	\textbf{No comparison was made to classical camera calibration results and no
-		discussion why results differ.}
-
-	The main contribution is the feature detection step. The user can use the
-	found camera parameters, or pass the obtained features to any camera
-	calibration toolchain.
+	\frametitle{Answers to the research questions}
+
+	\begin{itemize}
+		\item \textbf{How to find additional features on the calibration board which were not
+			      detected by the feature detector?}\\
+
+		      This thesis proposes a model-based approach to improve the detection of
+		      calibration board fiducials from calibration imagery taken by wide-angle or
+		      fisheye lenses.
+		\item \textbf{How to filter out falsely detected features?}\\
+
+		      We proposed a classifier that filters false positives, and
+		      shown that it works well on real data.
+		\item \textbf{Is there a need for finding additional features on the calibration
+			      board? Are all of the points detected?}\\
+
+		      We demonstrated that the proposed method successfully detected
+		      additional features on the real data.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Reviewers' comments 1}
+	\textbf{No comparison was made to classical camera calibration results}
+
+	The main contribution is the feature detection step.
+
+	The algorithm estimates camera parameters, but we don't claim that they are
+	better than state-of-the-art. The user can use those, or pass the refined
+	features into any camera calibration toolchain.
+	% The user can use the
+	% obtained camera parameters, however, we do not claim that they will always beat the
+	% SOTA. Alternatively, the user should pass the refined features to any camera
+	% calibration toolchain.
+\end{frame}
+
+\begin{frame}
+	\frametitle{Reviewers' comments 2}
+	\textbf{The literature review
+		does not include a review of methods that solve the feature detection step in
+		a different way}
+
+	A review of feature detection methods is presented in the paper.
+
+	The specific subtask of model-based missed
+	feature detection is not big enough to have a separate review. However, we
+	included TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}.
+\end{frame}
+
+\begin{frame}
+	\frametitle{Reviewers' comments 3}
+	\textbf{There is no general block diagram of the algorithm}
+
+	\begin{figure}
+		\begin{tikzpicture}[
+				block/.style={rectangle, draw, align=center, minimum width=2cm, minimum
+						height=1cm, font=\footnotesize},
+				line/.style={draw, -latex}
+			]
+			\node [block] (block1) {Feature\\ detection};
+			\node [block, right=of block1, minimum width=8cm, minimum height=3cm] (block2) {};
+			\node [block, at={(block2.center)}, xshift=-2.0cm] (block3) {Initialize camera\\ parameters (\(R\), \(\mathbf{t}\), \(\boldsymbol{\lambda}\))\\ using the solver};
+			\node [block, at={(block2.center)}, xshift=2.0cm] (block4) {Refine camera\\ parameters and\\ estimate \(K\)\\ by optimization};
+			\node [block, below=of block4] (block5) {Impute the gaps in\\ the board, and\\ extend it};
+			\node [block, left=of block5] (block6) {Get positions of\\ new points on\\ the image};
+			\node [block, left=of block6] (block7) {Filter out\\ false positives};
+
+			\node [above of=block2, node distance=1.8cm] {Camera calibration};
+
+			\path [line] (block1) -- (block3);
+			\path [line] (block3) -- (block4);
+			% \path [line] (block2) -| (block3);
+			% \path [line] (block2) -| (block4);
+			% \path [line] (block3) -- (block5);
+			\path [line] (block4) -- (block5);
+			\path [line] (block5) -- (block6);
+			\path [line] (block6) -- (block7);
+		\end{tikzpicture}
+	\end{figure}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Reviewers' comments 4}
+	\textbf{It is not sufficiently described what results are obtained on
+		test sets}
+
+	The datasets we used did not contain the ground truth camera calibration.
+	Also, the algorithm does not include the learning step, hence there is no
+	reason to use the test set.
+	% Also, we used three datasets with different setup.
+\end{frame}
+
+\begin{frame}
+	\frametitle{Reviewers' comments 4}
+	\textbf{The questions "How to filter incorrectly defined grid points" and "Is there a
+		need to search for additional grid points" posed in the work are insufficiently disclosed}
+
+	Addressed in section Conclusions.
+\end{frame}
+
+\begin{frame}
+	\frametitle{Reviewers' comments 5}
+	\textbf{A comparison of the results with other feature detection methods has not been made}
+
+	We have added a feature-wise comparison to the state-of-the-art methods, and
+	numerical comparison to the
+	LIBCBDETECT\footcite{geigerAutomaticCameraRange2012} method.
+
+	The TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022} method
+	currently supports only AprilGrid boards.
 \end{frame}

### 2023-08-14 calibration/benchmark/calib.py
Add type hints

@@ -1,6 +1,7 @@
 from functools import partial
 from typing import Callable
 import numpy as np
+from numpy.typing import NDArray
 from tqdm.contrib.concurrent import process_map
 
 from calibration.projector.camera import Camera
@@ -9,7 +10,7 @@ from calibration.projector.projector import Projector
 from .features import Features
 
 
-_SOLVER = Callable[[np.ndarray, np.ndarray, Camera], Projector | None]
+_SOLVER = Callable[[NDArray[np.float64], NDArray[np.float64], Camera], Projector | None]
 
 
 def _calibrate_helper(

### 2023-08-14 calibration/benchmark/test_benchmark.py

@@ -43,11 +43,11 @@
 #                     self.fail("ValueError in benchmark_simul")
 #                 for k, v in kwargs.items():
 #                     for r in results:
-#                         if isinstance(v, np.ndarray):
+#                         if isinstance(v, NDArray[np.float64]):
 #                             np.testing.assert_array_equal(getattr(r.input, k), v)
 #                         else:
 #                             for f in fields(v):
-#                                 if isinstance(getattr(v, f.name), np.ndarray):
+#                                 if isinstance(getattr(v, f.name), NDArray[np.float64]):
 #                                     np.testing.assert_array_equal(
 #                                         getattr(v, f.name), getattr(camera, f.name)
 #                                     )

### 2023-08-14 calibration/feature_detector/checkerboard.py

@@ -9,7 +9,7 @@ from numpy import pi
 # import cv2
 #
 # try:
-#     import gputools  
+#     import gputools
 #
 #     GPUTOOLS = True
 # except ImportError:
@@ -113,34 +113,31 @@ def detect_corners(gray, radiuses=RADIUS):
     for angle_1, angle_2 in TPROPS:
         for radius in radiuses:
             temp = create_correlation_patch(angle_1, angle_2, radius)
-            import plotly.express as px
-            # for t_i, t in enumerate(temp):
-            #     px.imshow(t, title=f"{angle_1=}, {angle_2=}, {radius=}, {t_i=}").show()
             corr = detect_corners_template(gray, temp)
             out = np.max([corr, out], axis=0)
 
     return out
 
 
-
 def get_corner_candidates(corr, step=40, thres=0.01):
     out = []
     check = set()
-    for i in range(0, corr.shape[0], step//2):
-        for j in range(0, corr.shape[1], step//2):
-            region = corr[i:i+step, j:j+step]  # type: ignore
+    for i in range(0, corr.shape[0], step // 2):
+        for j in range(0, corr.shape[1], step // 2):
+            region = corr[i : i + step, j : j + step]  # type: ignore
             ix = np.argmax(region)
             r, c = np.unravel_index(ix, region.shape)
             val = region[r, c]
-            if val > thres and (r+i, c+j) not in check:
-                out.append( (r+i, c+j, val) )
-                check.add( (r+i, c+j) )
+            if val > thres and (r + i, c + j) not in check:
+                out.append((r + i, c + j, val))
+                check.add((r + i, c + j))
     return np.array(out)
+
 
 def non_maximum_suppression(corners, dist=40):
     tree = cKDTree(corners[:, :2])
-    good = np.ones(len(corners), dtype='bool')
-    for (a, b) in tree.query_pairs(dist):
+    good = np.ones(len(corners), dtype="bool")
+    for a, b in tree.query_pairs(dist):
         if not good[a] or not good[b]:
             continue
         sa = corners[a, 2]
@@ -151,13 +148,14 @@ def non_maximum_suppression(corners, dist=40):
             good[a] = False
     return corners[good]
 
+
[…]

### 2023-08-14 calibration/feature_detector/visualization.py

@@ -1,11 +1,14 @@
 import numpy as np
+from numpy.typing import NDArray
 import pandas as pd
 import plotly.express as px
 import plotly.graph_objects as go
 
 
 def show_corners(
-    img: np.ndarray, corners: np.ndarray, scores: np.ndarray | None = None
+    img: NDArray[np.float64],
+    corners: NDArray[np.float64],
+    scores: NDArray[np.float64] | None = None,
 ) -> go.Figure:
     fig1 = px.imshow(img, binary_string=True)
     fig2 = px.scatter(x=corners[:, 0], y=corners[:, 1], color=scores)
@@ -14,8 +17,9 @@ def show_corners(
     return go.Figure(data=[fig1.data[0], fig2.data[0]])
 
 
-# TODO: Pass lists of np.ndarray instead of Corner and Board
-def show_boards(img: np.ndarray, corners: np.ndarray, board: np.ndarray
+# TODO: Pass lists of NDArray[np.float64] instead of Corner and Board
+def show_boards(
+    img: NDArray[np.float64], corners: NDArray[np.float64], board: NDArray[np.float64]
 ) -> go.Figure:
     fig1 = px.imshow(img, binary_string=True)
 

### 2023-08-14 calibration/feature_refiner/visualization.py

@@ -1,15 +1,16 @@
 import numpy as np
+from numpy.typing import NDArray
 import pandas as pd
 import plotly.express as px
 import plotly.graph_objects as go
 
 
 def show_refined_corners(
-    img: np.ndarray,
-    corners: np.ndarray,
-    board: np.ndarray,
-    mask: np.ndarray,
-    responses: np.ndarray,
+    img: NDArray[np.float64],
+    corners: NDArray[np.float64],
+    board: NDArray[np.float64],
+    mask: NDArray[np.float64],
+    responses: NDArray[np.float64],
 ) -> go.Figure:
     fig1 = px.imshow(img, binary_string=True)
 
@@ -56,6 +57,11 @@ def show_refined_corners(
         "#bcbd22",  ## curry yellow-green
         "#17becf",  ## blue-teal
     ]
+    colors = [
+
+        "#17becf",  ## blue-teal
+            ]
+    df = df[df['mask'] == 'unchanged']
 
     fig2 = px.scatter(
         # df, x="x", y="y", color="resp", symbol="mask", hover_data=["i", "j"]
@@ -67,6 +73,6 @@ def show_refined_corners(
         # df, x="x", y="y", hover_data=["i", "j", "resp"]
         color_discrete_sequence=colors,
         category_orders={"mask": list(mask_mapping.values())},
-    ).update_traces(marker=dict(size=10))
+    ).update_traces(marker=dict(size=15))
     assert isinstance(fig1.data, tuple) and isinstance(fig2.data, tuple)
     return go.Figure(data=fig1.data + fig2.data)

### 2023-08-14 calibration/projector/board.py

@@ -1,8 +1,9 @@
 import numpy as np
+from numpy.typing import NDArray
 import plotly.express as px
 
 
-def gen_checkerboard_grid(h: int, w: int) -> np.ndarray:
+def gen_checkerboard_grid(h: int, w: int) -> NDArray[np.float64]:
     """Generate a checkerboard pattern
 
     Args:
@@ -10,7 +11,7 @@ def gen_checkerboard_grid(h: int, w: int) -> np.ndarray:
         w: width
 
     Returns:
-        np.ndarray: Array of pairs of [x, y]
+        NDArray[np.float64]: Array of pairs of [x, y]
     """
     board = np.array([[x, y] for y in range(h) for x in range(w)], np.float64)
     board /= board.max(axis=0)
@@ -18,7 +19,9 @@ def gen_checkerboard_grid(h: int, w: int) -> np.ndarray:
     return board
 
 
-def gen_charuco_grid(h: int, w: int, s1: float, s2: float | None = None) -> np.ndarray:
+def gen_charuco_grid(
+    h: int, w: int, s1: float, s2: float | None = None
+) -> NDArray[np.float64]:
     """Generate a charruco pattern
 
     Args:
@@ -28,7 +31,7 @@ def gen_charuco_grid(h: int, w: int, s1: float, s2: float | None = None) -> np.n
         s2: step size for y (default: s1)
 
     Returns:
-        np.ndarray: Array of pairs of [x, y]
+        NDArray[np.float64]: Array of pairs of [x, y]
     """
     s2 = s2 if s2 is not None else s1
     x = [i / 2 if i % 2 == 0 else (i - 1) / 2 + s1 for i in range(w)]
@@ -40,7 +43,9 @@ def gen_charuco_grid(h: int, w: int, s1: float, s2: float | None = None) -> np.n
 
 
 def draw_board(
-    board: np.ndarray, title: str | None = None, max_xy: np.ndarray | None = None
+    board: NDArray[np.float64],
+    title: str | None = None,
+    max_xy: NDArray[np.float64] | None = None,
 ):
     range_x = None if max_xy is None else (0, max_xy[0])
     range_y = None if max_xy is None else (0, max_xy[1])

### 2023-08-14 calibration/solver/optimization/backproject.py

@@ -18,12 +18,12 @@ def backproject(
 
     Args:
 
-    x (np.ndarray):
+    x (NDArray[np.float64]):
         An array of point in the image space, with shape (n, 2),
         where n is the number of points and each point is represented as [x, y].
 
     Returns:
-        X (np.ndarray):
+        X (NDArray[np.float64]):
             An array of point in the board space, with shape (n, 2),
             where n is the number of points and each point is represented as [x, y].
     """

### 2023-08-14 calibration/solver/optimization/helpers.py

@@ -1,18 +1,19 @@
 import numpy as np
 import jax.numpy as jnp
 import jax
+from numpy.typing import NDArray
 from calibration.projector.camera import Camera
 
 from calibration.projector.projector import Projector
 from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
 
 jArr = jax.Array
-nArr = np.ndarray
+nArr = NDArray[np.float64]
 
 def params_to_proj(jparams: dict[str, jArr], resolution: nArr) -> Projector | None:
     if any(np.isnan(v).any() for v in jparams.values()):
         return None
-    params = {k: np.array(v) for k, v in jparams.items()}
+    params = {k: np.array(v, dtype=np.float64) for k, v in jparams.items()}
 
     camera = Camera(
         float(jparams["focal_length"]), params["sensor_size"], np.array(resolution)

### 2023-08-14 calibration/solver/optimization/optimize.py

@@ -3,12 +3,9 @@ import numpy as np
 import jax.numpy as jnp
 import optax
 import jax
-from calibration.benchmark.benchmark_result import calc_error
 from calibration.benchmark.features import Features
 
-from calibration.solver.optimization.backproject import backproject, backprojection_loss
-from calibration.solver.optimization.helpers import params_to_proj
-from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+from calibration.solver.optimization.backproject import backprojection_loss
 
 jArr = jax.Array
 
@@ -21,7 +18,7 @@ def optimize_optax(
     # step_size=0.001,
     step_size=0.005,
     patience=100,
-) -> dict[str, jArr]:
+) -> tuple[dict[str, jArr], list]:
     # optimizer = optax.rmsprop(step_size)
     # optimizer = optax.adam(step_size)
     optimizer = optax.amsgrad(step_size)
@@ -76,8 +73,8 @@ def optimize_optax(
     phase = 0
     hist = []
     best_params, best_loss = None, np.inf
-    best_corners_error, best_board_error, best_error = np.inf, np.inf, np.inf
-    features = Features(np.array(board), np.array(corners))
+    # best_corners_error, best_board_error, best_error = np.inf, np.inf, np.inf
+    Features(np.array(board), np.array(corners))
     while True:
         params, opt_state, loss_history = step(
             i, params, opt_state, loss_history, phase
@@ -85,7 +82,7 @@ def optimize_optax(
         loss_val = loss_history[i % patience]
         # if i % 1000 == 0:
         #     proj_ = params_to_proj(params.copy(), np.array(resolution))
-            # if proj_ is not None:
+        #     if proj_ is not None:
             #     try:
             #         corners_ = proj_.project(np.array(board))
             #         corners_error = np.linalg.norm(corners_ - corners)
@@ -94,7 +91,8 @@ def optimize_optax(
             #         corners_error = np.inf
             #         # print("failed projecting")
             #     board_ = proj_.backproject(np.array(corners).astype(np.float32))
-            #     theta = jnp.concatenate([params["theta_x"], params["theta_y"], params["theta_z"]])
+            #     theta = jnp.concatenate([params["theta_x"], params["theta_y"],
+                                           #     params["theta_z"]])
             #     R = euler_angles_to_rotation_matrix(theta)
[…]

### 2023-08-14 calibration/solver/scaramuzza/extrinsics.py

@@ -1,29 +1,34 @@
 import numpy as np
+from numpy.typing import NDArray
 from scipy.linalg import svd
 
 
-def solve_extrinsic(x: np.ndarray, X: np.ndarray) -> list[np.ndarray]:
+def solve_extrinsic(
+    x: NDArray[np.float64], X: NDArray[np.float64]
+) -> list[NDArray[np.float64]]:
     """
     Computes the extrinsic parameters of a camera, given the 2D image points and
     the 3D world points.
 
     Args:
-        x (np.ndarray): Points in image space, with shape (n, 2),
+        x (NDArray[np.float64]): Points in image space, with shape (n, 2),
             where n is the number of points and each point is represented as [x, y].
-        X (np.ndarray): Points in the board space, with shape (n, 2),
+        X (NDArray[np.float64]): Points in the board space, with shape (n, 2),
             where n is the number of points and each point is represented as [x, y].
         image_center (tuple[float, float]): A tuple representing the
             image center coordinates (x, y).
 
     Returns:
-        np.ndarray: A 3x3 array representing the extrinsic parameters of the camera."""
+        NDArray[np.float64]: A 3x3 array representing the extrinsic parameters of the camera.
+    """
     M = np.vstack(
         [[-v * X_, -v * Y_, u * X_, u * Y_, -v, u] for (u, v), (X_, Y_) in zip(x, X)]
     )
 
-    # _, _, V = np.linalg.svd(M, full_matrices=False)
+    V: NDArray[np.float64]
     _, _, V = svd(M, full_matrices=False)
     assert isinstance(V, np.ndarray)
+    # Assert that it's np array of float
     H = V.T[:, -1]
     r_11, r_12, r_21, r_22, t_1, t_2 = H
 
@@ -79,5 +84,5 @@ def solve_extrinsic(x: np.ndarray, X: np.ndarray) -> list[np.ndarray]:
     #                               not behind it)
     RR_t1_dists = np.linalg.norm(RR[:2, 2, :] - x[0][:, np.newaxis], axis=0)
     min_, max_ = np.min(RR_t1_dists), np.max(RR_t1_dists)
-    min_ids =np.nonzero(RR_t1_dists < min_ + ((max_-min_) / 100) )[0]
+    min_ids = np.nonzero(RR_t1_dists < min_ + ((max_ - min_) / 100))[0]
     return [RR[:, :, i] for i in min_ids]

### 2023-08-14 calibration/solver/scaramuzza/intrinsics.py

@@ -1,22 +1,25 @@
 import numpy as np
+from numpy.typing import NDArray
 
 
 def solve_intrinsic(
-    x: np.ndarray, X: np.ndarray, p: np.ndarray
-) -> tuple[np.ndarray, np.ndarray]:
+    x: NDArray[np.float64], X: NDArray[np.float64], p: NDArray[np.float64]
+) -> tuple[NDArray[np.float64], NDArray[np.float64]]:
     """
     Computes the intrinsic parameters of a camera, given the 2D image points,
     the 3D world points, and the extrinsic parameters.
 
     Args:
-        x (np.ndarray): Points in image space, with shape (n, 2),
+        x (NDArray[np.float64]): Points in image space, with shape (n, 2),
             where n is the number of points and each point is represented as [x, y].
-        X (np.ndarray): Points in the board space, with shape (n, 2),
+        X (NDArray[np.float64]): Points in the board space, with shape (n, 2),
             where n is the number of points and each point is represented as [x, y].
-        p (np.ndarray): A 3x3 array representing the extrinsic parameters of the camera.
+        p (NDArray[np.float64]): A 3x3 array representing the extrinsic parameters
+            of the camera.
 
     Returns:
-        tuple[np.ndarray, np.ndarray]: A tuple containing the intrinsic parameters
+        tuple[NDArray[np.float64], NDArray[np.float64]]: A tuple containing the
+            intrinsic parameters
             (lambdas) and the updated extrinsic parameters (H)
             with the third translation component (t_3).
     """

### 2023-08-14 calibration/solver/scaramuzza/solve.py

@@ -1,4 +1,5 @@
 import numpy as np
+from numpy.typing import NDArray
 
 from calibration.projector.camera import Camera
 from calibration.projector.projector import Projector
@@ -7,7 +8,7 @@ from .extrinsics import solve_extrinsic
 from .intrinsics import solve_intrinsic
 
 
-def solve(x: np.ndarray, X: np.ndarray, camera: Camera) -> Projector:
+def solve(x: NDArray[np.float64], X: NDArray[np.float64], camera: Camera) -> Projector:
     """Find intrinsic and extrinsic parameters for a set of points
 
     Args:

### 2023-08-14 calibration/solver/test_solvers.py

@@ -35,8 +35,8 @@ class TestProjectorAndSolverOptimization(unittest.TestCase):
             Camera(135.0, np.array([40, 30]), np.array([1920, 1080]), 1.0),
         ]
         ts_for_cameras = [
-            list(map(np.array, product([-1.0, 0.0], [-0.7, -0.3], [3.0, 4.0]))),
-            list(map(np.array, product([-1.7, -0.8], [-1.2, -0.8], [20.0]))),
+            list(map(np.array, iter(product([-1.0, 0.0], [-0.7, -0.3], [3.0, 4.0])))),
+            list(map(np.array, iter(product([-1.7, -0.8], [-1.2, -0.8], [20.0])))),
         ]
         boards = [gen_checkerboard_grid(7, 9), gen_charuco_grid(7, 9, 0.4, 0.2)]
 
@@ -63,6 +63,7 @@ class TestProjectorAndSolverOptimization(unittest.TestCase):
                 x_ = proj_.project(board)
                 np.testing.assert_allclose(x_, x, atol=1e-10, rtol=1e-5)
 
+        # sourcery skip: no-loop-in-tests
         for solve_name, solve in [
             ("optimization", solve_optimization),
             ("scaramuzza", solve_scaramuzza),

### 2023-08-14 calibration/benchmark/test_benchmark.py
refactor: Improve code formatting and documentation

@@ -1,70 +1,0 @@
-# from dataclasses import fields
-# from tqdm.auto import tqdm
-# from itertools import product
-# from unittest import TestCase
-# import numpy as np
-# from scipy.spatial.transform import Rotation
-#
-# from calibration.benchmark.benchmark import benchmark_simul
-# from calibration.projector.camera import Camera
-#
-#
-# class TestBenchmark(TestCase):
-#     def test_benchmark(self):
-#         Rs = [
-#             np.eye(3),
-#             Rotation.from_euler("z", 10, degrees=True).as_matrix(),
-#             Rotation.from_euler("xyz", [10, 10, 10], degrees=True).as_matrix(),
-#         ]
-#         lambdass = [
-#             np.array([l1, l2])
-#             for l1 in np.arange(-5.0, 1.1, 2)
-#             for l2 in np.arange(
-#                 -2.61752136752137 * l1 - 6.85141810943093,
-#                 -2.61752136752137 * l1 - 4.39190876941320,
-#                 1.0,
-#             )
-#         ]
-#         cameras = [
-#             Camera(),
-#             Camera(135.0, np.array([40, 30]), np.array([1920, 1080]), 1.0),
-#         ]
-#         ts_for_cameras = [
-#             list(map(np.array, product([-1.0, 0.0], [-0.7, -0.3], [3.0, 4.0]))),
-#             list(map(np.array, product([-1.7, -0.8], [-1.2, -0.8], [13.0, 20.0]))),
-#         ]
-#
-#         def f(R, t, lambdas, camera):
-#             with self.subTest(t=t, R=R, lambdas=lambdas, camera=camera):
-#                 kwargs = dict(R=R, lambdas=lambdas, t=t, camera=camera)
-#                 try:
-#                     results = benchmark_simul(1, kwargs=kwargs)
-#                 except ValueError:
-#                     self.fail("ValueError in benchmark_simul")
-#                 for k, v in kwargs.items():
-#                     for r in results:
-#                         if isinstance(v, NDArray[np.float64]):
-#                             np.testing.assert_array_equal(getattr(r.input, k), v)
-#                         else:
-#                             for f in fields(v):
-#                                 if isinstance(getattr(v, f.name), NDArray[np.float64]):
-#                                     np.testing.assert_array_equal(
-#                                         getattr(v, f.name), getattr(camera, f.name)
-#                                     )
-#                                 else:
-#                                     self.assertEqual(
[…]

### 2023-08-14 calibration/solver/scaramuzza/extrinsics.py

@@ -19,7 +19,8 @@ def solve_extrinsic(
             image center coordinates (x, y).
 
     Returns:
-        NDArray[np.float64]: A 3x3 array representing the extrinsic parameters of the camera.
+        NDArray[np.float64]: A 3x3 array representing the extrinsic parameters
+        of the camera.
     """
     M = np.vstack(
         [[-v * X_, -v * Y_, u * X_, u * Y_, -v, u] for (u, v), (X_, Y_) in zip(x, X)]

### 2023-08-14 paper/poster.tex
Update pdfs, add poster

\documentclass[
  twocolumn,
  % 10pt,
  % english,
  % onehalfspacing,
]{article} % Method A for two-column formatting
\usepackage{preprint}

\usepackage{microtype}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{xfrac}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{cases}
\usepackage[noblocks]{authblk}
\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\addbibresource{references.bib}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}

% \title{Corner localization and camera calibration from imaged lattices\\
% \large supplementary material}
\title{Corner localization and camera calibration from imaged lattices
(supplementary material)}
\author{Andrii Stadnik}
\affil{Faculty of Computer Science, Ukrainian Catholic University, Lviv, Ukraine}
\author{James Pritts}
\affil{Czech Institute of Informatics, Robotics and Cybernetics at Czech Technical University in Prague, Czechia}
\date{2023}

\begin{document}

\twocolumn[
	\begin{@twocolumnfalse}
		\maketitle
	\end{@twocolumnfalse}
]

\section{Camera model}\label{sec:camera_model}

\subsection{Notation}\label{sub:notation}

\begin{table}[htbp]
	\centering
	\begin{tabularx}{\columnwidth}{lL} % use L for the long text column
		\toprule
		Term                           & Description                                                       \\
		\midrule
		\(\mathbf{u} = \begin{pmatrix}
			               u, v, 1
		               \end{pmatrix}^{T}\) & A point in the image space                                    \\
		\(\mathbf{x} = \begin{pmatrix}
			               x, y, z, 1
		               \end{pmatrix}^{T}\) & A point in the world space                                    \\
		\(R\)                          & A \(3 \times 3\) rotation matrix                                  \\
		\(\mathbf{t}\)                 & A  translation vector of length \(3\)                             \\
		\(\alpha_x, \alpha_y\)         & Scale factor in the x and y direction                             \\
		\(c_x, c_y\)                   & Coordinates of the principal point                                \\
		\(\theta\)                     & Angle between the x and y pixel axes                              \\
		\(f\)                          & Distance from the camera center to the image plane (focal length) \\
		\(f_x, f_y\)                   & Focal lengths in the x and y directions                           \\
		\(K\)                          & Intrinsic matrix                                                  \\
		\(H\)                          & A \(3 \times 3\) matrix viewing \(z=0\)                           \\
		\(\lambda_n\)                  & Distortion coefficients                                           \\
		\bottomrule
	\end{tabularx}
	\caption{Notation}
	\label{tab:notation}
\end{table}

\subsection{Extrinsic parameters}\label{sub:extrinsic_parameters}

The extrinsic parameters represent a rigid transformation from a 3-D world
coordinate system to the 3-D camera’s coordinate system.

\begin{equation*}
	\hat{\mathbf{x}} =
	R \begin{pmatrix}
		x, y, z
	\end{pmatrix}^{T} + \mathbf{t} =
	\begin{bmatrix}
		R              & \mathbf{t} \\
		\mathbf{0}^{T} & 1
	\end{bmatrix} \begin{pmatrix}
		x, y, z, 1
	\end{pmatrix}^{T},
\end{equation*}
where
\(\begin{pmatrix}
	x, y, z
\end{pmatrix}^{T}\) is a 3D scene point,
% \(R \begin{pmatrix}
% 	x, y, z
% \end{pmatrix}^{T} + \mathbf{t}\), where
\(R\) is a \(3 \times 3\) rotation matrix
and \(\mathbf{t}\) is
a \(3 \times 1\) translation vector.

Assuming coplanar scene points (\(z = 0\)):
\begin{equation*}
	\alpha \begin{pmatrix}
		u \\ v \\ 1
	\end{pmatrix} = \begin{bmatrix}
		\mathbf{r_1} & \mathbf{r_2} & \mathbf{r_3} & \mathbf{t}
	\end{bmatrix} \begin{pmatrix}
		x \\ y \\ 0 \\ 1
		% \end{pmatrix} = \begin{bmatrix}
		%   \mathbf{p_1} & \mathbf{p_2} & \mathbf{p_4}
		% \end{bmatrix} \begin{pmatrix}
		%   x \\ y \\ 1
		% \end{pmatrix}.
	\end{pmatrix} = \underbrace{\begin{bmatrix}
			\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
		\end{bmatrix}}_{H} \begin{pmatrix}
		x \\ y \\ 1
	\end{pmatrix}.
\end{equation*}

\subsection{Distortion model}
The distortion of the image is caused by the lens not being perfectly planar.
We used the division distortion model
\citep{fitzgibbonSimultaneousLinearEstimation2001} which maps a
point from a retinal plane to the
ray direction in the camera coordinates system.
\begin{equation*}
	g(\mathbf{\hat{u}}) = \begin{pmatrix}
		u, v, \psi(r(\mathbf{\hat{u}}))
	\end{pmatrix}^{T},
	\psi(\rho) = 1 + \sum_{n = 1}^{N} \lambda_n \rho^{2n},
\end{equation*}
where
\(\mathbf{\hat{u}} = \begin{pmatrix}
	u, v, 1
\end{pmatrix}^{T}\) is a point in the retinal plane
, \(r(\mathbf{\hat{u}}) = \sqrt{u^2 + v^2}\) is the radial distance from the
principal point and \(\lambda_n\) are the distortion coefficients.

\subsubsection{Back-projection using the Division Model}\label{subsub:back_projection_using_the_division_model}

The function \(\psi(\cdot)\) is not invertible in general.
Let \(\mathbf{\hat{x}} = \begin{pmatrix}
	x, y, z
\end{pmatrix}^{T} = \alpha g(\mathbf{\hat{u}})\) be a ray in the camera coordinate system.

Then,
\begin{equation} \label{eq:division_derivation1}
	\frac{\mathbf{x}}{z}  =
	\begin{pmatrix}
		\frac{x}{z}, \frac{y}{z}, 1
	\end{pmatrix}^{T}                                                                      =
	\begin{pmatrix}
		\frac{\alpha u}{\alpha \psi(r(\mathbf{\hat{u}}))},
		\frac{\alpha v}{\alpha \psi(r(\mathbf{\hat{u}}))},
		1
	\end{pmatrix}^{T} =
	\begin{pmatrix}
		\frac{u}{\psi(r(\mathbf{\hat{u}}))},
		\frac{v}{\psi(r(\mathbf{\hat{u}}))},
		1
	\end{pmatrix}^{T}.
\end{equation}

From \ref{eq:division_derivation1} we see that
\begin{equation} \label{eq:division_derivation2}
	\begin{cases}
		\frac{x}{z} = \frac{u}{\psi(r(\mathbf{\hat{u}}))} \\
		\frac{y}{z} = \frac{v}{\psi(r(\mathbf{\hat{u}}))}
	\end{cases} \implies \\
	\begin{cases}
		u = \frac{x \psi(r(\mathbf{\hat{u}}))}{z} \\
		v = \frac{y \psi(r(\mathbf{\hat{u}}))}{z}
	\end{cases}.
\end{equation}

Now, let \(\hat{r}\) be a root of
\(r(\mathbf{\hat{u}})
= \sqrt{
	\frac{x * \psi \left( \hat{r}\right)}{z}^{2} +
	\frac{y * \psi \left( \hat{r}\right)}{z}^{2}
} = \hat{r}\), assuming \(0 \leq \hat{r} \leq w\) where \(w\) is a width of
the image.

Then, \(\mathbf{\hat{u}} = f(\mathbf{x}) =
\frac{\hat{r}}{r(\mathbf{x})}\mathbf{x}\),
where \(f(\cdot)\) is the inverse of \(g(\cdot)\).

\subsection{Intrinsic parameters}
Represent a projective transformation from the 3-D camera’s coordinates into
the 2-D image coordinates.

\begin{equation*}
	K = \begin{bmatrix}
		\alpha_x & \alpha_x \cot \theta & c_x \\
		0        & \alpha_y             & c_y \\
		0        & 0                    & 1
	\end{bmatrix} \begin{bmatrix}
		f & 0 & 0 \\
		0 & f & 0 \\
		0 & 0 & 1
	\end{bmatrix} = \begin{bmatrix}
		f_x & k   & c_x \\
		0   & f_y & c_y \\
		0   & 0   & 1
	\end{bmatrix}.
\end{equation*}
For a typical camera, \(\theta = \sfrac{\pi}{2}\) and \(\alpha_x = \alpha_y\)
\citep{hartleyMultipleViewGeometry2004}:
\begin{equation*}
	K = \begin{bmatrix}
		f & 0 & c_x \\
		0 & f & c_y \\
		0 & 0 & 1
	\end{bmatrix}.
\end{equation*}

\subsection{Complete projection and backprojection}\label{sub:complete_projection_and_backprojection}

\begin{align}
	\alpha \mathbf{u} & = K f(H\mathbf{x})
	\tag{Projection} \label{eq:projection}                     \\
	\alpha \mathbf{x} & = H^{-1} g(K^{-1}\mathbf{u}) \tag{Back
		projection} \label{eq:back_projection}.
\end{align}

\section{Approach}\label{sec:approach}

\subsection{Camera calibration}\label{sub:camera_calibration}

\subsubsection{Initial approximation}\label{subsub:initial_approximation}

\subsubsection{Solving for the camera extrinsic parameters}\label{ssub:solving_for_the_camera_extrinsic_parameters}

To derive the solver for the camera extrinsic parameters, start from
\cref{eq:projection}:
\begin{align}
	\alpha \mathbf{u}                                                          & = K f(H\mathbf{x})       \\
	\alpha K^{-1} \mathbf{u}                                                   & = f(H\mathbf{x})    &  &
	\text{Move \(K\) to the left side}                                                                    \\
	\alpha g( K^{-1}\mathbf{u})                                                & = g(f(H\mathbf{x})) &  &
	\text{Set \(\mathbf{\widehat{u}} = K^{-1}\mathbf{u}\); apply \(g(\cdot)\)}                            \\
	\alpha \begin{pmatrix}
		       \widehat{u}_x \\ \widehat{u}_y \\ \psi(r(\mathbf{\widehat{u}}))
	       \end{pmatrix}^{T} & = H\mathbf{x}.
\end{align}

To eliminate the dependency on the scale \(\alpha\), multiply both sides
vectorially by \(g(\mathbf{\widehat{u}})\):
\begin{equation}
	\alpha g(\mathbf{\widehat{u}}) \times g(\mathbf{\widehat{u}})
	= g(\mathbf{\widehat{u}}) \times H\mathbf{x} \implies
	g(\mathbf{\widehat{u}})
	% \begin{pmatrix}
	% 	\widehat{u}, \widehat{v}, \psi(r(\mathbf{\widehat{u}}))
	% \end{pmatrix}^{T}
	\times \begin{bmatrix}
		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
	\end{bmatrix} \mathbf{x} = 0
	\label{eq:eq_no_multiplier}.
\end{equation}

From \cref{eq:eq_no_multiplier}, we can see that a point contributes to three
homogeneous equations:
\begin{align}
	\widehat{v} (r_{31}x + r_{32} y + t_3) -
	g(r(\mathbf{\widehat{u}})) (r_{21}x + r_{22}y + t_2 ) & = 0
	\label{eq:scaramuzza_system_1}                              \\
	g(r(\mathbf{\widehat{u}})) (r_{11}x + r_{12}y + t_1) -
	\widehat{u} (r_{31}x + r_{32} y + t_3)                & = 0
	\label{eq:scaramuzza_system_2}                              \\
	\widehat{u} (r_{21}x + r_{22}y + t_2 ) -
	\widehat{v} (r_{11}x + r_{12}y + t_1)                 & = 0
	\label{eq:scaramuzza_system_3}.
\end{align}

Only \cref{eq:scaramuzza_system_3} is linear in the unknowns. Each point gives a
single equation. Now, by rewriting the equation in the matrix form
\(M \cdot \mathbf{h} = 0\), where
\[
	\mathbf{h} = \begin{pmatrix}
		r_{11}, r_{12}, r_{21}, r_{22}, r_{31}, r_{32}
	\end{pmatrix}^{T},
\]
we get:
\begin{equation}
	M = \begin{bmatrix}
		-\widehat{v}_1 x_1 & -\widehat{v}_1 y_1 & -\widehat{u}_1 x_1 & -\widehat{u}_1 y_1 & -\widehat{v}_1 & -\widehat{u}_1 \\
		\vdots             & \vdots             & \vdots             & \vdots             & \vdots         & \vdots         \\
		-\widehat{v}_N x_N & -\widehat{v}_N y_N & -\widehat{u}_N x_N & -\widehat{u}_N y_N & -\widehat{v}_N & -\widehat{u}_N
	\end{bmatrix}
\end{equation}, where \(N\) is the number of points.

The linear estimate of \(\mathbf{h}\) is found by minimizing \(\left\lVert M \cdot
\mathbf{h} \right\rVert ^{2}\) using SVD. The solution is known up to a scale factor.

To find \(r_{31}\) and \(r_{33}\), note that \(\mathbf{r_1}\) and
\(\mathbf{r_2}\) are orthonormal. The derivation couldn't fit here, you can find
it in the thesis paper.

\subsubsection{Extrinsic parameters}\label{subsub:extrinsic_parameters}

Now, to find the rest of the parameters, we substitute the values, found in the
previous step into \cref{eq:scaramuzza_system_1} and
\cref{eq:scaramuzza_system_2}. We assumed the number of the division model's
parameter to be equal to 2, and the scalar multiplier to be equal to 1
\cref{subsub:back_projection_using_the_division_model}:

\begin{equation}
	\begin{bmatrix}
		A_1 \rho_1^{2} & A_1 \rho_1^{4} & -v_1   \\
		C_1 \rho_1^{2} & C_1 \rho_1^{4} & -v_1   \\
		\vdots         & \vdots         & \vdots \\
		A_N \rho_N^{2} & A_N \rho_N^{4} & -v_N   \\
		C_N \rho_N^{2} & C_N \rho_N^{4} & -v_N
	\end{bmatrix} \cdot \begin{bmatrix}
		\lambda_1 \\
		\lambda_2 \\
		t_3
	\end{bmatrix} = \begin{bmatrix}
		B_1 - A_1 \\
		D_1 - C_1 \\
		\vdots    \\
		B_N - A_N \\
		D_N - C_N
	\end{bmatrix},
\end{equation}
where
\begin{align}
	A_i & = r_{21} x_i + r_{22} y_i + t_2  \\
	B_i & = v_i (r_{31} x_i + r_{32} y_i)  \\
	C_i & = r_{11} x_i + r_{12} y_i + t_1  \\
	D_i & = u_i (r_{31} x_i + r_{32} y_i).
\end{align}

The solution can be found using the least squares method.

\end{document}

### 2024-05-10 calibration/solver/test_solvers.py
Add pixi

@@ -1,90 +1,0 @@
-import unittest
-from itertools import product
-
-import numpy as np
-from scipy.spatial.transform import Rotation
-from tqdm.auto import tqdm
-
-from calibration.projector.board import gen_charuco_grid, gen_checkerboard_grid
-from calibration.projector.camera import Camera
-from calibration.projector.projector import Projector
-from .optimization import solve as solve_optimization
-from .scaramuzza import solve as solve_scaramuzza
-
-
-class TestProjectorAndSolverOptimization(unittest.TestCase):
-    def test_proj_equal_backproj(self):
-        Rs = [
-            np.eye(3),
-            Rotation.from_euler("xyz", [5, 5, 5], degrees=True).as_matrix(),
-            Rotation.from_euler("xyz", [-5, 3, 5], degrees=True).as_matrix(),
-            Rotation.from_euler("xyz", [0, 0, 90], degrees=True).as_matrix(),
-            # Rotation.from_euler("xyz", [0, 0, 180], degrees=True).as_matrix(),
-        ]
-        lambdass = [
-            np.array([l1, l2])
-            for l1 in np.arange(-5.0, 1.1, 2)
-            for l2 in np.arange(
-                -2.61752136752137 * l1 - 6.85141810943093,
-                -2.61752136752137 * l1 - 4.39190876941320,
-                1.0,
-            )
-        ]
-        cameras = [
-            Camera(),
-            Camera(135.0, np.array([40, 30]), np.array([1920, 1080]), 1.0),
-        ]
-        ts_for_cameras = [
-            list(map(np.array, product([-1.0, 0.0], [-0.7, -0.3], [3.0, 4.0]))),
-            list(map(np.array, product([-1.7, -0.8], [-1.2, -0.8], [20.0]))),
-        ]
-        boards = [gen_checkerboard_grid(7, 9), gen_charuco_grid(7, 9, 0.4, 0.2)]
-
-        def f(R, t, lambdas, camera, board, solve, solve_name):
-            with self.subTest(
-                R=R, t=t, lambdas=lambdas, camera=camera, solve_name=solve_name
-            ):
-                self.assertEqual(board.dtype, np.float64)
-                proj = Projector(R=R, t=t, lambdas=lambdas, camera=camera)
-                x = proj.project(board)
-
-                self.assertTrue((x > 0).all())
-                self.assertTrue((x < proj.camera.resolution).all())
-
-                X_ = proj.backproject(x)
[…]

### 2024-05-10 main.py

@@ -3,16 +3,16 @@ import numpy as np
 
 from pandas.compat import os
 
-from calibration.benchmark.benchmark import (
+from src.benchmark.benchmark import (
     BenchmarkResult,
     benchmark_babelcalib,
     benchmark_simul,
 )
-from calibration.data.babelcalib.babelcalib import load_babelcalib
-from calibration.data.babelcalib.entry import Entry
-from calibration.feature_refiner.refine import refine_features
-from calibration.projector.camera import Camera
-from calibration.solver.optimization.solve import solve
+from src.data.babelcalib.babelcalib import load_babelcalib
+from src.data.babelcalib.entry import Entry
+from src.feature_refiner.refine import refine_features
+from src.projector.camera import Camera
+from src.solver.optimization.solve import solve
 
 
 def run_benchmark():

### 2024-05-10 src/augmentations/augmentations.py

@@ -1,7 +1,7 @@
 from PIL import Image
 import numpy as np
 
-from calibration.benchmark.features import Features
+from src.benchmark.features import Features
 
 
 def overlay_img(img: Image.Image, path: str = "data/octopus.png") -> Image.Image:

### 2024-05-10 src/benchmark/benchmark.py

@@ -1,24 +1,24 @@
 import numpy as np
 from tqdm.contrib.concurrent import process_map
-from calibration.augmentations.augmentations import overlay_img, prune_corners
-from calibration.benchmark.benchmark_result import BenchmarkResult
+from src.augmentations.augmentations import overlay_img, prune_corners
+from src.benchmark.benchmark_result import BenchmarkResult
 
-from calibration.benchmark.calib import calibrate
+from src.benchmark.calib import calibrate
 
-from calibration.benchmark.features import (
+from src.benchmark.features import (
     BABELCALIB_INP,
     SIMUL_INP,
     Features,
     babelcalib_features,
     simul_features,
 )
-from calibration.data.babelcalib.babelcalib import Dataset, load_babelcalib
-from calibration.data.babelcalib.entry import Entry
-from calibration.projector.board import gen_checkerboard_grid
-from calibration.projector.camera import Camera
-from calibration.projector.projector import Projector
-from calibration.solver.optimization.solve import solve as solve_optimization
-from calibration.solver.scaramuzza.solve import solve as solve_scaramuzza
+from src.data.babelcalib.babelcalib import Dataset, load_babelcalib
+from src.data.babelcalib.entry import Entry
+from src.projector.board import gen_checkerboard_grid
+from src.projector.camera import Camera
+from src.projector.projector import Projector
+from src.solver.optimization.solve import solve as solve_optimization
+from src.solver.scaramuzza.solve import solve as solve_scaramuzza
 
 
 def evaluate(

### 2024-05-10 src/benchmark/benchmark_result.py

@@ -1,9 +1,9 @@
 from dataclasses import asdict, dataclass, field
 import numpy as np
 import pandas as pd
-from calibration.benchmark.features import Features
-from calibration.data.babelcalib.entry import Entry
-from calibration.projector.projector import Projector
+from src.benchmark.features import Features
+from src.data.babelcalib.entry import Entry
+from src.projector.projector import Projector
 
 def calc_error(proj: Projector, features: Features) -> float:
     try:

### 2024-05-10 src/benchmark/calib.py

@@ -3,8 +3,8 @@ from typing import Callable
 import numpy as np
 from tqdm.contrib.concurrent import process_map
 
-from calibration.projector.camera import Camera
-from calibration.projector.projector import Projector
+from src.projector.camera import Camera
+from src.projector.projector import Projector
 
 from .features import Features
 

### 2024-05-10 src/benchmark/features.py

@@ -5,10 +5,10 @@ import numpy as np
 from cbdetect_py import CornerType, Params, boards_from_corners, find_corners
 from tqdm.contrib.concurrent import process_map
 
-from calibration.data.babelcalib.babelcalib import Dataset
-from calibration.data.babelcalib.entry import Entry
-from calibration.data.babelcalib.target import BoardType
-from calibration.projector.projector import Projector
+from src.data.babelcalib.babelcalib import Dataset
+from src.data.babelcalib.entry import Entry
+from src.data.babelcalib.target import BoardType
+from src.projector.projector import Projector
 
 
 @dataclass

### 2024-05-10 src/benchmark/test_benchmark.py

@@ -5,8 +5,8 @@
 # import numpy as np
 # from scipy.spatial.transform import Rotation
 #
-# from calibration.benchmark.benchmark import benchmark_simul
-# from calibration.projector.camera import Camera
+# from src.benchmark.benchmark import benchmark_simul
+# from src.projector.camera import Camera
 #
 #
 # class TestBenchmark(TestCase):

### 2024-05-10 src/data/babelcalib/babelcalib.py

@@ -8,7 +8,7 @@ from glob import glob
 from PIL import Image
 from tqdm.auto import tqdm
 
-from calibration.data.babelcalib.download import assure_babelcalib_downloaded
+from src.data.babelcalib.download import assure_babelcalib_downloaded
 
 from .entry import Entry
 from .target import load_from_dsc_file_tp_file, Target

### 2024-05-10 src/feature_refiner/classifier.py

@@ -3,9 +3,9 @@ from PIL import ImageOps
 from PIL.Image import Image
 from cbdetect_py import hessian_response
 from tqdm.auto import tqdm
-from calibration.benchmark.benchmark_result import BenchmarkResult
-from calibration.data.babelcalib.entry import Entry
-from calibration.feature_detector.checkerboard import detect_corners
+from src.benchmark.benchmark_result import BenchmarkResult
+from src.data.babelcalib.entry import Entry
+from src.feature_detector.checkerboard import detect_corners
 import cv2
 from sklearn.cluster import MeanShift, estimate_bandwidth
 import scipy.ndimage as ndi

### 2024-05-10 src/feature_refiner/refine.py

@@ -2,12 +2,12 @@ from dataclasses import dataclass, field
 from functools import partial
 import numpy as np
 from tqdm.contrib.concurrent import process_map
-from calibration.benchmark.benchmark_result import BenchmarkResult, calc_error
+from src.benchmark.benchmark_result import BenchmarkResult, calc_error
 
-from calibration.benchmark.features import Features
-from calibration.data.babelcalib.entry import Entry
-from calibration.feature_refiner.classifier import prune_corners
-from calibration.projector.projector import Projector
+from src.benchmark.features import Features
+from src.data.babelcalib.entry import Entry
+from src.feature_refiner.classifier import prune_corners
+from src.projector.projector import Projector
 
 
 @dataclass

### 2024-05-10 src/solver/optimization/helpers.py

@@ -1,10 +1,10 @@
 import numpy as np
 import jax.numpy as jnp
 import jax
-from calibration.projector.camera import Camera
+from src.projector.camera import Camera
 
-from calibration.projector.projector import Projector
-from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+from src.projector.projector import Projector
+from src.solver.optimization.rotation import euler_angles_to_rotation_matrix
 
 jArr = jax.Array
 nArr = np.ndarray
@@ -15,7 +15,7 @@ def params_to_proj(jparams: dict[str, jArr], resolution: nArr) -> Projector | No
     params = {k: np.array(v) for k, v in jparams.items()}
 
     camera = Camera(
-        float(jparams["focal_length"]), params["sensor_size"], np.array(resolution)
+        float(jparams["focal_length"].squeeze()), params["sensor_size"], np.array(resolution)
     )
 
     theta = jnp.concatenate(

### 2024-05-10 src/solver/optimization/optimize.py

@@ -3,12 +3,12 @@ import numpy as np
 import jax.numpy as jnp
 import optax
 import jax
-from calibration.benchmark.benchmark_result import calc_error
-from calibration.benchmark.features import Features
+from src.benchmark.benchmark_result import calc_error
+from src.benchmark.features import Features
 
-from calibration.solver.optimization.backproject import backproject, backprojection_loss
-from calibration.solver.optimization.helpers import params_to_proj
-from calibration.solver.optimization.rotation import euler_angles_to_rotation_matrix
+from src.solver.optimization.backproject import backproject, backprojection_loss
+from src.solver.optimization.helpers import params_to_proj
+from src.solver.optimization.rotation import euler_angles_to_rotation_matrix
 
 jArr = jax.Array
 

### 2024-05-10 src/solver/optimization/solve.py

@@ -2,13 +2,13 @@ import jax.numpy as jnp
 import numpy as np
 import jax
 from scipy.spatial.transform import Rotation
-from calibration.benchmark.benchmark_result import calc_error
-from calibration.benchmark.features import Features
-from calibration.projector.camera import Camera
-from calibration.projector.projector import Projector
-from calibration.solver.optimization.helpers import params_to_proj
-from calibration.solver.optimization.optimize import optimize_optax
-from calibration.solver.scaramuzza.solve import solve as solve_scaramuzza
+from src.benchmark.benchmark_result import calc_error
+from src.benchmark.features import Features
+from src.projector.camera import Camera
+from src.projector.projector import Projector
+from src.solver.optimization.helpers import params_to_proj
+from src.solver.optimization.optimize import optimize_optax
+from src.solver.scaramuzza.solve import solve as solve_scaramuzza
 
 jArr = jax.Array
 nArr = np.ndarray

### 2024-05-10 src/solver/scaramuzza/solve.py

@@ -1,7 +1,7 @@
 import numpy as np
 
-from calibration.projector.camera import Camera
-from calibration.projector.projector import Projector
+from src.projector.camera import Camera
+from src.projector.projector import Projector
 
 from .extrinsics import solve_extrinsic
 from .intrinsics import solve_intrinsic

### 2024-05-10 src/solver/test_solvers.py

@@ -1,0 +1,69 @@
+import numpy as np
+from itertools import product
+from scipy.spatial.transform import Rotation
+
+import pytest
+from src.projector.board import gen_charuco_grid, gen_checkerboard_grid
+from src.projector.camera import Camera
+from src.projector.projector import Projector
+from .optimization.solve import solve as solve_optimization
+from .scaramuzza.solve import solve as solve_scaramuzza
+
+Rs = [
+    np.eye(3),
+    Rotation.from_euler("xyz", [5, 5, 5], degrees=True).as_matrix(),
+    Rotation.from_euler("xyz", [-5, 3, 5], degrees=True).as_matrix(),
+    Rotation.from_euler("xyz", [0, 0, 90], degrees=True).as_matrix(),
+]
+lambdass = [
+    np.array([l1, l2])
+    for l1 in np.arange(-5.0, 1.1, 2)
+    for l2 in np.arange(
+        -2.61752136752137 * l1 - 6.85141810943093,
+        -2.61752136752137 * l1 - 4.39190876941320,
+        1.0,
+    )
+]
+cameras = [
+    Camera(),
+    Camera(135.0, np.array([40, 30]), np.array([1920, 1080]), 1.0),
+]
+ts_for_cameras = [
+    list(map(np.array, product([-1.0, 0.0], [-0.7, -0.3], [3.0, 4.0]))),
+    list(map(np.array, product([-1.7, -0.8], [-1.2, -0.8], [20.0]))),
+]
+
+boards = [gen_checkerboard_grid(7, 9), gen_charuco_grid(7, 9, 0.4, 0.2)]
+
+solve_functions = [
+    ("optimization", solve_optimization),
+    ("scaramuzza", solve_scaramuzza),
+]
+
+parameters = [
+    args
+    for camera, ts in zip(cameras, ts_for_cameras)
+    for args in product(solve_functions, [camera], ts, Rs, lambdass, boards)
+]
+
+
+@pytest.mark.parametrize("solve_name_solve, camera, t, R, lambdas, board", parameters)
+def test_proj_equal_backproj(solve_name_solve, camera, t, R, lambdas, board):
+    solve_name, solve = solve_name_solve
+    proj = Projector(R=R, t=t, lambdas=lambdas, camera=camera)
+    x = proj.project(board)
+
+    assert (x > 0).all()
+    assert (x < proj.camera.resolution).all()
+
[…]
